---
title: "01_old"
output: html_document
date: "2024-07-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##    Cleaning College File

```{r col clean, include=FALSE}
all_col_unrated = postsec %>%
  # Remove institutions that don't offer bachelor's degrees
  filter(HLOFFER > 4) %>%
  # Removing columns to ensure harmonious merge with K12 data
  select(c(UNITID:FIPS,CONTROL,C21UGPRF,CARNEGIE,HBCU,TRIBAL,LANDGRNT,CBSA,CBSATYPE)) %>%
  # Rename columns to ensure harmonious merge with K12 data
#  rename(GeoFIPS = CNTY) %>%
  # Match to CBSA codes using county-CBSA crosswalk
  mutate(FIPS = str_replace_all(FIPS," ","0"),
         CBSA = ifelse(CBSATYPE != 1,paste0(FIPS,999),CBSA),
         degree = "Bachelor's",
         alt_name = str_to_lower(INSTNM),
         alt_name = str_trim(alt_name),
         alt_name = str_replace_all(alt_name, "[[:punct:]]"," "),
         alt_name = str_replace_all(alt_name, "main campus",""),
         alt_name = str_replace_all(alt_name," at "," "),
         #  Manual recodes for large universities
         #  We can do more cleaning later
#         alt_name = str_replace_all(alt_name, "the pennsylvania state","penn state"),
#         alt_name = str_replace_all(alt_name, "at raleigh",""),
#         alt_name = str_replace_all(alt_name, "fort collins",""),
#         alt_name = str_replace_all(alt_name, "campus immersion",""),
#         alt_name = str_replace_all(alt_name, "and agricultural & mechanical college",""),
#         alt_name = str_replace_all(alt_name, "university oxford",""),
         alt_name = str_replace_all(alt_name, "the university of","university of"),
#         alt_name = str_replace_all(alt_name, "university carbondale","university"),
         alt_name = str_replace_all(alt_name, "a&m","agricultural and mechanical"),
         alt_name = str_replace_all(alt_name, "a & m","agricultural and mechanical"),
         alt_name = str_trim(alt_name),
         alt_name = str_squish(alt_name)) %>%
  rename("cbsa_code" = "CBSA",
         "col_state" = "STABBR")
```

##    Cleaning Chetty File
File will evenutally merge LI instituions with Chetty's selectivity data, which doesn't include all institutions 
Problem is particularly bad for institutions with multiple campuses
String cleaning occurs in chunk below
```{r chetty, include=FALSE}
# Merge selectivity rating with geographic data so there's only big merge with LI
# First use the data from Chetty (2019) found at
# https://opportunityinsights.org/wp-content/uploads/2018/04/mrc_table10.csv
chetty = chetty_raw %>%
  select(name,barrons) %>%
  rename(col_name = name) %>%
  mutate(alt_name = str_to_lower(col_name),
         alt_name = str_trim(alt_name),
         alt_name = str_replace_all(alt_name, "[[:punct:]]"," "),
         alt_name = str_replace_all(alt_name, "main campus",""),
         alt_name = str_replace_all(alt_name, " at "," "),
         alt_name = str_replace_all(alt_name, "the university of","university of"),
         alt_name = str_replace_all(alt_name, "a&m","agricultural and mechanical"),
         alt_name = str_replace_all(alt_name, "a & m","agricultural and mechanical"),
         alt_name = str_trim(alt_name),
         alt_name = str_squish(alt_name))
```

##    Cleaning Barron's File
File will eventually link institutions with no match in Chetty's data
Relies in 2001 Barron's data
String cleaning occurs in chunk below
```{r barrons, include=FALSE}
# Since their data collapses multiple branches of some universities into a
# single entry, I supplement with Barron's 2001 data available in the UMich library
barrons = barrons_raw %>%
  rename(col_name = name,
         col_state = state) %>%
  mutate(alt_name = str_to_lower(col_name),
         alt_name = str_trim(alt_name),
         alt_name = str_replace_all(alt_name, "[[:punct:]]"," "),
         alt_name = str_replace_all(alt_name, "main campus",""),
         alt_name = str_replace_all(alt_name, " at "," "),
         alt_name = str_replace_all(alt_name, "the university of","university of"),
         alt_name = str_replace_all(alt_name, "a&m","agricultural and mechanical"),
         alt_name = str_replace_all(alt_name, "a & m","agricultural and mechanical"),
         alt_name = str_trim(alt_name),
         alt_name = str_squish(alt_name))
```

##    Merging Selectivity and LI Data

```{r barrons, include=FALSE}
# Begin by matching Chetty to all_col
# Chetty includes 913 2-year schools that shouldn't show up in our data
# The remaining 1,550 should show up
tiered_chetty = all_col_unrated %>%
  left_join(chetty, by = "alt_name") %>%
  filter(is.na(col_name)==FALSE) %>%
  # To appease the rbind gods
  select(-c(col_name))

# Create crosswalk with 2001 Barron's ratings
tiered_barrons = all_col_unrated %>%
  left_join(chetty, by = "alt_name") %>%
  filter(is.na(col_name)==TRUE) %>%
  select(-c(col_name:barrons)) %>%
  left_join(barrons, by = c("alt_name","col_state")) %>%
  select(-col_name) %>%
  filter(is.na(barrons)==FALSE)

barrons_chetty = rbind(tiered_chetty,tiered_barrons) %>%
  select(c(alt_name,cbsa_code,barrons)) %>%
  distinct()
#  rename(col_name = NAME)
```


##    Creating Outputs
all_col will be passed onto step 2
completed_neither helps me find problematic institutions without selectivity ratings
```{r output, include=FALSE}
all_col = all_col_unrated %>%
  left_join(barrons_chetty, by = c("alt_name","cbsa_code")) %>%
  mutate(barrons = ifelse(is.na(barrons)==TRUE,"Unrated",barrons)) %>%
  mutate(cleaned_name = alt_name)
  
completed_neither = all_col_unrated %>%
  left_join(chetty, by = "alt_name") %>%
  filter(is.na(col_name)==TRUE) %>%
  select(-c(col_name:barrons)) %>%
  left_join(barrons, by = c("alt_name","col_state")) %>%
  select(-col_name) %>%
  filter(is.na(barrons)==TRUE)
```
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
