---
title: "04_dummies_optimized"
author: "Nicholas Martens"
date: "2024-01-15"
output: html_document
---

# Setup

Directories and filenames that change with machine
```{r directory, include=FALSE}
directory = "/Volumes/lsa-areynoso"
#directory = "/nfs/turbo/lsa-areynoso"
eckertcbpfilename = "efsy_panel_naics.csv"
cbp19filename = "cbp19co.txt"
cbp20filename = "cbp20co.txt"
cbp21filename = "cbp21co.txt"
cbp22filename = "cbp22co.txt"

```

Import necessary packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(table.express)
library(DescTools)
library(data.table)

options(scipen=999)
```

#    Import Eckert CBP (1975-2018)

```{r eckert cbp import, include=FALSE}

# Import County Business Patterns data downloaded from:
# https://fpeckert.me/cbp/ 
cbp = fread(file.path(directory,"Data/04",eckertcbpfilename),
            # Ensure state and county codes are characters
            colClasses=list(character=1:3),
            # Omit last column to save memory
            drop=c("v1"))

# Select appropriate columns to ensure consistent merge with recent CBP
cbp_cols = c('fipstate','fipscty','naics','emp')
colnames(cbp) = c(cbp_cols,"year")

# Standardize formatting of county and state FIPS to simplify future merges
cbp = cbp %>% 
  table.express::mutate(fipstate = str_pad(fipstate, width=2, side="left", pad="0"),
                        fipscty = str_pad(fipscty, width=3, side = "left", pad = "0"))

```

#    Import Census CBP (2019-2021)

```{r census cbp import, include=FALSE}

# Import CBP from Census website
# Starting in 2018, the Census added random noise
# So none of the cells are missing
cbp22 = fread(file.path(directory,"Data/04",cbp22filename),
              select = cbp_cols,
              # Ensure state and county codes are characters
              colClasses=list(character=1:3)) %>%
  table.express::mutate(year = 2022)
cbp21 = fread(file.path(directory,"Data/04",cbp21filename),
              select = cbp_cols,
              # Ensure state and county codes are characters
              colClasses=list(character=1:3)) %>%
  table.express::mutate(year = 2021)
cbp20 = fread(file.path(directory,"Data/04",cbp20filename),
              select = cbp_cols,
              # Ensure state and county codes are characters
              colClasses=list(character=1:3)) %>%
  table.express::mutate(year = 2020)
cbp19 = fread(file.path(directory,"Data/04",cbp19filename),
              select = cbp_cols,
              # Ensure state and county codes are characters
              colClasses=list(character=1:3)) %>%
  table.express::mutate(year = 2019)

# Combine 2018-21 CBP into single file
cbp_census = rbind(cbp21,cbp20,cbp19)

# Remove total and subtotal columns
cbp_census = cbp_census[grepl("-",naics)==FALSE]

# Remove all but three-digit NAICS
# Keeping other columns would result in double, triple, and quadruple counting
cbp_census = cbp_census[grepl("///",naics)==TRUE]

# Remove intermediate objects to save memory
rm(cbp19,cbp20,cbp21,cbp22)

```

#    Clean CBP Data

```{r clean cbp, include=FALSE}

# Merge Eckert and recent CBP data into single series
cbp = rbind(cbp,cbp_census)

cbp[, fips_county := do.call(paste0, .SD), .SDcols = c("fipstate","fipscty")]
# Remove original geo-code data, which could be reconstructed from fips_county
cbp = cbp[,c("fipstate", "fipscty") := NULL]

# Merge with cbsa codes
cbp_cbsa = cbp[unified_cbsa, on = c(fips_county = "GeoFIPS")] %>%
  # Group into three digit NAICS codes
  table.express::mutate(naics3 = str_sub(naics, start = 1, end = 3))

# Summarize table by cbsa, to ease memory constraints
cbp_cbsa = cbp_cbsa[,.(cbsa_total=sum(emp)),.(naics3,year,cbsa_code)]

# Remove intermediate objects to save memory
rm(cbp,cbp_census)
gc()
```

#   Calculating National Employment Growth

```{r cbp national, include=FALSE}

# Calculate national employment by 3-digit NAICS code
cbp_nat = cbp_cbsa[,.(nat_total=sum(cbsa_total)),.(naics3,year)]

# Reorder columns to ensure net change calculations behave
setorder(cbp_nat, cols = "naics3","year")

# Define annual change function
# https://stackoverflow.com/questions/29055597/data-table-operation-with-sd-calculating-percentage-change-concisely 
# Importantly, to project 1976 we need multiply local 1975 emp by national 1975-76 growth
# So quite a bit of shifting occurs
pct_change <- function(x) shift((x - shift(x))/shift(x) + 1, type="lead")

# Specify column for calculating annual change
cols <- c("nat_total")

# Calculate annual change by 3-digit NAICS code
cbp_nat_chg = cbp_nat[, paste("chg", cols, sep="_") := lapply(.SD, pct_change), 
                      by = c("naics3"), .SDcols = cols][] 
```

#   Projecting Local Employment
Interacting local industrial mix with national employment growth to project annual
employment in CBSA. 
Projected annual employment subtracted from employment measured by CBP
```{r cbp national, include=FALSE}

# Merge national change into CBSA-level dataset
# Calculation of local employment becomes a summarization of a column-wise operation
cbp_cbsa = cbp_cbsa[cbp_nat_chg, on = c("year","naics3")] %>%
  table.express::mutate(proj_emp = cbsa_total * chg_nat_total)

# Projected local CBSA-employment (available starting in 1976 for most NAICS)
cbp_cbsa_proj = cbp_cbsa[,.(cbsa_proj=sum(proj_emp,na.rm=TRUE)),.(year,cbsa_code)] %>%
  # Shift projected employment to correspond with projected year, not year used for calculation
  mutate(year = year + 1)


# Remove intermediate objects to save memory
rm(cbp_nat,cbp_nat_chg)
```

#   Shock Calculation

```{r cbp national, include=FALSE}

# Calculate actual CBSA-level employment totals by year
cbp_cbsa_actual = cbp_cbsa[,.(cbsa_actual=sum(cbsa_total)),.(cbsa_code,year)]

# Merge projected and actual CBSA-level employment totals
cbsa_shock = merge(cbp_cbsa_actual, cbp_cbsa_proj, by = c("year","cbsa_code"), all.x = TRUE)
# Arrange object by cbsa_code and year to ensure differencing goes smoothly
setorder(cbsa_shock, cbsa_code, year)
# Calculcation of log shifts so we can estimate semi-elasticities 
cbsa_shock = cbsa_shock[,cbsa_proj_change := cbsa_proj - shift(cbsa_actual, type = "lag"), by = cbsa_code] %>%
  # Calculate year-over-year change to compare OLS versus IV
  table.express::mutate(cbsa_growth = log(cbsa_actual) - log(shift(cbsa_actual, type = "lag"))) %>%
  # Calculate the labor demand shock
  table.express::mutate(cbsa_shock = log(cbsa_actual) - log(cbsa_proj)) %>%
  #table.express::mutate(cbsa_shock = (cbsa_actual - cbsa_proj)/cbsa_actual) %>%
  filter(is.na(year)==FALSE)


# Replace values with NA in specific columns when year == 2017
# Eckert et al's documentation recommends treating 2016-2017 comparisons with caution
# Shifting from suppression to noised cells leads to over-estimates in large MSAs 
# and undercounts in small ones.
cbsa_shock[year == 2017, `:=`(
  cbsa_shock = NA,
  cbsa_growth = NA
)]

# Reorder columns to ensure net change calculations behave
setorder(cbsa_shock, cols = "cbsa_code","year")

# Lag appropriate data for calculation of average shocks
shock_cols <- c("cbsa_shock")
growth_cols <- c("cbsa_growth")
 
for ( i in 1:6 ) { # update for the number of shifts
  shock_lag_names <- paste("shock_lag", i, sep = "_")
  growth_lag_names <- paste("growth_lag", i, sep = "_")
  cbsa_shock[, (shock_lag_names) := lapply(.SD, shift, i, type = "lag"), by = c("cbsa_code"), .SDcols = shock_cols]
  cbsa_shock[, (growth_lag_names) := lapply(.SD, shift, i, type = "lag"), by = c("cbsa_code"), .SDcols = growth_cols]
}

# Remove intermediate objects to save memory
#rm(cbp_cbsa,cbp_cbsa_actual,cbp_cbsa_proj)
```

#   Calculate Averages

```{r shock averages, include=FALSE}

# One-year average is just cbsa_shock
# I call it one-year average to keep names consistent 
cbsa_shock = cbsa_shock %>%
  table.express::mutate(shock_avg_1 = cbsa_shock,
                        growth_avg_1 = cbsa_growth) %>%
  # Remove observation for 2022 because CBP data stops in 2021
  table.express::filter(is.na(cbsa_actual)==FALSE)

# Identify columns used for each average
shock_avg_3_cols = c('cbsa_shock',paste0("shock_lag_",c(1:2)))
shock_avg_5_cols = c('cbsa_shock',paste0("shock_lag_",c(1:4)))
shock_avg_7_cols = c('cbsa_shock',paste0("shock_lag_",c(1:6)))
growth_avg_3_cols = c('cbsa_growth',paste0("growth_lag_",c(1:2)))
growth_avg_5_cols = c('cbsa_growth',paste0("growth_lag_",c(1:4)))
growth_avg_7_cols = c('cbsa_growth',paste0("growth_lag_",c(1:6)))

# Calculate averages
cbsa_shock[, shock_avg_3 := rowMeans(.SD, na.rm = TRUE), .SDcols = shock_avg_3_cols] 
cbsa_shock[, shock_avg_5 := rowMeans(.SD, na.rm = TRUE), .SDcols = shock_avg_5_cols] 
cbsa_shock[, shock_avg_7 := rowMeans(.SD, na.rm = TRUE), .SDcols = shock_avg_7_cols] 
cbsa_shock[, growth_avg_3 := rowMeans(.SD, na.rm = TRUE), .SDcols = growth_avg_3_cols] 
cbsa_shock[, growth_avg_5 := rowMeans(.SD, na.rm = TRUE), .SDcols = growth_avg_5_cols] 
cbsa_shock[, growth_avg_7 := rowMeans(.SD, na.rm = TRUE), .SDcols = growth_avg_7_cols] 

# Remove unnecessary columns
cbsa_shock = cbsa_shock[,c(growth_avg_7_cols,shock_avg_7_cols) := NULL]
```

# Standardize Shocks
```{r shock percentiles, include=FALSE}

# Calculate weighted quantile for the one-year average, which has no NAs
# Every other average isn't fully available at the start of the period
cbsa_shock_ptile = cbsa_shock[, ptile_shock_avg_1 := (shock_avg_1 - weighted.mean(shock_avg_1, w = cbsa_actual))/sd(shock_avg_1), by = c("year")]
cbsa_shock_ptile[, ptile_growth_avg_1 := (growth_avg_1 - weighted.mean(growth_avg_1, w = cbsa_actual))/sd(growth_avg_1), by = c("year")]

# Since wtd.quantile doesn't want to behave, we will filter then re-merge
avg_3 = cbsa_shock_ptile[,c("cbsa_code","year","cbsa_actual","shock_avg_3","growth_avg_3")] %>%
  table.express::filter(is.na(shock_avg_3)==FALSE)
avg_5 = cbsa_shock_ptile[,c("cbsa_code","year","cbsa_actual","shock_avg_5","growth_avg_5")] %>%
  table.express::filter(is.na(shock_avg_5)==FALSE)
avg_7 = cbsa_shock_ptile[,c("cbsa_code","year","cbsa_actual","shock_avg_7","growth_avg_7")] %>%
  table.express::filter(is.na(shock_avg_7)==FALSE)

# Calculate quantiles weighted by size of labor force as measured by CBP
avg_3[, ptile_shock_avg_3 := (shock_avg_3 - weighted.mean(shock_avg_3, w = cbsa_actual))/sd(shock_avg_3), by = c("year")]
avg_3[, ptile_growth_avg_3 := (growth_avg_3 - weighted.mean(growth_avg_3, w = cbsa_actual))/sd(growth_avg_3), by = c("year")]
avg_5[, ptile_shock_avg_5 := (shock_avg_5 - weighted.mean(shock_avg_5, w = cbsa_actual))/sd(shock_avg_5), by = c("year")]
avg_5[, ptile_growth_avg_5 := (growth_avg_5 - weighted.mean(growth_avg_5, w = cbsa_actual))/sd(growth_avg_5), by = c("year")]
avg_7[, ptile_shock_avg_7 := (shock_avg_7 - weighted.mean(shock_avg_7, w = cbsa_actual))/sd(shock_avg_7), by = c("year")]
avg_7[, ptile_growth_avg_7 := (growth_avg_7 - weighted.mean(growth_avg_7, w = cbsa_actual))/sd(growth_avg_7), by = c("year")]

# Re-merge normalized into cbsa_shock
# I'm not sure why I lose pre-1982 observations but they're not essential to my analysis
cbsa_shock_ptile = cbsa_shock_ptile[avg_3, 
                                    on = c("cbsa_code","year","cbsa_actual","shock_avg_3","growth_avg_3"), 
                                    nomatch = NA]
cbsa_shock_ptile = cbsa_shock_ptile[avg_5, 
                                    on = c("cbsa_code","year","cbsa_actual","shock_avg_5","growth_avg_5"), 
                                    nomatch = NA]
cbsa_shock_ptile = cbsa_shock_ptile[avg_7, 
                                    on = c("cbsa_code","year","cbsa_actual","shock_avg_7","growth_avg_7"), 
                                    nomatch = NA]

# Some glitch in wtd.quantile added NAs for 3 cbsa x year observations
# All observations fall within the top decile in their respective year distributions
avg_names = c(paste0("ptile_growth_avg_",c(1,3,5,7)),paste0("ptile_shock_avg_",c(1,3,5,7)))
setDT(cbsa_shock_ptile)[, (avg_names) := lapply(.SD, nafill, fill = 10), .SDcols = avg_names]

write.csv(cbsa_shock_ptile,file.path(directory,"Data/04","cbsa_shock.csv"))

rm(cbp_cbsa_actual,cbp_cbsa_proj,cbp_cbsa)

```
