---
title: "02_import_ed_microdata"
author: "Nicholas Martens"
date: "2023-06-09"
output: html_document
---
## Setup

Directories and filenames that change with machine
```{r directory, include=FALSE}
directory = "/Users/nickmartens/Dropbox (University of Michigan)/Linkedin/"
edufilename = "raw_educ_STATES.csv"
```

Import necessary packages
```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(table.express)
library(data.table)
```

## Declaring Functions
Function used to compute mode of a dataset

```{r mode, include=FALSE}
Mode <- function(x, na.rm = TRUE)
{
  if(na.rm)
  {
    x = x[!is.na(x)]
  }
  ux <- unique(x)
  return(ux[which.max(tabulate(match(x,ux)))])
}
```

Declare %nin% so we can filter observations

```{r negate, include=FALSE}
`%nin%` = Negate(`%in%`)
```

## Import and Clean Education File
Import raw education file from LinkedIN
Complete basic string cleaning like removing dashes and making lowercase

```{r import, echo=FALSE}
ed_li = fread(file.path(directory,"Data/02",edufilename),
              drop = c('world_rank'))
# Adding the information from the position file doesn't increase matches
# For now it can be skipped
#ed_pos = fread(file.path(directory,"Data/03",posfilename),
#            select = c('user_id','educ_startdate','university_name','educ_enddate',
#                'degree','field','university_country'),
#            colClasses=list(character=c('educ_startdate','university_name',
#                                        'educ_enddate','degree','field',
#                                        'university_country'),
#                            integer=c('user_id'))) %>%
#  distinct(university_name,user_id,degree) %>%
  #filter(university_country == "United States") %>%
#  table.express::filter(is.na(university_name)==FALSE)
# Combine attainment data from educational and position files
#ed_li = rbind(ed_li,ed_pos)
# Remove redundant intermediate objects to save memory
#rm(ed_pos)
# Filter out associates degrees
ed_li = ed_li[degree != "Associate"]
# Filter universities outside US
# Simplifies encoding by removing institutions with foreign accents
ed_li = ed_li[university_country %in% c("United States","\\N")]
# I convert to ASCII because it avoids headaches associated with non-English characters
# Since my analysis focuses on American educational institutions,
# foreign names are not very prevalent
ed_li$university_name = iconv(ed_li$university_name, from = "UTF-8", to = "ASCII", sub = "")

# Remove extra spaces and punctuation from institution names
ed_li = ed_li[, alt_name := str_trim(str_to_lower(gsub("[[:punct:]]"," ",university_name)))]
# Remove observations with empty institution name
ed_li = ed_li[-which(ed_li$alt_name == ""), ]
# Remove "main campus" to improve matches
ed_li = ed_li[, alt_name := gsub("main campus","",alt_name)]

```

## Extract High School Diplomas

```{r hs split, echo=FALSE}
li_hs = ed_li %>%
  table.express::filter(degree == "High School") %>%
  # Remove any observations that match to a postsecondary institution
  table.express::left_join(all_col, "alt_name") %>%
  table.express::distinct(user_id,INSTNM, .keep = TRUE)

# Reclassifies observations Revelio misidentified
li_hs_misclassified = li_hs %>%
  table.express::filter(is.na(barrons)==FALSE)

# Standardize columns to ease rbind later on
li_hs_misclassified = li_hs_misclassified[,c("user_id","educ_startdate",
                                             "educ_enddate","university_name","degree",
                                             "field","alt_name","col_state","CONTROL",
                                             "C21UGPRF","CARNEGIE","HBCU","TRIBAL","LANDGRNT",
                                             "cbsa_code","CBSATYPE","barrons")]

# High schools correctly classified by Revelio
li_hs_correct = li_hs %>%
  table.express::filter(is.na(barrons)==TRUE) %>%
  table.express::distinct(user_id,university_name, .keep = TRUE)
li_hs_correct[,(names(li_hs_correct)[3:18]):=NULL]
li_hs_correct = li_hs_correct[all_hs, on = "alt_name", allow.cartesian=TRUE] %>%
  table.express::filter(is.na(user_id)==FALSE) %>%
  table.express::distinct(user_id,NAME)

# Delete columns to avoid confusion
li_hs_correct[, c("NAME","degree"):=NULL] %>%
  # Rename to columns to appease to rbind gods
  setnames(c("i.degree.1","STATE"),c("degree","hs_state"))

# Standardize columns to ease rbind later on
li_hs_correct = li_hs_correct[,c("user_id","educ_startdate","educ_enddate",
                                 "university_name","degree","field","alt_name",
                                 "hs_state","cbsa_code")]
  
```

## Extract Unknown Degrees

```{r hs split, echo=FALSE}

# Users with unknown degrees
# Currently matches based on first institution listed
# Eventually I will hone the matching based on workhistory
li_unknown = ed_li %>%
  table.express::filter(degree == "empty")

# Delete degree column from user-inputted data and merge
# We will merge with institutional data for imputed degree 
li_unknown[,c("degree"):=NULL]
li_unknown_col = li_unknown[all_col, on = "alt_name"] %>%
  table.express::distinct(user_id,INSTNM) %>%
  table.express::filter(is.na(user_id)==FALSE)

# Standardize columns to ease rbind later on
li_unknown_col = li_unknown_col[,c("user_id","educ_startdate","educ_enddate",
                                   "university_name","degree","field",
                                   "alt_name","col_state","CONTROL","C21UGPRF",
                                   "CARNEGIE", "HBCU", "TRIBAL", "LANDGRNT",
                                   "cbsa_code","CBSATYPE","barrons")]

# Identify high schools among institutions with no degree marked
li_unknown_hs = li_unknown[all_hs, on = "alt_name"] %>%
  table.express::distinct(user_id,university_name) %>%
  filter(is.na(user_id)==FALSE) %>%
  setnames("STATE","hs_state")

# Standardize columns to ease rbind later on
li_unknown_hs = li_unknown_hs[,c("user_id","educ_startdate","educ_enddate",
                                 "university_name","degree","field","alt_name",
                                 "hs_state","cbsa_code")]
```

## Extract College Degrees

```{r col split, echo=FALSE}

# College groups bachelor's and master's degrees together
li_col = ed_li %>%
  table.express::filter(degree %nin% c("empty","High School"))

# Remove any observations that match to a secondary institution
li_col_misclassified = li_col[all_hs, on = "alt_name"] %>%
  table.express::filter(is.na(user_id)==FALSE) %>%
  # Marks any graduates of the New School as high schoolers unless corrected
  table.express::filter(alt_name != "the new school")

# Reclassifies observations Revelio misidentified
li_col_misclassified[, c("degree") := NULL] %>%
  table.express::mutate(degree = "High School") %>%
  setnames(c("i.degree","STATE"),c("degree","hs_state"))

# Standardize columns to ease rbind later on
li_col_misclassified = li_col_misclassified[,c("user_id","educ_startdate",
                                               "educ_enddate","university_name",
                                               "degree","field","alt_name",
                                               "hs_state","cbsa_code")]

# Colleges correctly classified by Revelio
li_col_correct = li_col[all_col, on = "alt_name"] %>%
  table.express::filter(is.na(degree)==FALSE) %>%
  # For now I will filter out all graduate degrees
  table.express::filter(degree == "Bachelor") %>%
  # Remove duplicate entries from the same institution for the same user_id
  distinct(user_id,INSTNM)
# Standardize columns to ease rbind later on
li_col_correct = li_col_correct[,c("user_id","educ_startdate","educ_enddate","university_name",
                  "degree","field","alt_name","col_state","CONTROL","C21UGPRF",
                  "CARNEGIE","HBCU","TRIBAL","LANDGRNT","cbsa_code","CBSATYPE","barrons")]

```


## Consolidated and Simplified

```{r col split, echo=FALSE}

hs_match = ed_li[all_hs, on = "alt_name"]
not_hs = ed_li[!all_hs, on = "alt_name"]
col_match = not_hs[all_col, on = "alt_name"] %>%
  table.express::filter(is.na(university_name)==FALSE)

# Extract user IDs for people listing baccalaureate institution on LI
col_users = col_match %>% table.express::select(user_id)

# Extract user IDs for people listing high school on LI
hs_users = hs_match %>% table.express::select(user_id)

# Create list of people listing both high school and baccalaureate institutions
# Wait on creating both until data extracted from position file
both = as.data.table(intersect(col_users$user_id,hs_users$user_id)) %>%
  setnames("V1","user_id")

# Find users with multiple baccalaureate institutions
transfer = both[col_match, on = "user_id"] %>%
  # Remove users who listed the same baccalaureate institution twice
  distinct(user_id,alt_name)

# Create list of users with multiple users
transfer = transfer[, .(count = .N), by = user_id] %>%
  table.express::filter(count > 1)

# Remove extra column
transfer = transfer[,c("count"):=NULL]

transfer = intersect(both$user_id,transfer$user_id)

# Remove redundant intermediate objects to save memory
rm(li_col_correct,li_hs_misclassified,li_unknown_col)

```



##    Combine Correct + Incorrect

```{r combine, echo=FALSE}

# Remove redundant intermediate objects to save memory
rm(ed_li,li_col,li_hs)

# Create unified list of users with bachelors degrees
#col = rbind(li_col_correct, li_hs_misclassified, li_unknown_col)

# Create unified list of users with high schools listed
#hs = rbind(li_hs_correct, li_col_misclassified, li_unknown_hs) 

# Remove redundant intermediate objects to save memory
rm(li_hs_correct,li_col_misclassified,li_unknown_hs)

# Extract user IDs for people listing baccalaureate institution on LI
col_users = col_match %>% table.express::select(user_id)

# Extract user IDs for people listing high school on LI
hs_users = hs_match %>% table.express::select(user_id)

# Create list of people listing both high school and baccalaureate institutions
# Wait on creating both until data extracted from position file
both = as.data.table(intersect(col_users$user_id,hs_users$user_id)) %>%
  setnames("V1","user_id")

# Find users with multiple baccalaureate institutions
transfer = both[col, on = "user_id"] %>%
  # Remove users who listed the same baccalaureate institution twice
  distinct(user_id,alt_name)

# Create list of users with multiple users
transfer = transfer[, .(count = .N), by = user_id] %>%
  table.express::filter(count > 1)

# Remove extra column
transfer = transfer[,c("count"):=NULL]

# Remove redundant intermediate objects to save memory
rm(li_col_correct,li_hs_misclassified,li_unknown_col)

```