---
title: "04_ed_pos_merge"
author: "Nicholas Martens"
date: "2023-06-10"
output: html_document
---

## Setup

Directories and filenames that change with machine
```{r directory, include=FALSE}
directory = "/Users/nickmartens/Dropbox (University of Michigan)/Linkedin"
posfilename = "cleaned_pos_educ_STATES.csv"
```

Import necessary packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(tidyverse)
```

##    Import Position File
fread is faster and more effective for large .csv files
```{r pos import, include=FALSE}

pos = fread(file.path(directory,"Data",posfilename))

```

##    Trim Position File
Remove extra columns
Compute number of unique users represented in file with pos_keys
```{r pos trim, include=FALSE}
pos_keys = pos %>%
  group_by(user_id) %>%
  group_keys() %>%
  distinct()

position = pos %>%
  filter(user_id %in% both$user_id) %>%
  filter(country == "United States") %>%
  # For now we will just filter out 'empty'
  # It appears CBSA could be imputed for some of them based on the LI raw geography
  filter(state != "empty")

position_trimmed = position %>%
  select(-c(educ_startdate:n))
```


##    Filtering to Include HS + College

```{r filter, include=FALSE}
# We need to calculate graduation year 
both_col = col %>%
  filter(user_id %in% both$user_id)
both_hs = hs %>%
  filter(user_id %in% both$user_id)

# Merging high school and college experiences into one file
merge_col_hs = both_col %>%
  left_join(both_hs, by = "user_id", multiple = "all") %>%
  select(c(user_id, university_name.x, educ_startdate.x, educ_enddate.x, col_state,
           field.x, cbsa_code.x, university_name.y, educ_enddate.y, cbsa_code.y))
```

##    Linking HS + College to User

```{r merge hs col, include=FALSE}
# Convert date columns into years (remove months and days)
merge_col_hs_date = merge_col_hs %>%
  filter(educ_startdate.x != "\\N" | educ_enddate.x != "\\N" | educ_enddate.y != "\\N") %>%
  mutate(col_start = str_sub(educ_startdate.x, start = 1, end = 4),
         col_end = str_sub(educ_enddate.x, start = 1, end = 4),
         hs_end = str_sub(educ_enddate.y, start = 1, end = 4))

merge_col_hs_date$col_start = as.numeric(merge_col_hs_date$col_start)
merge_col_hs_date$col_end = as.numeric(merge_col_hs_date$col_end)
merge_col_hs_date$hs_end = as.numeric(merge_col_hs_date$hs_end)
```

##    Calculating Birth Year

```{r birth year, include=FALSE}
# Calculating birth date based on high school graduation if available, 
# then college start date, and finally college graduation if the first two aren't available
birth = merge_col_hs_date %>%
  mutate(birth1 = ifelse(is.na(hs_end)==FALSE, hs_end - 18,0),
         birth2 = ifelse(is.na(col_start)==FALSE, col_start - 18,0),
         birth3 = ifelse(is.na(col_end)==FALSE, col_end - 22,0)) %>%
  mutate(birth = ifelse(birth1 > 0, birth1, ifelse(birth2 > 0, birth2, birth3))) %>%
  select(-c(birth1,birth2,birth3)) %>%
  # Use estimated birth years to fill in missing graduation or start dates
  mutate(col_start = ifelse(is.na(col_start)==FALSE, col_start, birth + 18),
         col_end = ifelse(is.na(col_end)==FALSE, col_end, birth + 18),
         hs_end = ifelse(is.na(hs_end)==FALSE, hs_end, birth + 18))
```

##    Filtering to Millennial Cohorts

```{r millennial, include=FALSE}
# Filter birth cohorts outside of current focus
birth_trimmed = birth %>%
  filter(birth > 1979 & birth < 2001)
```

##    Checking for Position in nth Year
Creates binary variable with a 1 if LI profile includes a position within nth year
```{r return binary, include=FALSE}
# Merge education and position files
birth_position = birth_trimmed %>%
  left_join(position_trimmed, by = "user_id", multiple = "all") %>%
  mutate(startdate = as.character(startdate),
         enddate = as.character(enddate))

# Compute commuting zone 1:10 years after graduation, if possible
bp_datemod = birth_position %>%
  mutate(post_1 = col_end + 1,
         post_2 = col_end + 2,
         post_3 = col_end + 3,
         post_4 = col_end + 4,
         post_5 = col_end + 5,
         post_6 = col_end + 6,
         post_7 = col_end + 7,
         post_8 = col_end + 8,
         post_9 = col_end + 9,
         post_10 = col_end + 10,) %>%
  separate(startdate, into = c("st_y","st_m","st_d"), sep = "-") %>%
  mutate(enddate = ifelse(is.na(enddate)==TRUE,"2023-05-01",enddate)) %>%
  separate(enddate, into = c("en_y","en_m","en_d"), sep = "-") %>%
  mutate(st_y = as.numeric(st_y),
         st_m = as.numeric(st_m),
         st_d = as.numeric(st_d),
         en_y = as.numeric(en_y),
         en_m = as.numeric(en_m),
         en_d = as.numeric(en_d))

# The tests used to determine if a person worked a given job n years after graduation
bp_datemod_cbsa = bp_datemod %>%
  group_by(user_id) %>%
  # A little bit of string cleaning for MSA name
  # Separates state and city for hyphenated metros (Philly) and two-word cities (El Paso)
  mutate(cbsa_clean = str_replace_all(msa, " MSA",""),
         cbsa_city = str_extract(cbsa_clean,'(^.{1,}-(?=([A-Z][a-z].*)))|(^.{1,} (?=([A-Z][A-Z].*)))'),
         cbsa_city = str_replace_all(cbsa_city, '-'," ")) %>%
  separate(cbsa_clean, into = c(NA,"cbsa_state"), sep = (' (?=([A-Z][A-Z].*))')) %>%
  mutate(cbsa_city = str_replace_all(cbsa_city,"Austin","Austin Round Rock"),
         cbsa_city = str_replace_all(cbsa_city,"Baltimore","Baltimore Columbia"),
         cbsa_city = str_replace_all(cbsa_city,"Blacksburg Christiansburg","Blacksburg"),
         cbsa_city = str_replace_all(cbsa_city,"Bremerton","Bremerton Silverdale"),
         cbsa_city = str_replace_all(cbsa_city,"Charlotte Gastonia","Charlotte Concord"),
         cbsa_city = str_replace_all(cbsa_city,"Cleveland Elyria","Cleveland"),
         cbsa_city = str_replace_all(cbsa_city,"Corvalis","Corvallis"),
         cbsa_city = str_replace_all(cbsa_city,"Fort Walton Beach Crestview","Crestview Fort Walton Beach"),
         cbsa_city = str_replace_all(cbsa_city,"Denver","Denver Aurora"),
         cbsa_city = str_replace_all(cbsa_city,"Greenville Mauldin","Greenville"),
         cbsa_city = str_replace_all(cbsa_city,"Houma Bayou Cane","Houma"),
         cbsa_city = str_replace_all(cbsa_city,"Houston Sugar Land","Houston The Woodlands"),
         cbsa_city = str_replace_all(cbsa_city,"Indianapolis","Indianapolis Carmel"),
         cbsa_city = str_replace_all(cbsa_city,"Kennewick Richland","Kennewick"),
         cbsa_city = str_replace_all(cbsa_city,"Killeen Temple","Killeen"),
         cbsa_city = str_replace_all(cbsa_city,"Kingsport Bristol","Kingsport"),
         cbsa_city = str_replace_all(cbsa_city,"Las Vegas","Las Vegas Henderson"),
         cbsa_city = str_replace_all(cbsa_city,"Milwaukee Waukesha","Milwaukee"),
         cbsa_city = str_replace_all(cbsa_city,"New Orleans Metairie","New Orleans"),
         cbsa_city = str_replace_all(cbsa_city,"New York Northern New Jersey","New York Newark"),
         cbsa_city = str_replace_all(cbsa_city,"Sarasota Bradenton","North Port Sarasota"),
         cbsa_city = str_replace_all(cbsa_city,"Olympia","Olympia Lacey"),
         cbsa_city = str_replace_all(cbsa_city,"Orlando","Orlando Kissimmee"),
         cbsa_city = str_replace_all(cbsa_city,"Parkersburg Marietta","Parkersburg"),
         cbsa_city = str_replace_all(cbsa_city,"Portland South Portland","Portland"),
         cbsa_city = str_replace_all(cbsa_city,"Prescott","Prescott Valley"),
         cbsa_city = str_replace_all(cbsa_city,"Providence New Bedford","Providence"),
         cbsa_city = str_replace_all(cbsa_city,"Sacramento Arden Arcade","Sacramento Roseville"),
         cbsa_city = str_replace_all(cbsa_city,"San Diego Carlsbad","San Diego Chula Vista"),
         cbsa_city = str_replace_all(cbsa_city,"Santa Barbara Santa Maria","Santa Maria"),
 #        cbsa_city = str_replace_all(cbsa_city,"Texarkana TX","Texarkana"),
         cbsa_city = str_replace_all(cbsa_city,"Honolulu","Urban Honolulu"),
         cbsa_city = str_replace_all(cbsa_city,"Vineland Millville","Vineland"),
         cbsa_city = str_replace_all(cbsa_city,"Danville","VA NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"Anderson","IN NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"Sandusky","OH NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"Palm Coast","FL NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"Anderson","SC NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"Holland","MI NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"Norwich","CT NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"New Haven","CT NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"Hartford West Hartford","CT NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"Bridgeport Stamford","CT NONMETROPOLITAN"),
         cbsa_city = str_replace_all(cbsa_city,"DE NONMETROPOLITAN","Dover"),
#         cbsa_state = str_replace_all(cbsa_state,"AR-MO","AR"),
#         cbsa_state = str_replace_all(cbsa_state,"^MA","MA-CT"),
         cbsa_city = str_replace_all(cbsa_city,"Nashville Davidson Murfreesboro ","Nashville Davidson  Murfreesboro"),
         cbsa_city = str_replace_all(cbsa_city,"Pascagoula","Gulfport"),
         cbsa_state = str_replace_all(cbsa_state,"TN-AR-MS","TN-MS-AR"),
#         cbsa_state = str_replace_all(cbsa_state,"VA","NONMETROPOLITAN"),
#         cbsa_state = str_replace_all(cbsa_state,"IN","NONMETROPOLITAN"),
#         cbsa_state = str_replace_all(cbsa_state,"OH","NONMETROPOLITAN"),
#         cbsa_State = str_replace_all(cbsa_state,"FL","NONMETROPOLITAN"),
#         cbsa_state = str_replace_all(cbsa_state,"SC","NONMETROPOLITAN"),
#         cbsa_state = str_replace_all(cbsa_state,"MI","NONMETROPOLITAN"),
#         cbsa_state = str_replace_all(cbsa_state,"^CT","NONMETROPOLITAN"),
#         cbsa_state = str_replace_all(cbsa_state,"NONMETROPOLITAN","DE")
  ) %>%
  left_join(name_match, by = c("cbsa_state","cbsa_city")) %>%
 # rename(cbsa_name = msa_clean) %>%
  mutate(inside_1 = ifelse((st_y < post_1 & post_1 < en_y) | 
                             (st_y < post_1 & post_1 == en_y) |
                             (st_y == post_1 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0),
         inside_2 = ifelse((st_y < post_2 & post_2 < en_y) | 
                             (st_y < post_2 & post_2 == en_y) |
                             (st_y == post_2 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0),
         inside_3 = ifelse((st_y < post_3 & post_3 < en_y) | 
                             (st_y < post_3 & post_3 == en_y) |
                             (st_y == post_3 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0),
         inside_4 = ifelse((st_y < post_4 & post_4 < en_y) | 
                             (st_y < post_4 & post_4 == en_y) |
                             (st_y == post_4 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0),
         inside_5 = ifelse((st_y < post_5 & post_5 < en_y) | 
                             (st_y < post_5 & post_5 == en_y) |
                             (st_y == post_5 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0),
         inside_6 = ifelse((st_y < post_6 & post_6 < en_y) | 
                             (st_y < post_6 & post_6 == en_y) |
                             (st_y == post_6 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0),
         inside_7 = ifelse((st_y < post_7 & post_7 < en_y) | 
                             (st_y < post_7 & post_7 == en_y) |
                             (st_y == post_7 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0),
         inside_8 = ifelse((st_y < post_8 & post_8 < en_y) | 
                             (st_y < post_8 & post_8 == en_y) |
                             (st_y == post_8 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0),
         inside_9 = ifelse((st_y < post_9 & post_9 < en_y) | 
                             (st_y < post_9 & post_9 == en_y) |
                             (st_y == post_9 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0),
         inside_10 = ifelse((st_y < post_10 & post_10 < en_y) | 
                             (st_y < post_10 & post_10 == en_y) |
                             (st_y == post_10 & st_m < 4 & (en_y > st_y | en_m > 4)),1,0))
         

# Manual repair of CBSA merge problems
cbsa_merge_problems = bp_datemod_cbsa %>%
  filter(is.na(cbsa_code)==TRUE) %>%
  group_by(cbsa_city,cbsa_state) %>%
  summarize(n = n()) %>%
  arrange(n)
```

##    Link Positions to Geographies
If LI profile includes during 
```{r pos geo, include=FALSE}
# Clean file such that a single row contains:
# College name, hs name, 
pos_cbsa = bp_datemod_cbsa %>%
  select(c(user_id,cbsa_code,inside_1:inside_10)) %>%
  mutate(cbsa_1 = ifelse(inside_1==1,cbsa_code,NA),
         cbsa_2 = ifelse(inside_2==1,cbsa_code,NA),
         cbsa_3 = ifelse(inside_3==1,cbsa_code,NA),
         cbsa_4 = ifelse(inside_4==1,cbsa_code,NA),
         cbsa_5 = ifelse(inside_5==1,cbsa_code,NA),
         cbsa_6 = ifelse(inside_6==1,cbsa_code,NA),
         cbsa_7 = ifelse(inside_7==1,cbsa_code,NA),
         cbsa_8 = ifelse(inside_8==1,cbsa_code,NA),
         cbsa_9 = ifelse(inside_9==1,cbsa_code,NA),
         cbsa_10 = ifelse(inside_10==1,cbsa_code,NA)
         ) %>%
  select(-c(inside_1:inside_10)) %>%
  group_by(user_id) %>%
  summarize(cbsa_1 = na.omit(cbsa_1)[1],
            cbsa_2 = na.omit(cbsa_2)[1],
            cbsa_3 = na.omit(cbsa_3)[1],
            cbsa_4 = na.omit(cbsa_4)[1],
            cbsa_5 = na.omit(cbsa_5)[1],
            cbsa_6 = na.omit(cbsa_6)[1],
            cbsa_7 = na.omit(cbsa_7)[1],
            cbsa_8 = na.omit(cbsa_8)[1],
            cbsa_9 = na.omit(cbsa_9)[1],
            cbsa_10 = na.omit(cbsa_9)[1])

# Linking post-graduation CBSA data with postsecondary and high school
unified = pos_cbsa %>%
  left_join(birth, by = "user_id") %>%
  select(-c(educ_startdate.x,educ_enddate.x,educ_enddate.y,cbsa_code.y)) %>%
  rename(col_name = university_name.x,
         hs_name = university_name.y,
         major = field.x, 
         col_cbsa = cbsa_code.x) %>%
  group_by(user_id) %>%
  # Remove observations with no work history
  mutate(work_exists = ifelse((is.na(cbsa_1)==FALSE | is.na(cbsa_2)==FALSE |
                              is.na(cbsa_3)==FALSE | is.na(cbsa_4)==FALSE |
                              is.na(cbsa_5)==FALSE | is.na(cbsa_6)==FALSE |
                              is.na(cbsa_7)==FALSE | is.na(cbsa_8)==FALSE |
                              is.na(cbsa_9)==FALSE | is.na(cbsa_9)==FALSE |
                              is.na(cbsa_10)==FALSE),1,0)) %>%
  filter(work_exists == 1)
```

##    Original and Unoriginal Schools
Delineating between high schools with a unique name 
and those sharing a name with some other institution in the US
```{r original hs, include=FALSE}
# Removing extraneous columns from all_hs
clean_hs = all_hs %>%
  mutate(alt_name = str_replace_all(alt_name, "high$","high school")) %>%
  group_by(clean_name,cbsa_code) %>%
  distinct() %>%
  select(c(STATE,cbsa_code,clean_name))

# Schools located in a single CBSA
original_name = clean_hs %>%
  group_by(clean_name) %>%
  summarize(n = n()) %>%
  filter(n == 1)

# Schools located in multiple CBSAs
unoriginal_name = clean_hs %>%
  group_by(clean_name) %>%
  summarize(n = n()) %>%
  filter(n > 1)
```

##    Matching High School to Geography

```{r hs heuristic, include=FALSE}
# Constructing a sensitive high school imputation method
better_hs = unified %>%
  # Standard string cleaning to ease matching
  mutate(alt_name = str_to_lower(hs_name),
         alt_name = str_trim(alt_name),
         alt_name = str_replace_all(alt_name, "-"," "),
         alt_name = str_replace_all(alt_name, "—"," "),
         alt_name = str_replace_all(alt_name, ","," "),
         alt_name = str_replace_all(alt_name, "main campus",""),
         alt_name = str_replace_all(alt_name, "high$","high school"),
         alt_name = str_trim(alt_name)) %>%
  mutate(clean_name = alt_name,
         unoriginal = ifelse(clean_name %in% unoriginal_name$clean_name,1,0))

# High schools with unoriginal names
# Matching won't be as straightforward
better_hs_unoriginal = better_hs %>%
  filter(unoriginal == 1) %>%
  left_join(clean_hs, by = "clean_name") %>%
  select(-c(alt_name,unoriginal,work_exists)) %>%
  # First check if any of the high schools are in the post-graduation CBSA 
  mutate(same_as_post = ifelse((str_detect(cbsa_1,cbsa_code)==TRUE | 
                                 str_detect(cbsa_2,cbsa_code)==TRUE |
                                 str_detect(cbsa_3,cbsa_code)==TRUE | 
                                 str_detect(cbsa_4,cbsa_code)==TRUE |
                                 str_detect(cbsa_5,cbsa_code)==TRUE | 
                                 str_detect(cbsa_6,cbsa_code)==TRUE |
                                 str_detect(cbsa_7,cbsa_code)==TRUE | 
                                 str_detect(cbsa_8,cbsa_code)==TRUE |
                                 str_detect(cbsa_9,cbsa_code)==TRUE | 
                                 str_detect(cbsa_10,cbsa_code)==TRUE),1,NA)) %>%
  mutate(same_state_col = ifelse(col_state == STATE,1,0))

# Isolate the simplest test case: high school with unoriginal name in post-grad CBSA
unoriginal_same_as_post = better_hs_unoriginal %>%
  filter(is.na(same_as_post)==FALSE) %>%
  select(-c(same_as_post,same_state_col))

# Isolate people who attended college in a state that contains an unoriginal hs
unoriginal_same_state_col = better_hs_unoriginal %>%
  filter(user_id %nin% unoriginal_same_as_post$user_id) %>%
  filter(is.na(same_as_post)==TRUE) %>%
  filter(same_state_col == 1) %>%
  select(-c(same_as_post,same_state_col))
  
# Isolate people who live in the same state where they went to high school
# First pull a list of CBSAs by state
cbsa_state = big_chungus %>%
  select('Official Name State',cbsa_code) %>%
  rename(STATE = 'Official Name State') %>%
  distinct()

# If somebody with an unoriginal high school doesn't fall into the previous categories,
# same_state_as_post checks if their high school is in the same state as post-grad work
same_state = better_hs_unoriginal %>%
  filter(user_id %nin% unoriginal_same_as_post$user_id) %>%
  filter(user_id %nin% unoriginal_same_state_col$user_id) %>%
  filter(is.na(same_as_post)==TRUE) %>%
  filter(same_state_col == 0) %>%
  left_join(cbsa_state, by = "STATE") %>%
  mutate(same_state_as_post = ifelse((str_detect(cbsa_1,cbsa_code.y)==TRUE | 
                                         str_detect(cbsa_2,cbsa_code.y)==TRUE |
                                         str_detect(cbsa_3,cbsa_code.y)==TRUE | 
                                         str_detect(cbsa_4,cbsa_code.y)==TRUE |
                                         str_detect(cbsa_5,cbsa_code.y)==TRUE | 
                                         str_detect(cbsa_6,cbsa_code.y)==TRUE |
                                         str_detect(cbsa_7,cbsa_code.y)==TRUE | 
                                         str_detect(cbsa_8,cbsa_code.y)==TRUE |
                                         str_detect(cbsa_9,cbsa_code.y)==TRUE | 
                                         str_detect(cbsa_10,cbsa_code.y)==TRUE),1,NA))

# Isolate people who lived in the same state as their high school
# For metros across multiple states the MSA will be included as a possibility
# for every constitutive state
unoriginal_same_state_post = same_state %>%
  filter(is.na(same_state_as_post)==FALSE) %>%
  select(-c(same_as_post:same_state_as_post)) %>%
  rename(cbsa_code = cbsa_code.x)

# The remaining don't live in the same state as their high school or college
# For now we will just randomly select one of the possible high schools
# in the future I might adjust the code so choose the closest possible high school
unoriginal_last_resort = same_state %>%
  filter(is.na(same_state_as_post)==TRUE) %>%
  filter(user_id %nin% unoriginal_same_state_post$user_id) %>%
  select(-c(same_as_post:same_state_as_post)) %>%
  rename(cbsa_code = cbsa_code.x) %>%
  distinct() %>%
  group_by(user_id) %>%
  slice_sample(n = 1)

# High schools with unique names
# Matching should be straightforward
better_hs_original = better_hs %>%
  filter(unoriginal == 0) %>%
  left_join(clean_hs, by = "clean_name") %>%
  select(-c(alt_name,unoriginal,work_exists))
```

##    Combine High School Merges

```{r combine hs, include=FALSE}
# Combine the correct data and filter so that only most recent bachelor's institution listed
completed = rbind(better_hs_original,
                  unoriginal_same_as_post,
                  unoriginal_same_state_col,
                  unoriginal_same_state_post,
                  unoriginal_last_resort) %>%
  arrange(-col_end) %>%
  slice_max(col_end, n = 1)

completed_col = completed %>%
  select(user_id,col_name)
```

##    Create Outputs

```{r output, include=FALSE}
# Pull institutional characteristics 
completed_tiered = completed %>%
  mutate(alt_name = str_to_lower(col_name),
         alt_name = str_trim(alt_name),
         alt_name = str_replace_all(alt_name, "-"," "),
         alt_name = str_replace_all(alt_name, "—"," "),
         alt_name = str_replace_all(alt_name, ","," "),
         alt_name = str_replace_all(alt_name, "main campus",""),
         alt_name = str_replace_all(alt_name, " at "," "),
         alt_name = str_replace_all(alt_name, "a&m","agricultural and mechanical"),
         alt_name = str_replace_all(alt_name, "a & m","agricultural and mechanical"),
         alt_name = str_trim(alt_name),
         alt_name = str_squish(alt_name)) %>%
  left_join(all_col, by = c("col_state","alt_name")) %>%
  # For now just filter out the ~1500 with no tier
  filter(is.na(barrons)==FALSE) %>%
  # Remove unnecessary columns before advancing to regression analysis
  rename(hs_cbsa = cbsa_code.x,
         hs_state = STATE,
         hs_fips = FIPS) %>%
  relocate(c("hs_state","hs_fips","hs_cbsa"), .before = "col_start") %>%
  select(-c(alt_name,cbsa_code.y,clean_name,INSTNM,UNITID,IALIAS:ZIP,degree))

completed_tiered_problems = completed_tiered %>%
  filter(is.na(barrons)==TRUE) %>%
  group_by(col_name) %>%
  summarize(n = n()) %>%
  arrange(-n)
```
