---
title: "06_regression_aug"
author: "Nicholas Martens"
date: "2024-09-04"
output: html_document
---

##    Import necessary packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(texreg)
library(tidyverse)
library(readxl)
library(table.express)
library(data.table)

options(digits = 1)
```

##    Setup
Directories and filenames that change with machine
```{r directory, include=FALSE}
#directory = "/nfs/turbo/lsa-areynoso"
directory = "/Volumes/lsa-areynoso"

geos = c("cbsa","state")
#geos = c("state")
#avgs = c(7,5,3,1)
avgs = c(7)
norm = c("","_ptile")
stage = c("_shock","_growth")
shock_lbl = c("1-Year Shock",
              "3-Year Average",
              "5-Year Average",
              "7-Year Average")
# Number of bins is flexible
num_bins = c(5,10,25)

```

##    Create Universal Label

```{r label}

# Function to generate variable labels for multiple prefixes
generate_labels <- function(var_prefixes, avgs, inst_groups) {
  labels_list <- lapply(var_prefixes, function(var_prefix) {
    labels <- paste0(var_prefix, "_", avgs, ":")
    do.call(paste0, expand.grid(labels, inst_groups))
  })
  unlist(labels_list)  # Flatten the list into a single vector
}

controls = c("in_stateIn-State",
             "non_traditionalTraditional",
             "transferTransfer")
control_lbl = c("College In State",
                "BA by Age 24",
                "Transfer Student")
inst_groups = c("inst_groupPrivate, For-Profit",
                "inst_groupPrivate, Non-Profit",
                "inst_groupRPU")
                #"inst_groupRPU, Less Selective",
                #"inst_groupRPU, More Selective")

# Create Universal Labels
output_instate = paste0(inst_groups, ":in_stateIn-State")
output_dist = paste0("dist", c("[0,50]", "(50,100]", "(100,150]", "(150,200]", 
                                "(200,250]", "(250,500]", "(500,1e+03]", "(1e+03,1e+04]"))

# Crete labor demand shock variables
hs_vars = paste0("hs",do.call(paste0, expand.grid(stage, norm, stringsAsFactors = FALSE)))
col_vars = paste0("col",do.call(paste0, expand.grid(stage, norm, stringsAsFactors = FALSE)))

# Generate labels for all variable types
hs_output_vars = generate_labels(hs_vars, avgs, inst_groups)
col_output_vars = generate_labels(col_vars, avgs, inst_groups)

# Create labels for hs_shock * dist (using the original prefix)
output_distance = paste0(rep(paste0(rep(hs_vars,each = length(avgs)),"_",avgs,":"),each = length(output_dist)),output_dist) 

# Combine all interaction labels
interactions = c(output_instate, hs_output_vars, col_output_vars, output_distance)

# Remove variable names through flexible regex
basic_pattern = "[^0-9]*[0-9]+"
hs_pattern <- paste0("hs",basic_pattern)
col_pattern <- paste0("col",basic_pattern)


# Create clean labels for final table
interactions_lbl = c(paste0(str_replace_all(inst_groups, "inst_group", ""), " $times$ In-State"),
                     paste0(str_replace_all(hs_output_vars, paste0(hs_pattern,"(:inst_group)?"), ""), " $times$ HS LD Shock"),
                     paste0(str_replace_all(col_output_vars, paste0(col_pattern,"(:inst_group)?"), ""), " $times$ College LD Shock"),
                     paste0(str_replace_all(output_distance, paste0(hs_pattern,"(:dist)?"), ""), " $times$ HS LD Shock"))

# Bind regression outputs with cleaned names
label = data.frame(output_names = c(do.call(paste, expand.grid(hs_vars, avgs, stringsAsFactors = FALSE, sep = "_")),
                                    do.call(paste, expand.grid(col_vars, avgs, stringsAsFactors = FALSE, sep = "_")),
                                    inst_groups,
                                    output_dist,
                                    interactions,
                                    controls),
                   label_names = c(rep(times = length(avgs) * length(hs_vars),"HS LD Shock"),
                                   rep(times = length(avgs) * length(col_vars),"College LD Shock"),
                                   str_replace_all(inst_groups,"inst_group",""),
                                   str_replace_all(output_dist,"dist",""),
                                   interactions_lbl,
                                   control_lbl))

nestedlist <- split(label$label_names, factor(label$output_names, 
                                               levels = unique(label$output_names)))

```

##    Import Microdata
Avoid rerunning previous eight steps and saving ~6 hours
```{r import, include=FALSE}
if(directory == "/nfs/turbo/lsa-areynoso")
{
  microdata <- fread(file.path(directory,"Data/06/microdata.csv"))
} else {
  microdata <- fread(file.path(directory,"Data/06/microdata_sample.csv"))
}
microdata <- microdata[,V1 := NULL]

regression <- microdata[, !duplicated(names(microdata)), with = FALSE] %>%
  # Create variable for non-traditional students
  table.express::mutate(non_traditional = ifelse(col_end - birth > 24,
                                                 "Non-Traditional",
                                                 "Traditional"),
                        # Recode variable for transfer students to ease interpretation
                        transfer = ifelse(transfer == "0",
                                          "Non-Transfer",
                                          "Transfer"),
                        in_state = ifelse(col_state == hs_state, "In-State","Out-of-State"),
                        col_end = as.factor(col_end),
                        #in_state = ifelse(hs_state == col_state,"In-State","Out-of-State"),
                        binary_dist = case_when(dist %in% c("[0,50]","(50,100]","(100,150]","(150,200]","(200,250]") ~ "Near",
                                               TRUE ~ "Far"
                                               ),
                        col_in_not_hs_cbsa = ifelse(hs_cbsa_code == col_cbsa_code,0,1),
                        soc_2 = substr(soc_code_mode, start = 1, stop = 2),
                        soc_3 = substr(soc_code_mode, start = 1, stop = 4)) %>%
  table.express::filter(is.na(dist)==FALSE) %>%
  # For now just filter out College Station
  table.express::filter(hs_name != "College Station High School")
dist_bins = levels(regression$dist)[-1]

# Select only the 'unitid' and 'inst_group' columns from institutional_characteristics
inst_group <- fread(file.path(directory,"Data/06","institutional_characteristics.csv")) %>%
  select(unitid,inst_group)#institutional_characteristics[,c("unitid", "inst_group")]

# Merge the two data.tables on 'unitid'
regression <- merge(regression, inst_group, by.x = "col_unitid",by.y = "unitid",all.x = TRUE)
regression[, inst_group := factor(inst_group)]
regression[, in_state := factor(in_state)]
regression[, inst_group := relevel(inst_group, ref = "PF")]
regression[, in_state := relevel(regression$in_state, ref = "Out-of-State")]
regression[, instate := ifelse(hs_state==col_state,1,0)]

# Filter instititons without a unitid (mostly community college)
regression <- regression[!is.na(inst_group) & inst_group != "Private, For-Profit"]


# Do people who finish college after age 24 have different mobility patterns than
# those who finish before age 24. Probably use, profile of institutions varies
na_count = regression[, lapply(.SD, function(x) sum(is.na(x)))]  

missing_inst_group = regression[is.na(inst_group), .N, by = .(col_unitid,col_name)]
#all_binary_final = read.csv(file.path(directory,"Data/regression_data.csv"))
#actual_cohort = read.csv(file.path(directory,"Data/actual_cohort.csv"))

```

##    Stocks of College Graduates by Labor Market

```{r spat}

# Conditional on graduating college, what are the most common alma maters in every
# local labor market
local_stocks <- regression[,.N,by=.(col_unitid,cbsa_mode,state_mode)]
local_stocks[,shr_col := N/sum(N),by=.(cbsa_mode,state_mode)]
local_stocks <- merge(local_stocks,
                      cbsa_li_crosswalk %>% mutate(cbsa_code = as.integer(cbsa_code)),
                      by.x=c("cbsa_mode","state_mode"),
                      by.y=c("cbsa_code","cbsa_state"),all.x=TRUE) %>%
  merge(ope_unit_crosswalk %>%
          select(IPEDSMatch,PEPSSchname) %>%
          distinct() %>%
          mutate(col_unitid = as.integer(IPEDSMatch)) %>%
          select(-IPEDSMatch),
        by=c("col_unitid"))
  
  
# Export
write.csv(local_stocks %>% 
            table.express::filter(!is.na(cbsa_core)) %>%
            table.express::filter(N > 9),
          file.path(directory,"Data/05","local_stocks.csv"))

state_stocks <- local_stocks[,.(N = sum(N)),by=.(state_mode,col_unitid,PEPSSchname)]
state_stocks[,shr_col := N/sum(N), by=.(state_mode)]
write.csv(state_stocks %>% 
            table.express::filter(N > 9),
          file.path(directory,"Data/05","state_stocks.csv"))

##  Compute share of LI users attending institution
li_inst <- microdata[, .N, by = .(col_unitid)]
li_inst[, li_shr := N/sum(N)]
write.csv(li_inst,file.path(directory,"Data/05","li_inst.csv"))

# Select only the 'unitid' and 'inst_group' columns from institutional_characteristics
inst_group = fread(file.path(directory,"Data/06","institutional_characteristics.csv")) %>%
  select(unitid,inst_group)
# Intermediate object used to create cross-sectional measure of return by inst_group and occupational prestige
occp_inst_group <- merge(microdata, inst_group, by.x = "col_unitid",by.y = "unitid",all.x = TRUE) %>%
  table.express::filter(!is.na(prestige_bin) & !is.na(inst_group)) %>%
  table.express::filter(inst_group != "Private, For-Profit") %>%
  table.express::mutate(col_end_bin = cut(col_end,
                        breaks = c(2022,2017,2012,2007,1982),
                        labels = c("0-5","6-10","11-15","15+"),
                        right = TRUE,
                        ordered = TRUE
                        )) %>%
  table.express::filter(!is.na(col_end_bin))
occp_inst_group_counts <- occp_inst_group[, .N, by = .(prestige_bin,inst_group,col_end_bin)]
write.csv(occp_inst_group_counts,file.path(directory,"Data/06","occp_inst_group.csv"))

```

##    Origin-Destination Plot Data

```{r net}

# Compute in-state share by institution
instate_li = regression[col_end %in% c(2000:2022),shr_instate_li := mean(instate), by = col_unitid]
instate_li <- unique(instate_li[!is.na(col_unitid) & !is.na(shr_instate_li), .(col_unitid, shr_instate_li)])
write.csv(instate_li,file.path(directory,"Data/07","instate_li.csv"))

regression_od <- regression[!is.na(cbsa_mode) & !is.na(hs_cbsa) & col_end %in% c(2010:2018)]

# Count observations by where they went to high school
origin_cbsa <- regression_od[,.(origin = .N),by=.(hs_cbsa,col_unitid)]
# Count observations by where they lived after college
destination_cbsa <- regression_od[,.(destination = .N),by=.(cbsa_mode,col_unitid)]
destination_cbsa[,li_total_college := sum(destination),by=.(col_unitid)]

#destination_cbsa[,total_destination := sum(destination),by=.(cbsa_mode)]
write.csv(destination_cbsa,file.path(directory,"Data/07","destination_cbsa.csv"))

# Merge orign and destination data to compute net flows by labor market
od_cbsa <- merge(origin_cbsa,destination_cbsa,by.x=c("hs_cbsa","col_unitid"),by.y=c("cbsa_mode","col_unitid"),all=TRUE) %>%
  table.express::mutate(destination = fifelse(is.na(destination)==TRUE,0,destination),
                        origin = fifelse(is.na(origin)==TRUE,0,origin)) %>%
  merge(inst_group,
        by.x = c("col_unitid"),by.y="unitid") %>%
  rename(cbsa = hs_cbsa)

net_cbsa <- od_cbsa[, .(origin = sum(origin),
            destination = sum(destination)),by=.(cbsa,inst_group)]
net_cbsa[,total_origin := sum(origin),by=.(cbsa)]
net_cbsa[,total_destination := sum(destination),by=.(cbsa)]
net_cbsa[,net := destination - origin]
net_cbsa[,net_norm := net/total_origin]
# Export file
write.csv(net_cbsa,file.path(directory,"Data/06","net_cbsa.csv"))

# Count observations by where they went to high school
origin_state <- regression_od[,.(origin = .N),by=.(hs_state,col_unitid)]
# Count observations by where they lived after college
destination_state <- regression_od[,.(destination = .N),by=.(state_mode,col_unitid)]
destination_state[,li_total_college := sum(destination),by=.(col_unitid)]
write.csv(destination_state,file.path(directory,"Data/07","destination_state.csv"))

# Merge orign and destination data to compute net flows by state
# Merge orign and destination data to compute net flows by labor market
od_state <- merge(origin_state,destination_state,by.x=c("hs_state","col_unitid"),by.y=c("state_mode","col_unitid"),all=TRUE) %>%
  table.express::mutate(destination = fifelse(is.na(destination)==TRUE,0,destination),
                        origin = fifelse(is.na(origin)==TRUE,0,origin)) %>%
  merge(inst_group,
        by.x = c("col_unitid"),by.y="unitid") %>%
  rename(state = hs_state)
net_state <- od_state[, .(origin = sum(origin),
            destination = sum(destination)),by=.(state,inst_group)]
net_state[,total_origin := sum(origin),by=.(state)]
net_state[,total_destination := sum(destination),by=.(state)]
net_state[,net := destination - origin]
net_state[,net_norm := net/total_origin]
# Export file
write.csv(net_state,file.path(directory,"Data/06","net_state.csv"))

# Measure levels of return for first figure 
return_levels_state <- regression[,.N,by=.(ever_leave_state_hs,same_state_hs,inst_group)]
write.csv(return_levels_state,file=file.path(directory,"Data/07","return_levels_state.csv"))
return_levels_cbsa <- regression[,.N,by=.(ever_leave_cbsa_hs,same_cbsa_hs,inst_group)]
write.csv(return_levels_cbsa,file=file.path(directory,"Data/07","return_levels_cbsa.csv"))

```

##    Local Ties

```{r inst-levels}
# Newcomers move away from their hometown at some point after college
newcomers_cbsa <- regression[ever_leave_cbsa_hs == 1 ,.N,by=.(hs_cbsa,col_cbsa_code,cbsa_mode)] %>%
  table.express::mutate(return_hs_col = case_when(hs_cbsa == cbsa_mode & col_cbsa_code == cbsa_mode ~ N,
                                          TRUE ~ 0),
                        return_hs_only = case_when(hs_cbsa == cbsa_mode & col_cbsa_code != cbsa_mode ~ N,
                                            TRUE ~ 0),
                        return_col_only = case_when(hs_cbsa != cbsa_mode & col_cbsa_code == cbsa_mode ~ N,
                                          TRUE ~ 0),
                        return_no_ties = case_when(hs_cbsa != cbsa_mode & col_cbsa_code != cbsa_mode ~ N,
                                            TRUE ~ 0))
local_ties_cbsa <- newcomers_cbsa[,.(return_hs_col = sum(return_hs_col),
                  return_hs_only = sum(return_hs_only),
                  return_col_only = sum(return_col_only),
                  no_ties = sum(return_no_ties)), by = .(cbsa_mode)]
# Natives might have gone away for college and returned
natives_cbsa <- regression[ever_leave_cbsa_hs == 0 ,.N,by=.(hs_cbsa,col_cbsa_code,cbsa_mode)] %>%
  table.express::mutate(stay_hs_col = case_when(hs_cbsa == cbsa_mode & col_cbsa_code == cbsa_mode ~ N,
                                          TRUE ~ 0),
                        stay_hs_only = case_when(hs_cbsa == cbsa_mode & col_cbsa_code != cbsa_mode ~ N,
                                            TRUE ~ 0))
# Merge local and natives into single object
# Cross-sectional measurement of where a given CBSA's residents are from 
local_ties_cbsa <- natives_cbsa[,.(stay_hs_col = sum(stay_hs_col),
                  stay_hs_only = sum(stay_hs_only)), by = .(cbsa_mode)] %>%
  merge(local_ties_cbsa, by = "cbsa_mode") %>%
  mutate(cbsa_code = str_pad(cbsa_mode,width=5,side="left",pad="0"))
local_ties_cbsa[,total := stay_hs_col + stay_hs_only + return_hs_col + return_hs_only + return_col_only + no_ties]
# Calculate normalized counts
count_cols <- names(local_ties_cbsa)[2:7]  # Select only the count columns
local_ties_cbsa[, (count_cols) := lapply(.SD, function(x) x / rowSums(.SD)), .SDcols = count_cols]
write.csv(local_ties_cbsa,file.path(directory,"Data/07","local_ties_cbsa.csv"))

# Newcomers move away from their hometown at some point after college
newcomers_state <- microdata[ever_leave_state_hs == 1 ,.N,by=.(hs_state,col_state,state_mode)] %>%
  table.express::mutate(return_hs_col = case_when(hs_state == state_mode & col_state == state_mode ~ N,
                                          TRUE ~ 0),
                        return_hs_only = case_when(hs_state == state_mode & col_state != state_mode ~ N,
                                            TRUE ~ 0),
                        return_col_only = case_when(hs_state != state_mode & col_state == state_mode ~ N,
                                          TRUE ~ 0),
                        return_no_ties = case_when(hs_state != state_mode & col_state != state_mode ~ N,
                                            TRUE ~ 0))
local_ties_state <- newcomers_state[,.(return_hs_col = sum(return_hs_col),
                  return_hs_only = sum(return_hs_only),
                  return_col_only = sum(return_col_only),
                  no_ties = sum(return_no_ties)), by = .(state_mode)]
# Natives might have gone away for college and returned
natives_state <- microdata[ever_leave_state_hs == 0 ,.N,by=.(hs_state,col_state,state_mode)] %>%
  table.express::mutate(stay_hs_col = case_when(hs_state == state_mode & col_state == state_mode ~ N,
                                          TRUE ~ 0),
                        stay_hs_only = case_when(hs_state == state_mode & col_state != state_mode ~ N,
                                            TRUE ~ 0))
# Merge local and natives into single object
# Cross-sectional measurement of where a given state's residents are from 
local_ties_state <- natives_state[,.(stay_hs_col = sum(stay_hs_col),
                  stay_hs_only = sum(stay_hs_only)), by = .(state_mode)] %>%
  merge(local_ties_state, by = "state_mode")
local_ties_state[,total := stay_hs_col + stay_hs_only + return_hs_col + return_hs_only + return_col_only + no_ties]
# Calculate normalized counts
count_cols <- names(local_ties_state)[2:7]  # Select only the count columns
local_ties_state[, (count_cols) := lapply(.SD, function(x) x / rowSums(.SD)), .SDcols = count_cols]
write.csv(local_ties_state,file.path(directory,"Data/07","local_ties_state.csv"))
```


##    Institutional Group Levels

```{r inst-levels}


# Order that institutions will appear in table
col_order = c("PF","RPU",
              "Private, Non-Profit")

# Calculating return rates by institutional groups 
inst_levels = regression %>%
  as.data.frame() %>%
  mutate(in_state = case_when(in_state == "In-State" ~ "is",
                              in_state == "Out-of-State" ~ "oos"),
         inst_group = factor(inst_group, ordered = TRUE,
                           levels = col_order)) %>%
  group_by(inst_group,in_state) %>%
  dplyr::summarise(same_cbsa_hs = sum(same_cbsa_hs),
                   same_state_hs = sum(same_state_hs),
                   n = n()) %>%
  mutate(same_cbsa_prop = round((same_cbsa_hs/n) * 100,1),
         same_state_prop = round((same_state_hs/n) * 100,1)) %>%
  select(-c(same_cbsa_hs,same_state_hs)) %>%
  pivot_wider(names_from = in_state,
              values_from = c(same_cbsa_prop,same_state_prop,n)) %>%
  mutate(cbsa_retention_gap = same_cbsa_prop_is - same_cbsa_prop_oos,
         state_retention_gap = same_state_prop_is - same_state_prop_oos) %>%
  relocate(c("n_is","n_oos"), .before = "same_cbsa_prop_is") %>%
  relocate("cbsa_retention_gap", .after = "same_cbsa_prop_oos") %>%
  # Convert institutional grouping back into character so it appears in table
  mutate(inst_group = as.character(inst_group))

# Splitting data into CBSA and state-level tables
inst_levels_cbsa = inst_levels %>%
  select(contains("cbsa"))
inst_levels_state = inst_levels %>%
  select(contains("state"))

write.csv(inst_levels,file.path(directory,"Data/07","inst_levels.csv"))
```



##    Characterizing Shocks

```{r shocks}

# Create relevant universes
# Ultimately, we are most concerned with people who actually left their hometowns at some point
regression_cbsa <- regression %>% table.express::filter(ever_leave_cbsa_hs == 1)
regression_state <- regression %>% table.express::filter(ever_leave_state_hs == 1)

# Select all columns measuring labor demand shocks or growth
iv_cols <- names(regression)[grepl("^(hs|col).*[1357]$", names(regression))]
  
# Measuring the incidence of shocks by CBSA, education group, and occupation  
for(b in num_bins)
{
  for(h in geos) 
  {
    data <- if(h == "cbsa") regression_cbsa else regression_state
    #data = regression_cbsa
    # Compute which CBSAs appear in each quantile
    for(col in iv_cols)
    {
      bin_shares = list()
      bin_col_name <- paste0(col,"_bin")
      data[, paste0(col, "_bin") := cut(get(col), 
                                             breaks = quantile(get(col), 
                                                               probs = seq(0,1,length.out = b+1),
                                                               na.rm=TRUE),
                                             labels = FALSE,
                                             include.lowest = TRUE)]
      bin_share <- data[, .(same_cbsa_hs = mean(same_cbsa_hs, na.rm = TRUE),
                                 same_state_hs = mean(same_state_hs, na.rm = TRUE),
                                 same_cbsa_col = mean(same_cbsa_col, na.rm = TRUE),
                                 same_state_col = mean(same_state_col, na.rm = TRUE)
                            ),
                                 by = bin_col_name]
      bin_share[, variable := col]
      setnames(bin_share, bin_col_name,"bin")
      bin_shares[[col]] <- bin_share
    }
    
    # Create df with return rates by quantile for 
    all_bin_shares <- rbindlist(bin_shares,use.names=TRUE,fill=TRUE) %>%
      mutate(geo = sub("_.*","",variable),
             avg = sub(".*_([0-9]+)$","\\1",variable),
             var = sub("(_[0-9]+)$","", sub("^[^_]+_","",variable)))
    # Export qunatile-level return statistics
    all_bin_filename = paste0("all_bin_shares_",h,"_",b,".csv")
    write.csv(all_bin_shares,file.path(directory,"Data/05",all_bin_filename))
    
    # Calculate which local labor markets contribute observations to each quantile
    bin_shares = data[, .(count = .N), by = .(hs_shock_7_bin,hs_cbsa,hs_state)] %>%
      table.express::filter(!is.na(hs_shock_7_bin))
    bin_shares[, shr_bin := count/sum(count), by = .(hs_shock_7_bin)]
    bin_shares[, shr_cbsa := count/sum(count), by = .(hs_cbsa,hs_state)]
    
    # Compute return statistics by high school labor market
    cbsa_returns <- data[, .(same_cbsa_hs = mean(same_cbsa_hs, na.rm = TRUE),
                                 same_state_hs = mean(same_state_hs, na.rm = TRUE),
                                 same_cbsa_col = mean(same_cbsa_col, na.rm = TRUE),
                                 same_state_col = mean(same_state_col, na.rm = TRUE)),
                                 by = .(hs_cbsa,hs_state,hs_shock_7_bin)] %>%
      table.express::filter(!is.na(hs_shock_7_bin))
    
    # Merge crosswalk from step 0 and returns by cbsa x shock_bin
    bin <- merge(bin_shares, cbsa_li_crosswalk %>% 
                  mutate(cbsa_code = as.integer(cbsa_code)), by.x = c("hs_cbsa","hs_state"),by.y = c("cbsa_code","cbsa_state"), all.x = TRUE) %>%
      merge(cbsa_returns,by = c("hs_cbsa","hs_state","hs_shock_7_bin"))
    # Export quantile-level return statistics
    bin_filename = paste0("bin_",h,"_",b,".csv")
    write.csv(bin,file.path(directory,"Data/05",bin_filename))
    
    # Compute totals by occupation x shock_bin x inst_group
    total_result <- data[, .N, by = .(hs_shock_7_bin, inst_group, soc_code_mode)]

    # Select the appropriate condition dynamically
    filter_condition <- if (h == "cbsa") "same_cbsa_hs == 1" else "same_state_hs == 1"
    # Compute both returners by occupation x shock_bin x inst_group
    returner_result <- data[eval(parse(text = filter_condition)), .N, by = .(hs_shock_7_bin, inst_group, soc_code_mode)]
    returner_result <- merge(returner_result,total_result,by=c("hs_shock_7_bin","inst_group","soc_code_mode"))
    names(returner_result) <- c("hs_shock_7_bin","inst_group","soc_code_mode","returners","total")
    assign(paste0("returners_", h,"_",b), returner_result)
     
    
    write.csv(get(paste0("returners_", h,"_",b)),file.path(directory,"Data/05",paste0("returners_", h,"_",b,".csv")))
  }
}

# Distribution of shocks over time
hs_shock_year_state = regression_state[, .(
  p01 = quantile(hs_shock_7,0.01,na.rm=TRUE),
  p05 = quantile(hs_shock_7,0.05,na.rm=TRUE),
  p25 = quantile(hs_shock_7,0.25,na.rm=TRUE),
  p50 = quantile(hs_shock_7,0.5,na.rm=TRUE),
  p75 = quantile(hs_shock_7,0.75,na.rm=TRUE),
  p95 = quantile(hs_shock_7,0.95,na.rm=TRUE),
  p99 = quantile(hs_shock_7,0.99,na.rm=TRUE),
  sd = sd(hs_shock_7,na.rm=TRUE),
  count = .N), by = col_end]
write.csv(hs_shock_year_state,file.path(directory,"Data/07",paste0("hs_shock_year_state.csv")))
hs_shock_year_cbsa = regression_cbsa[, .(
  p01 = quantile(hs_shock_7,0.01,na.rm=TRUE),
  p05 = quantile(hs_shock_7,0.05,na.rm=TRUE),
  p25 = quantile(hs_shock_7,0.25,na.rm=TRUE),
  p50 = quantile(hs_shock_7,0.5,na.rm=TRUE),
  p75 = quantile(hs_shock_7,0.75,na.rm=TRUE),
  p95 = quantile(hs_shock_7,0.95,na.rm=TRUE),
  p99 = quantile(hs_shock_7,0.99,na.rm=TRUE),
  sd = sd(hs_shock_7,na.rm=TRUE),
  count = .N), by = col_end]
write.csv(hs_shock_year_cbsa,file.path(directory,"Data/07",paste0("hs_shock_year_cbsa.csv")))

```

##    First Stage

```{r first-stage}
models = list()
geos = c("state","cbsa")
avgs = c(7)
norm = c("")
stage = c("_shock","_growth")

# Define each first-stage model with the respective year, formula, and variable names
models_info <- list(
  "7" = list(formula = hs_growth_7 ~ hs_shock_7 + col_shock_7 + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end + hs_state + prestige_bin, early_filt = 1982, late_filt = 2019)) #,
  #"5" = list(formula = hs_growth_5 ~ hs_shock_5 + col_shock_5 + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end + hs_state + prestige_bin, filter_year = 1980),
  #"3" = list(formula = hs_growth_3 ~ hs_shock_3 + col_shock_3 + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end + hs_state + prestige_bin, filter_year = 1978),
  #"1" = list(formula = hs_growth_1 ~ hs_shock_1 + col_shock_1 + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end + hs_state + prestige_bin, filter_year = 1976))

# Filter observations with no labor demand shock
regression <- regression[is.na(hs_shock_7)==FALSE & is.na(col_shock_7)==FALSE]

# Initialize list to store results
first_stage_stats <- list()
hs_stats <- list()
col_stats <- list()
# Loop through each model info, run the regression, and extract the relevant statistics
for(a in avgs) 
{
  model_info <- models_info[[as.character(a)]]
  early_filt <- model_info$early_filt
  late_filt <- model_info$late_filt
  regression_first_stage <- regression[!col_end %in% c(1975:early_filt)]
  regression_first_stage <- regression_first_stage[!col_end %in% c(late_filt:2023)]
  table(regression_first_stage$col_end)
  # Run traditional first-stage with endogenous variable on LHS
  hs_first <- lm(hs_growth_7 ~ hs_shock_7 + col_shock_7 + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end + hs_state + prestige_bin,data = regression_first_stage)
  col_first <- lm(col_growth_7 ~ hs_shock_7 + col_shock_7 + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end + hs_state + prestige_bin,data = regression_first_stage)
  
  # Extract fitted values
  regression_first_stage$hs_shock_7_fit = fitted(hs_first)
  regression_first_stage$col_shock_7_fit = fitted(col_first)
  
  # Re-run first-stage controling for the fitted values of the other shock
  hs_second <- lm(hs_growth_7 ~ hs_shock_7 + col_shock_7_fit + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end + hs_state + prestige_bin, data = regression_first_stage)
  col_second <- lm(col_growth_7 ~ hs_shock_7_fit + col_shock_7 + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end + hs_state + prestige_bin, data = regression_first_stage)

  # Extract F-statistic and R-squared, store in list
  hs_stats[[as.character(a)]] <- list(
    f_stat = summary(hs_second)$fstatistic[1],
    r_squared = summary(hs_second)$r.squared,
    intercept = summary(hs_second)$coefficients[1],
    intercept_se = summary(hs_second)$coefficients[201],
    slope = summary(hs_second)$coefficients[2],
    slope_se = summary(hs_second)$coefficients[202]
  )
  col_stats[[as.character(a)]] <- list(
    f_stat = summary(col_second)$fstatistic[1],
    r_squared = summary(col_second)$r.squared,
    intercept = summary(col_second)$coefficients[1],
    intercept_se = summary(col_second)$coefficients[201],
    slope = summary(col_second)$coefficients[3],
    slope_se = summary(col_second)$coefficients[203]
  )
}
```

##    Semi-Elasticity Regressions

```{r}

models <- list()
group_semi_elasticities <- data.frame()
# Prepare data to collect coefficients
coef_data <- data.frame()
norm = c("")

for(h in geos) 
{
    data <- if(h == "cbsa") regression_cbsa else regression_state
    data <- data[!col_end %in% c(2019:2023)]
    for(a in avgs) {
      # Retrieve relevant statistics for the current average type
      #hs_f_stat <- hs_stats[[as.character(a)]]$f_stat
      #hs_r_squared <- hs_stats[[as.character(a)]]$r_squared
      #col_f_stat <- col_stats[[as.character(a)]]$f_stat
      #col_r_squared <- col_stats[[as.character(a)]]$r_squared
      for(n in norm)
      {
        for(s in stage) 
        {
          hs_var <- paste0("hs", s, n, "_", a)
          col_var <- paste0("col", s, n, "_", a)
          current <- paste0("same_", h, "_hs ~ ", paste(hs_var, col_var, sep=" + "))
          
          formula <- c(
            current,
            paste0(current, " + inst_group + in_state + (inst_group * in_state)"),
            paste0(current, " + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + prestige_bin"),
            paste0(current, " + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + prestige_bin + col_end"),
            paste0(current, " + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + prestige_bin + col_end + hs_state")
          )
          
          for (f in 1:length(formula)) 
          {
            form <- formula[f]
            model <- lm(form, data = data)
            models[[paste0(h, s, n, "_avg_", a, "_", f)]] <- model
            model_key <- paste0(h, stage[1], norm[1], "_avg_", a, "_", f)
            coef_data <- coef_data %>%
              bind_rows(
                data.frame(
                  hs_var = hs_var,
                  col_var = col_var,
                  geo = h,
                  avg = a,
                  model = f,
                  hs_coef = coef(model)[hs_var],
                  hs_conf_low = confint(model)[hs_var, 1],
                  hs_conf_high = confint(model)[hs_var, 2],
                  col_coef = coef(model)[col_var],
                  col_conf_low = confint(model)[col_var, 1],
                  col_conf_high = confint(model)[col_var, 2]
                )
              )
          }
          hs_coef = coef(model)[hs_var]
          col_coef = coef(model)[col_var]
          for(inst in unique(regression$inst_group))
          {
            for(in_state in unique(regression$in_state))
            {
              
              # Determine coefficients for current group
              inst_coef <- ifelse(inst == "PF", 0, coef(model)[paste0("inst_group", inst)])
              in_state_coef <- ifelse(in_state == "Out-of-State", 0, coef(model)[paste0("in_state", in_state)])
              interaction_coef <- ifelse(
                inst == "PF" || in_state == "Out-of-State",
                0,
                coef(model)[paste0("inst_group", inst, ":in_state", in_state)]
              )
    
            # Calculate semi-elasticity for high school labor demand (hs_var)
            hs_group_semi <- (hs_coef + inst_coef + in_state_coef + interaction_coef)
        
            # Calculate semi-elasticity for college labor demand (col_var)
            col_group_semi <- (col_coef + inst_coef + in_state_coef + interaction_coef)
        
            # Store results in dataframe
            group_semi_elasticities <- group_semi_elasticities %>%
              bind_rows(data.frame(
                  geo = h,
                  avg = a,
                  norm = n,
                  stage = s,
                  inst_group = inst,
                  in_state = in_state,
                  hs_semi_elasticity = hs_group_semi,
                  col_semi_elasticity = col_group_semi
                  ))
              }
            }

          
          # Define control inclusion for each model
          controls <- list(
            "Undergraduate Major FE" = c("No", "No", "Yes", "Yes", "Yes", "No", "No", "Yes", "Yes", "Yes"),
            "Transfer and Non-Traditional FE" = c("No", "No", "Yes", "Yes", "Yes", "No", "No", "Yes", "Yes", "Yes"),
            "Occupational Group FE" = c("No", "No", "Yes", "Yes", "Yes", "No", "No", "Yes", "Yes", "Yes"),
            "Occupational Prestige Bin FE" = c("No", "No", "Yes", "Yes", "Yes", "No", "No", "Yes", "Yes", "Yes"),
            "Year of College Graduation FE" = c("No", "No", "No", "Yes", "Yes", "No", "No", "No", "Yes", "Yes"),
            "High School State FE" = c("No", "No", "No", "No", "Yes", "No", "No", "No", "No", "Yes")
          )
        }
        texreg(
          list(
            models[[paste0(h, stage[1], n, "_avg_", a, "_1")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_2")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_3")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_4")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_5")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_1")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_2")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_3")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_4")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_5")]]
          ),
          custom.model.names = rep(paste0("(", 1:5, ")"), 2),
          label = paste0("table:opt_", h, n, "_", a),
          #caption = paste0(
          # "Probability of returning to ", h, " containing high school. ",
          # "First-stage partial F-statistic for HS shock: ", round(hs_f_stat, 2),
          # ", R-squared: ", round(hs_r_squared, 2),
          #"; First-stage partial F-statistic for college shock: ", round(col_f_stat, 2),
          # ", R-squared: ", round(col_r_squared, 2)),
          center = FALSE,
          digits = 3,
          custom.gof.rows = controls,
          custom.coef.map = nestedlist,
          file = paste0(directory, "/Outputs/Tables/opt_", h, n, "_", a,"_final.tex"),
          append = TRUE
        )
      }
    }
  }
write.csv(group_semi_elasticities,file.path(directory,"Data/06","group_semi_elasticities.csv"))
write.csv(coef_data,file.path(directory,"Data/06","coef_data_semi.csv"))
  
cbsa_shock_ptile <- fread(file.path(directory,"Data/04","cbsa_shock.csv")) %>%
  table.express::select(year,cbsa_code,shock_avg_7,ptile_shock_avg_7)
cbsa_shock_ptile[,year := factor(year)]

# Extract semi-elasticities for relevant return measurement
# First, return to high school labor market
semi_cbsa <- group_semi_elasticities %>%
  table.express::filter(geo == "cbsa" & avg == 7 & norm != "_ptile" & stage == "_shock") %>%
  table.express::select(inst_group,in_state,hs_semi_elasticity)
# Next, return to high school state
semi_state <- group_semi_elasticities %>%
  table.express::filter(geo == "state" & avg == 7 & norm != "_ptile" & stage == "_shock") %>%
  table.express::select(inst_group,in_state,hs_semi_elasticity)

# Compute predictions for labor market returns across entire sample
predictions_cbsa <- regression[,.N,by=.(col_end,inst_group,in_state,same_cbsa_hs,ever_leave_cbsa_hs)] %>%
  dcast(col_end + inst_group + in_state ~ same_cbsa_hs + ever_leave_cbsa_hs,
         value.var = "N", fill = 0)
setnames(predictions_cbsa, old = c("0_0", "0_1", "1_0", "1_1"), 
  new = c("weird", "pred_leavers", "pred_stayers", "pred_returners"))
predictions_cbsa[,pred_shr_returners_base := pred_returners/(pred_returners+pred_leavers)]
predictions_cbsa <- predictions_cbsa[, .(col_end,inst_group,in_state,pred_shr_returners_base)]
# Compute predictions for state returns across entire sample
predictions_state <- regression[,.N,by=.(col_end,inst_group,in_state,same_state_hs,ever_leave_state_hs)] %>%
  dcast(col_end + inst_group + in_state ~ same_state_hs + ever_leave_state_hs,
        value.var = "N",fill = 0)
setnames(predictions_state, old = c("0_0", "0_1", "1_0", "1_1"),
         skip_absent = TRUE,
  new = c("weird", "pred_leavers", "pred_stayers", "pred_returners"))
predictions_state[,pred_shr_returners_base := pred_returners/(pred_returners+pred_leavers)]
predictions_state <- predictions_state[, .(col_end,inst_group,in_state,pred_shr_returners_base)]

# Compute labor market x year of college graduation return rates, to compare against predictions
empir_cbsa <- regression[,.N,by=.(col_end,hs_cbsa,inst_group,in_state,same_cbsa_hs,ever_leave_cbsa_hs)] %>%
  dcast( hs_cbsa + col_end + inst_group + in_state ~ same_cbsa_hs + ever_leave_cbsa_hs,
         value.var = "N", fill = 0) %>%
  merge(cbsa_shock_ptile, by.x = c("hs_cbsa","col_end"), by.y = c("cbsa_code","year"), all.x=TRUE) %>%
  merge(predictions_cbsa, by = c("col_end","inst_group","in_state"),all.x=TRUE) %>%
  merge(semi_cbsa, by = c("inst_group","in_state"),all.x=TRUE)
# Renaming columns based on conditions
setnames(empir_cbsa, old = c("0_0", "0_1", "1_0", "1_1"),  # Original column names from dcast
  new = c("weird", "leavers", "stayers", "returners"))
empir_cbsa[,total_non_stayers := returners+leavers]
empir_cbsa[,shr_returners := returners/total_non_stayers]
empir_cbsa[,pred_shr_returners := pred_shr_returners_base + (shock_avg_7 * hs_semi_elasticity)]
# Next aggregate upward, taking weighted average of predictions and actual return rates
# for different combinations of in_state and inst_group
diff_cbsa <- empir_cbsa[, .(shr_returners = weighted.mean(shr_returners,w=total_non_stayers,na.rm=TRUE),
                             pred_shr_returners = weighted.mean(pred_shr_returners,w=total_non_stayers,na.rm=TRUE),
                             difference = shr_returners - pred_shr_returners), by = .(col_end,hs_cbsa)]
# Between 2000 and 2022, by how many percentage points did the local labor market's return
# rate exceed the prediction, controlling for year and where natives attended college
diff_cbsa <- diff_cbsa[, .(shr_returners_cbsa = mean(shr_returners,na.rm=TRUE),
                           pred_shr_returners_cbsa = mean(pred_shr_returners,na.rm=TRUE),
                           difference_cbsa = mean(difference, na.rm=TRUE)),by=.(hs_cbsa)]

# Compute state x year of college graduation return rates, to compare against predictions
empir_state <- regression[,.N,by=.(col_end,hs_cbsa,inst_group,in_state,same_state_hs,ever_leave_state_hs)] %>%
  dcast( hs_cbsa + col_end + inst_group + in_state ~ same_state_hs + ever_leave_state_hs,
         value.var = "N", fill = 0) %>%
  merge(cbsa_shock_ptile, by.x = c("hs_cbsa","col_end"), by.y = c("cbsa_code","year"), all.x=TRUE) %>%
  merge(predictions_state, by = c("col_end","inst_group","in_state"),all.x=TRUE) %>%
  merge(semi_state, by = c("inst_group","in_state"),all.x=TRUE)
# Renaming columns based on conditions
setnames(empir_state, old = c("0_0", "0_1", "1_0", "1_1"),  # Original column names from dcast
  new = c("weird", "leavers", "stayers", "returners"),
  skip_absent = TRUE)
empir_state[,total_non_stayers := returners+leavers]
empir_state[,shr_returners := returners/total_non_stayers]
empir_state[,pred_shr_returners := pred_shr_returners_base + (shock_avg_7 * hs_semi_elasticity)]
# Next aggregate upward, taking weighted average of predictions and actual return rates
# for different combinations of in_state and inst_group
diff_state <- empir_state[, .(shr_returners = weighted.mean(shr_returners,w=total_non_stayers,na.rm=TRUE),
                             pred_shr_returners = weighted.mean(pred_shr_returners,w=total_non_stayers,na.rm=TRUE),
                             difference= shr_returners - pred_shr_returners), by = .(col_end,hs_cbsa)]
# Between 2000 and 2022, by how many percentage points did the local labor market's return
# rate exceed the prediction, controlling for year and where natives attended college
diff_state <- diff_state[, .(shr_returners_state = mean(shr_returners,na.rm=TRUE),
                           pred_shr_returners_state = mean(pred_shr_returners,na.rm=TRUE),
                           difference_state = mean(difference, na.rm=TRUE)),by=.(hs_cbsa)]

# Merge labor market and state-level analyses into single object for export
differences <- merge(diff_state,diff_cbsa,by=c("hs_cbsa"))

# Export merged file
write.csv(differences,file.path(directory,"Data/06","local_differences.csv"))

```

##      Second Stage

```{r second-stage}

models <- list()
years <- 2000:2021
# Prepare data to collect coefficients
coef_data <- data.frame()

for(yr in years)
{
  for(h in geos) {
    data <- if(h == "cbsa") regression_cbsa else regression_state
    data <- data[col_end == yr]
    for(a in avgs) {
      # Retrieve relevant statistics for the current average type
      hs_f_stat <- hs_stats[[as.character(a)]]$f_stat
      hs_r_squared <- hs_stats[[as.character(a)]]$r_squared
      col_f_stat <- col_stats[[as.character(a)]]$f_stat
      col_r_squared <- col_stats[[as.character(a)]]$r_squared
      for(n in norm)
      {
        for(s in stage) 
        {
          hs_var <- paste0("hs", s, n, "_", a)
          col_var <- paste0("col", s, n, "_", a)
          current <- paste0("same_", h, "_hs ~ ", paste(hs_var, col_var, sep=" + "))
          
          formula <- c(
            current,
            paste0(current, " + inst_group + in_state + (inst_group * in_state)"),
            paste0(current, " + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3"),
            paste0(current, " + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end"),
            paste0(current, " + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + col_end + hs_state")
          )
          
          }
          
          
        
          # Define control inclusion for each model
          controls <- list(
            "Undergraduate Major FE" = c("No", "No", "Yes", "Yes", "Yes", "No", "No", "Yes", "Yes", "Yes"),
            "Transfer and Non-Traditional FE" = c("No", "No", "Yes", "Yes", "Yes", "No", "No", "Yes", "Yes", "Yes"),
            "Occupational Group FE" = c("No", "No", "Yes", "Yes", "Yes", "No", "No", "Yes", "Yes", "Yes"),
            "Year of College Graduation FE" = c("No", "No", "No", "Yes", "Yes", "No", "No", "No", "Yes", "Yes"),
            "High School State FE" = c("No", "No", "No", "No", "Yes", "No", "No", "No", "No", "Yes")
          )
        }
        texreg(
          list(
            models[[paste0(h, stage[1], n, "_avg_", a, "_1")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_2")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_3")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_4")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_5")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_1")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_2")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_3")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_4")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_5")]]
          ),
          custom.model.names = rep(paste0("(", 1:5, ")"), 2),
          label = paste0("table:opt_", h, n, "_", a),
          caption = paste0(
           "Probability of returning to ", h, " containing high school. ",
           "First-stage partial F-statistic for HS shock: ", round(hs_f_stat, 2),
           ", R-squared: ", round(hs_r_squared, 2),
          "; First-stage partial F-statistic for college shock: ", round(col_f_stat, 2),
           ", R-squared: ", round(col_r_squared, 2)),
          center = FALSE,
          digits = 3,
          custom.gof.rows = controls,
          custom.coef.map = nestedlist,
          file = paste0(directory, "/Outputs/Tables/opt_", h, n, "_", a, "_2019-24.tex"),
          append = TRUE
        )
      }
    }
  }

```


##    Single-Year Regressions

```{r}

models <- list()
years <- 2000:2021
# Prepare data to collect coefficients
coef_data <- data.frame()

for(yr in years)
{
  for(h in geos) {
    data <- if(h == "cbsa") regression_cbsa else regression_state
    data[col_end == yr]
    for(a in avgs) {
      # Retrieve relevant statistics for the current average type
      #hs_f_stat <- hs_stats[[as.character(a)]]$f_stat
      #hs_r_squared <- hs_stats[[as.character(a)]]$r_squared
      #col_f_stat <- col_stats[[as.character(a)]]$f_stat
      #col_r_squared <- col_stats[[as.character(a)]]$r_squared
      for(n in norm)
      {
        for(s in stage) 
        {
          hs_var <- paste0("hs", s, n, "_", a)
          col_var <- paste0("col", s, n, "_", a)
          current <- paste0("same_", h, "_hs ~ ", paste(hs_var, col_var, sep=" + "))
          
          formula <- c(
            current,
            paste0(current, " + inst_group + in_state + (inst_group * in_state)"),
            paste0(current, " + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3"),
            paste0(current, " + inst_group + in_state + (inst_group * in_state) + non_traditional + transfer + col_major + soc_3 + hs_state")
          )
          
          for (f in 1:length(formula)) 
          {
            form <- formula[f]
            model <- lm(form, data = data)
            models[[paste0(h, s, n, "_avg_", a, "_", f)]] <- model
            model_key <- paste0(h, stage[1], norm[1], "_avg_", a, "_", f)
            coef_data <- coef_data %>%
              bind_rows(
                data.frame(
                  year = yr,
                  hs_var = hs_var,
                  col_var = col_var,
                  geo = h,
                  avg = a,
                  model = f,
                  hs_coef = coef(model)[hs_var],
                  hs_conf_low = confint(model)[hs_var, 1],
                  hs_conf_high = confint(model)[hs_var, 2],
                  col_coef = coef(model)[col_var],
                  col_conf_low = confint(model)[col_var, 1],
                  col_conf_high = confint(model)[col_var, 2]
                )
              )
          }
          
          # Define control inclusion for each model
          controls <- list(
            "Undergraduate Major FE" = c("No", "No", "Yes","Yes", "No", "No", "Yes","Yes"),
            "Transfer and Non-Traditional FE" = c("No", "No", "Yes","Yes", "No", "No", "Yes","Yes"),
            "Occupational Group FE" = c("No", "No", "Yes","Yes", "No", "No", "Yes","Yes"),
            "High School State FE" = c("No", "No", "No", "Yes", "No", "No", "No",  "Yes")
          )
        }
        texreg(
          list(
            models[[paste0(h, stage[1], n, "_avg_", a, "_1")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_2")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_3")]],
            models[[paste0(h, stage[1], n, "_avg_", a, "_4")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_1")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_2")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_3")]],
            models[[paste0(h, stage[2], n, "_avg_", a, "_4")]]
          ),
          custom.model.names = rep(paste0("(", 1:4, ")"), 2),
          label = paste0("table:opt_", h, n, "_", a),
          #caption = paste0(
           #"Probability of returning to ", h, " containing high school. ",
           #"First-stage partial F-statistic for HS shock: ", round(hs_f_stat, 2),
           #", R-squared: ", round(hs_r_squared, 2),
          #"; First-stage partial F-statistic for college shock: ", round(col_f_stat, 2),
          # ", R-squared: ", round(col_r_squared, 2)),
          center = FALSE,
          digits = 3,
          custom.gof.rows = controls,
          custom.coef.map = nestedlist,
          file = paste0(directory, "/Outputs/Tables/opt_", h, n, "_", a,"_",yr,".tex"),
          append = TRUE
        )
      }
    }
  }
}

write.csv(coef_data,file.path(directory,"Data/06","coef_data.csv"))
  

```