---
title: "08_regression_june"
author: "Nicholas Martens"
date: "2023-06-14"
output: html_document
---

##    Import necessary packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(texreg)
library(tidyverse)

options(digits = 1)
```

##    Setup
Directories and filenames that change with machine
```{r directory, include=FALSE}
directory = "/Users/nickmartens/Dropbox (University of Michigan)/Linkedin"

```

##    Import Microdata
Avoid rerunning previous eight steps and saving ~6 hours
```{r import, include=FALSE}
#microdata_1 = microdata
all_binary_final = read.csv(file.path(directory,"Data/regression_data.csv"))
actual_cohort = read.csv(file.path(directory,"Data/actual_cohort.csv"))
```


##    Convert Shock to Decile
On the advice of Shane Reed to "fully saturate" linear probability model
```{r saturation, include=FALSE}
actual_cohort$coh_02 = ntile(actual_cohort$coh_02, n = 10)
actual_cohort$coh_03 = ntile(actual_cohort$coh_03, n = 10)
actual_cohort$coh_04 = ntile(actual_cohort$coh_04, n = 10)
actual_cohort$coh_05 = ntile(actual_cohort$coh_05, n = 10)
actual_cohort$coh_06 = ntile(actual_cohort$coh_06, n = 10)
actual_cohort$coh_07 = ntile(actual_cohort$coh_07, n = 10)
actual_cohort$coh_08 = ntile(actual_cohort$coh_08, n = 10)
actual_cohort$coh_09 = ntile(actual_cohort$coh_09, n = 10)
actual_cohort$coh_10 = ntile(actual_cohort$coh_10, n = 10)
actual_cohort$coh_11 = ntile(actual_cohort$coh_11, n = 10)
actual_cohort$coh_12 = ntile(actual_cohort$coh_12, n = 10)
actual_cohort$coh_13 = ntile(actual_cohort$coh_13, n = 10)
actual_cohort$coh_14 = ntile(actual_cohort$coh_14, n = 10)
actual_cohort$coh_15 = ntile(actual_cohort$coh_15, n = 10)
actual_cohort$coh_16 = ntile(actual_cohort$coh_16, n = 10)

# Rename columns to ease merging
col_shock = actual_cohort %>%
  rename(col_cbsa = cbsa_code)
hs_shock = actual_cohort %>%
  rename(hs_cbsa = cbsa_code)
```

##    Merge Shocks with Microdata
```{r merge, include=FALSE}
# Filter by college graduation year and attach shock data for hs and college CBSA
all_binary02 = microdata %>%
  filter(col_end == 2002) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_03":"coh_16")) %>%
  rename(col_shock = coh_02) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_03":"coh_16")) %>%
  rename(hs_shock = coh_02) %>%
  relocate(hs_shock, .before = "col_start")
all_binary03 = microdata %>%
  filter(col_end == 2003) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02","coh_04":"coh_16")) %>%
  rename(col_shock = coh_03) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02","coh_04":"coh_16")) %>%
  rename(hs_shock = coh_03) %>%
  relocate(hs_shock, .before = "col_start") 
all_binary04 = microdata %>%
  filter(col_end == 2004) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_03","coh_05":"coh_16")) %>%
  rename(col_shock = coh_04) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_03","coh_05":"coh_16")) %>%
  rename(hs_shock = coh_04) %>%
  relocate(hs_shock, .before = "col_start") 
all_binary05 = microdata %>%
  filter(col_end == 2005) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_04","coh_06":"coh_16")) %>%
  rename(col_shock = coh_05) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_04","coh_06":"coh_16")) %>%
  rename(hs_shock = coh_05) %>%
  relocate(hs_shock, .before = "col_start") 
all_binary06 = microdata %>%
  filter(col_end == 2006) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_05","coh_07":"coh_16")) %>%
  rename(col_shock = coh_06) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_05","coh_07":"coh_16")) %>%
  rename(hs_shock = coh_06) %>%
  relocate(hs_shock, .before = "col_start") 
all_binary07 = microdata %>%
  filter(col_end == 2007) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_06","coh_08":"coh_16")) %>%
  rename(col_shock = coh_07) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_06","coh_08":"coh_16")) %>%
  rename(hs_shock = coh_07) %>%
  relocate(hs_shock, .before = "col_start") 
all_binary08 = microdata %>%
  filter(col_end == 2008) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_07","coh_09":"coh_16")) %>%
  rename(col_shock = coh_08) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_07","coh_09":"coh_16")) %>%
  rename(hs_shock = coh_08) %>%
  relocate(hs_shock, .before = "col_start")
all_binary09 = microdata %>%
  filter(col_end == 2009) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_08","coh_10":"coh_16")) %>%
  rename(col_shock = coh_09) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_08","coh_10":"coh_16")) %>%
  rename(hs_shock = coh_09) %>%
  relocate(hs_shock, .before = "col_start") 
all_binary10 = microdata %>%
  filter(col_end == 2010) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_09","coh_11":"coh_16")) %>%
  rename(col_shock = coh_10) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_09","coh_11":"coh_16")) %>%
  rename(hs_shock = coh_10) %>%
  relocate(hs_shock, .before = "col_start")
all_binary11 = microdata %>%
  filter(col_end == 2011) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_10","coh_12":"coh_16")) %>%
  rename(col_shock = coh_11) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_10","coh_12":"coh_16")) %>%
  rename(hs_shock = coh_11) %>%
  relocate(hs_shock, .before = "col_start") 
all_binary12 = microdata %>%
  filter(col_end == 2012) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_11","coh_13":"coh_16")) %>%
  rename(col_shock = coh_12) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_11","coh_13":"coh_16")) %>%
  rename(hs_shock = coh_12) %>%
  relocate(hs_shock, .before = "col_start")
all_binary13 = microdata %>%
  filter(col_end == 2013) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_12","coh_14":"coh_16")) %>%
  rename(col_shock = coh_13) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_12","coh_14":"coh_16")) %>%
  rename(hs_shock = coh_13) %>%
  relocate(hs_shock, .before = "col_start") 
all_binary14 = microdata %>%
  filter(col_end == 2014) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_13","coh_15":"coh_16")) %>%
  rename(col_shock = coh_14) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_13","coh_15":"coh_16")) %>%
  rename(hs_shock = coh_14) %>%
  relocate(hs_shock, .before = "col_start")
all_binary15 = microdata %>%
  filter(col_end == 2015) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_14","coh_16")) %>%
  rename(col_shock = coh_15) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_14","coh_16")) %>%
  rename(hs_shock = coh_15) %>%
  relocate(hs_shock, .before = "col_start")
all_binary16 = microdata %>%
  filter(col_end == 2016) %>%
  left_join(col_shock, by = "col_cbsa") %>%
  select(-c("coh_02":"coh_15")) %>%
  rename(col_shock = coh_16) %>%
  relocate(col_shock, .before = "barrons") %>%
  left_join(hs_shock, by = "hs_cbsa") %>%
  select(-c("coh_02":"coh_15")) %>%
  rename(hs_shock = coh_16) %>%
  relocate(hs_shock, .before = "col_start")
# Rejoin individual graduation years
# Add binary variable to check if individual left hs CBSA for college
all_binary_final = rbind(all_binary02,
                         all_binary03,
                         all_binary04,
                         all_binary05,
                         all_binary06,
                         all_binary07,
                         all_binary08,
                         all_binary09,
                         all_binary10,
                         all_binary11,
                         all_binary12,
                         all_binary13,
                         all_binary14,
                         all_binary15,
                         all_binary16) %>%
  ungroup() %>%
  group_by(user_id) %>%
  mutate(col_hs_diff_cbsa = ifelse(col_cbsa == hs_cbsa,0,1))
```


##    Creating Dummies
Binary dummies for Barron's selectivity ratings and deciles for labor demand shocks
```{r final clean, include=FALSE}
# Land Grant: LANDGRNT == 1
# Not land grant: LANDGRNT == 2

# Public Non-Profit CONTROL == 1
# Private Non-Profit: CONTROL == 2
# Private For-Profit: CONTROL == 3

# Historically Black Institution: HBCU == 1
# Primarily White Institution: HBCU == 2
regression_data = all_binary_final %>%  
  mutate(freq_barrons = 1,
         freq_hs = 1,
         freq_col = 1,
         freq_cont = 1
         ) %>%
  pivot_wider(names_from = "barrons",
              values_from = "freq_barrons",
              names_prefix = "barrons_",
              names_sort = TRUE,
              values_fill = 0
              ) %>%
  # Combine Barron's ratings 5, 9, and 999
  mutate(barrons_last = barrons_5 + barrons_9 + barrons_999) %>%
  filter(is.na(col_shock)==FALSE) %>%
  mutate(hs_decile = ntile(hs_shock, n = 10),
         col_decile = ntile(col_shock, n = 10)) %>%
  pivot_wider(names_from = "hs_decile", 
              values_from = "freq_hs",
              names_prefix = "hs_decile",
              names_sort = TRUE,
              values_fill = 0
              ) %>%
  pivot_wider(names_from = "col_decile", 
              values_from = "freq_col",
              names_prefix = "col_decile",
              names_sort = TRUE,
              values_fill = 0) %>%
  # Convert institutional control to dummies
  pivot_wider(names_from = "CONTROL",
              values_from = "freq_cont",
              names_prefix = "control",
              names_sort = TRUE,
              values_fill = 0) %>%
  mutate(pub_eli = case_when(control1 == 1 & ((barrons_1 | barrons_2)==1) ~ 1,
                             TRUE ~ 0),
         pri_eli = case_when(control2 == 1 & ((barrons_1 | barrons_2)==1) ~ 1,
                             TRUE ~ 0),
         pub_sel = case_when(control1 == 1 & barrons_3 == 1 ~ 1,
                             TRUE ~ 0),
         pri_sel = case_when(control2 == 1 & barrons_3 == 1 ~ 1,
                             TRUE ~ 0),
         pub_non = case_when(control1 == 1 & barrons_4 == 1 ~ 1,
                             TRUE ~ 0),
         pri_non = case_when(control2 == 1 & barrons_4 == 1 ~ 1,
                             TRUE ~ 0),
         pub_last = case_when(control1 == 1 & barrons_last == 1 ~ 1,
                             TRUE ~ 0),
         pri_last = case_when(control2 == 1 & barrons_last == 1 ~ 1,
                             TRUE ~ 0),
         for_prof = case_when(control3 == 1 ~ 1,
                              TRUE ~ 0)
         )
```

##    Regressions!
hs_state * col_end fixed effects
Variable must be omitted for decile dummies to work
1 is the lowest decile by default
10 is the highest
Strongest labor demand shocks are in decile 10

```{r regression cbsa, include=FALSE}
# Most parsimonious (no major, interactions, state-year fixed effects)
attempt1 = lm(data = regression_data, same_cbsa ~  
                #barrons_1 + barrons_2 + barrons_3 + barrons_4 + 
                # Formerly Beta_1
                hs_decile1 + hs_decile2 + hs_decile3 + hs_decile4 + hs_decile4 +
                hs_decile5 + hs_decile6 + hs_decile7 +
                hs_decile8 + hs_decile9 + #hs_decile10 + 
                # Formerly Beta_2
                col_decile1 + col_decile2 + col_decile3 + col_decile4 +
                col_decile5 + col_decile6 + col_decile7 + col_decile8 +
                col_decile9 +
                # New coefficient for institutional control relative to elite public college
                pri_eli + 
                pub_sel + pri_sel + 
                pub_non + pri_non +
                pub_last + pri_last +
                for_prof)

# Include state-year fixed effects
attempt2 = lm(data = regression_data, same_cbsa ~  
                #barrons_1 + barrons_2 + barrons_3 + barrons_4 + 
                # Formerly Beta_1
                hs_decile1 + hs_decile2 + hs_decile3 + hs_decile4 + hs_decile4 +
                hs_decile5 + hs_decile6 + hs_decile7 +
                hs_decile8 + hs_decile9 + #hs_decile10 + 
                # Formerly Beta_2
                col_decile1 + col_decile2 + col_decile3 + col_decile4 +
                col_decile5 + col_decile6 + col_decile7 + col_decile8 +
                col_decile9 + #col_decile10 + 
                pri_eli + 
                pub_sel + pri_sel + 
                pub_non + pri_non +
                pub_last + pri_last +
                for_prof +
                (hs_state * col_end))

# State-year fixed effects and shock decile interactions 
# R automatically excludes the 10th decile, which are the largest labor demand shocks
# Holding selectivity constant, individuals who attended college in weaker local labor markets are more likely to leave their hometown
# [Beta]% more likely to leave hometown than somebody from the least selective
# Other binaries will be relative to omitted variable 
attempt3 = lm(data = regression_data, same_cbsa ~  
                #barrons_1 + barrons_2 + barrons_3 + barrons_4 + 
                # Formerly Beta_1
                hs_decile1 + hs_decile2 + hs_decile3 + hs_decile4 + hs_decile4 +
                hs_decile5 + hs_decile6 + hs_decile7 +
                hs_decile8 + hs_decile9 + #hs_decile10 + 
                # Formerly Beta_2
                col_decile1 + col_decile2 + col_decile3 + col_decile4 +
                col_decile5 + col_decile6 + col_decile7 + col_decile8 +
                col_decile9 + #col_decile10 + 
                pri_eli + 
                pub_sel + pri_sel + 
                pub_non + pri_non +
                pub_last + pri_last +
                for_prof +
                # Formerly Beta_3
                (hs_decile1 * col_hs_diff_cbsa) + 
                (hs_decile2 * col_hs_diff_cbsa) +
                (hs_decile3 * col_hs_diff_cbsa) +
                (hs_decile4 * col_hs_diff_cbsa) +
                (hs_decile5 * col_hs_diff_cbsa) +
                (hs_decile6 * col_hs_diff_cbsa) +
                (hs_decile7 * col_hs_diff_cbsa) +
                (hs_decile8 * col_hs_diff_cbsa) +
                (hs_decile9 * col_hs_diff_cbsa) +
                (hs_decile10 * col_hs_diff_cbsa) +               
                # Formerly Beta_4
                # People who go to college in weak labor markets are
                # more likely to stay in their hometowns 
                (col_decile1 * col_hs_diff_cbsa) + 
                (col_decile2 * col_hs_diff_cbsa) +
                (col_decile3 * col_hs_diff_cbsa) +
                (col_decile4 * col_hs_diff_cbsa) +
                (col_decile5 * col_hs_diff_cbsa) +
                (col_decile6 * col_hs_diff_cbsa) +
                (col_decile7 * col_hs_diff_cbsa) +
                (col_decile8 * col_hs_diff_cbsa) +
                (col_decile9 * col_hs_diff_cbsa) +
                (col_decile10 * col_hs_diff_cbsa) +
                (hs_state * col_end))

# State-year fixed effects, shock decile interactions, major fixed effects
# Using barrons_last as basis for selectivity
# Tenth decile of labor demand shocks in high school and college 
attempt4 = lm(data = regression_data, same_cbsa ~  
                #barrons_1 + barrons_2 + barrons_3 + barrons_4 +
                # Formerly Beta_1
                hs_decile1 + hs_decile2 + hs_decile3 + hs_decile4 + hs_decile4 +
                hs_decile5 + hs_decile6 + hs_decile7 +
                hs_decile8 + hs_decile9 + #hs_decile10 + 
                # Formerly Beta_2
                col_decile1 + col_decile2 + col_decile3 + col_decile4 +
                col_decile5 + col_decile6 + col_decile7 + col_decile8 +
                col_decile9 + #col_decile10 + 
                control2 + control3 +
                pri_eli + 
                pub_sel + pri_sel + 
                pub_non + pri_non +
                pub_last + pri_last +
                for_prof +
                # Formerly Beta_3
                (hs_decile1 * col_hs_diff_cbsa) + 
                (hs_decile2 * col_hs_diff_cbsa) +
                (hs_decile3 * col_hs_diff_cbsa) +
                (hs_decile4 * col_hs_diff_cbsa) +
                (hs_decile5 * col_hs_diff_cbsa) +
                (hs_decile6 * col_hs_diff_cbsa) +
                (hs_decile7 * col_hs_diff_cbsa) +
                (hs_decile8 * col_hs_diff_cbsa) +
                (hs_decile9 * col_hs_diff_cbsa) +
    #            (hs_decile10 * col_hs_diff_cbsa) +               
                # Formerly Beta_4
                # People who go to college in weak labor markets are
                # more likely to stay in their hometowns 
                (col_decile1 * col_hs_diff_cbsa) + 
                (col_decile2 * col_hs_diff_cbsa) +
                (col_decile3 * col_hs_diff_cbsa) +
                (col_decile4 * col_hs_diff_cbsa) +
                (col_decile5 * col_hs_diff_cbsa) +
                (col_decile6 * col_hs_diff_cbsa) +
                (col_decile7 * col_hs_diff_cbsa) +
                (col_decile8 * col_hs_diff_cbsa) +
                (col_decile9 * col_hs_diff_cbsa) +
  #              (col_decile10 * col_hs_diff_cbsa) +
  #              (starts_with(hs_decile) * col_hs_diff_cbsa) +
                (hs_state * col_end) +
                major
  ) 

```


```{r regression state, include=FALSE}
# Most parsimonious (no major, interactions, state-year fixed effects)
attempt5 = lm(data = regression_data, same_state ~  
                #barrons_1 + barrons_2 + barrons_3 + barrons_4 + 
                # Formerly Beta_1
                hs_decile1 + hs_decile2 + hs_decile3 + hs_decile4 + hs_decile4 +
                hs_decile5 + hs_decile6 + hs_decile7 +
                hs_decile8 + hs_decile9 + #hs_decile10 + 
                # Formerly Beta_2
                col_decile1 + col_decile2 + col_decile3 + col_decile4 +
                col_decile5 + col_decile6 + col_decile7 + col_decile8 +
                col_decile9 +
                # New coefficient for institutional control relative to elite public college
                pri_eli + 
                pub_sel + pri_sel + 
                pub_non + pri_non +
                pub_last + pri_last +
                for_prof)

# Include state-year fixed effects
attempt6 = lm(data = regression_data, same_state ~  
                #barrons_1 + barrons_2 + barrons_3 + barrons_4 + 
                # Formerly Beta_1
                hs_decile1 + hs_decile2 + hs_decile3 + hs_decile4 + hs_decile4 +
                hs_decile5 + hs_decile6 + hs_decile7 +
                hs_decile8 + hs_decile9 + #hs_decile10 + 
                # Formerly Beta_2
                col_decile1 + col_decile2 + col_decile3 + col_decile4 +
                col_decile5 + col_decile6 + col_decile7 + col_decile8 +
                col_decile9 + #col_decile10 + 
                pri_eli + 
                pub_sel + pri_sel + 
                pub_non + pri_non +
                pub_last + pri_last +
                for_prof +
                (hs_state * col_end))

# State-year fixed effects and shock decile interactions 
# R automatically excludes the 10th decile, which are the largest labor demand shocks
# Holding selectivity constant, individuals who attended college in weaker local labor markets are more likely to leave their hometown
# [Beta]% more likely to leave hometown than somebody from the least selective
# Other binaries will be relative to omitted variable 
attempt7 = lm(data = regression_data, same_state ~  
                #barrons_1 + barrons_2 + barrons_3 + barrons_4 + 
                # Formerly Beta_1
                hs_decile1 + hs_decile2 + hs_decile3 + hs_decile4 + hs_decile4 +
                hs_decile5 + hs_decile6 + hs_decile7 +
                hs_decile8 + hs_decile9 + #hs_decile10 + 
                # Formerly Beta_2
                col_decile1 + col_decile2 + col_decile3 + col_decile4 +
                col_decile5 + col_decile6 + col_decile7 + col_decile8 +
                col_decile9 + #col_decile10 + 
                pri_eli + 
                pub_sel + pri_sel + 
                pub_non + pri_non +
                pub_last + pri_last +
                for_prof +
                # Formerly Beta_3
                (hs_decile1 * col_hs_diff_cbsa) + 
                (hs_decile2 * col_hs_diff_cbsa) +
                (hs_decile3 * col_hs_diff_cbsa) +
                (hs_decile4 * col_hs_diff_cbsa) +
                (hs_decile5 * col_hs_diff_cbsa) +
                (hs_decile6 * col_hs_diff_cbsa) +
                (hs_decile7 * col_hs_diff_cbsa) +
                (hs_decile8 * col_hs_diff_cbsa) +
                (hs_decile9 * col_hs_diff_cbsa) +
                (hs_decile10 * col_hs_diff_cbsa) +               
                # Formerly Beta_4
                # People who go to college in weak labor markets are
                # more likely to stay in their hometowns 
                (col_decile1 * col_hs_diff_cbsa) + 
                (col_decile2 * col_hs_diff_cbsa) +
                (col_decile3 * col_hs_diff_cbsa) +
                (col_decile4 * col_hs_diff_cbsa) +
                (col_decile5 * col_hs_diff_cbsa) +
                (col_decile6 * col_hs_diff_cbsa) +
                (col_decile7 * col_hs_diff_cbsa) +
                (col_decile8 * col_hs_diff_cbsa) +
                (col_decile9 * col_hs_diff_cbsa) +
                (col_decile10 * col_hs_diff_cbsa) +
                (hs_state * col_end))

# State-year fixed effects, shock decile interactions, major fixed effects
# Using barrons_last as basis for selectivity
# Tenth decile of labor demand shocks in high school and college 
attempt8 = lm(data = regression_data, same_state ~  
                #barrons_1 + barrons_2 + barrons_3 + barrons_4 +
                # Formerly Beta_1
                hs_decile1 + hs_decile2 + hs_decile3 + hs_decile4 + hs_decile4 +
                hs_decile5 + hs_decile6 + hs_decile7 +
                hs_decile8 + hs_decile9 + #hs_decile10 + 
                # Formerly Beta_2
                col_decile1 + col_decile2 + col_decile3 + col_decile4 +
                col_decile5 + col_decile6 + col_decile7 + col_decile8 +
                col_decile9 + #col_decile10 + 
                control2 + control3 +
                pri_eli + 
                pub_sel + pri_sel + 
                pub_non + pri_non +
                pub_last + pri_last +
                for_prof +
                # Formerly Beta_3
                (hs_decile1 * col_hs_diff_cbsa) + 
                (hs_decile2 * col_hs_diff_cbsa) +
                (hs_decile3 * col_hs_diff_cbsa) +
                (hs_decile4 * col_hs_diff_cbsa) +
                (hs_decile5 * col_hs_diff_cbsa) +
                (hs_decile6 * col_hs_diff_cbsa) +
                (hs_decile7 * col_hs_diff_cbsa) +
                (hs_decile8 * col_hs_diff_cbsa) +
                (hs_decile9 * col_hs_diff_cbsa) +
    #            (hs_decile10 * col_hs_diff_cbsa) +               
                # Formerly Beta_4
                # People who go to college in weak labor markets are
                # more likely to stay in their hometowns 
                (col_decile1 * col_hs_diff_cbsa) + 
                (col_decile2 * col_hs_diff_cbsa) +
                (col_decile3 * col_hs_diff_cbsa) +
                (col_decile4 * col_hs_diff_cbsa) +
                (col_decile5 * col_hs_diff_cbsa) +
                (col_decile6 * col_hs_diff_cbsa) +
                (col_decile7 * col_hs_diff_cbsa) +
                (col_decile8 * col_hs_diff_cbsa) +
                (col_decile9 * col_hs_diff_cbsa) +
  #              (col_decile10 * col_hs_diff_cbsa) +
  #              (starts_with(hs_decile) * col_hs_diff_cbsa) +
                (hs_state * col_end) +
                major
  ) 

```

##    Exporting Regression Result
```{r regression export, include=FALSE}


texreg(list(attempt1, attempt2, attempt3, attempt4),
       custom.model.names = c("Shock Only",
                              "Shock \\ State-Year FE",
                              "Shock \\ State-Year FE \\ LD Shock $\times$ Return",
                              "Labor Shock \\ State-Year FE \\ LD Shock $\times$ Return \\ Major"),
       custom.coef.names = c("Private Elite",
                             "Public Selective",
                             "Private Selective",
                             "Public Competitve",
                             "Private Competitive ",
                             "Public Non-Competitive",
                             "Private Non-Competitive",
                             "For Profit",
                             "Moving for College"),
       custom.header = list("Residing in Same Labor Market as High School" = 1:4),
      caption = "Labor market-level retention under different specifications. All of the coefficients except 'Moving for College' are dummy variables relative to public elite universities. For example, a negative 'Private Elite' coefficient indicates graduates of private elite universities are less likely to stay in their home labor market than graduates of public elite universities.",
      center = TRUE,
      digits = 3,
      omit.coef=c('Intercept|barrons_1|barrons_2|barrons_3|barrons_4|hs_state|col_end|hs_decile|col_decile|major|control'))


texreg(list(attempt5, attempt6, attempt7, attempt8),
       custom.model.names = c("Shock Only",
                              "Shock \\ State-Year FE",
                              "Shock \\ State-Year FE \\ LD Shock $\times$ Return",
                              "Labor Shock \\ State-Year FE \\ LD Shock $\times$ Return \\ Major"),
       custom.coef.names = c("Private Elite",
                             "Public Selective",
                             "Private Selective",
                             "Public Competitve",
                             "Private Competitive ",
                             "Public Non-Competitive",
                             "Private Non-Competitive",
                             "For Profit",
                             "Moving for College"),
       custom.header = list("Residing in Same State as High School" = 1:4),
      caption = "State-level retention under different specifications. All of the coefficients except 'Moving for College' are dummy variables relative to public elite universities. For example, a negative 'Private Elite' coefficient indicates graduates of private elite universities are less likely to stay in their home state than graduates of public elite universities.",
      center = TRUE,
      digits = 3,
      omit.coef=c('Intercept|barrons_1|barrons_2|barrons_3|barrons_4|hs_state|col_end|hs_decile|col_decile|major|control'))

```

##    Tables for Internal Use
```{r internal, include=FALSE}
# Problem: the negative effect of attending elite institution likely diluted
# because 58 percent students in sample who attend selective universities originate 
# in New England

# Compare migration by selectivity
elite = regression_data %>% 
  filter(col_name == "Cornell University") %>%
  group_by(col_name) %>%
  summarize(n = n()) %>%
  arrange(n)
  mutate(shr = n/sum(n))

elite_state = regression_data %>% 
          group_by(hs_state) %>%
          summarize(n = n()) %>%
          mutate(shr = n/sum(n))

# Are graduates of public elite universities more likely to return home than their peers at private institutions?
cont = regression_data %>% 
  filter(CONTROL == 3) %>%
  group_by(col_name) %>%
  summarize(n = n()) %>%
  mutate(shr = n/sum(n))
```

##    Tables for Paper
```{r external, include=FALSE}
major_dist = all_binary_final %>% group_by(barrons,major) %>% summarize(n = n())
sel_dist = major_dist %>% group_by(barrons) %>% summarize(total = sum(n))
big_majors = major_dist %>% 
  left_join(sel_dist, by = "barrons") %>% 
  filter(major %in% c("Business","Engineering")) %>% 
  mutate(Selectivity = case_when(barrons == 1 | barrons == 2 ~ "Elite",
                          barrons == 3 ~ "Selective",
                          barrons == 4 ~ "Competitive",
                          barrons %in% c(5,9) ~ "Non-Competitive",
                          barrons == 999 ~ "For-Profit"))

big_majors$Selectivity = factor(big_majors$Selectivity,ordered = TRUE, 
                       levels = c("Elite","Selective","Competitive","Non-Competitive","For-Profit"))
major_sel_table = big_majors %>%  
  group_by(Selectivity,major) %>%
  summarize(n = sum(n),
            total = sum(total)) %>%
  mutate(pct = n/total) %>%
  select(-c(n,total)) %>%
  distinct() %>%
  pivot_wider(names_from = major,
              values_from = pct) %>%
  mutate(Business = Business * 100,
         Engineering = Engineering * 100) %>%
  mutate(Selectivity = as.character(Selectivity))
 
stargazer(major_sel_table[,1:3], 
          summary = FALSE,
          rownames = FALSE,
          digits = 1)
          #covariate.labels=c("Selectivity",
          #                   "Business",
          #                   "Engineering"),
          #rownames = TRUE,
          digit.separator = ","
          )

col_inc_dist = read_xlsx(paste(directory,"Data/chetty_college_inc_dist.xlsx",sep="/"))
dist_by_sel = col_inc_dist %>% 
  filter(is.na(selectivity_nick)==FALSE) %>%
  group_by(selectivity_nick) %>% 
  summarize(par_q1_n = sum(par_q1_n),
            par_q2_n = sum(par_q2_n),
            par_q3_n = sum(par_q3_n),
            par_q4_n = sum(par_q4_n),
            par_q5_n = sum(par_q5_n)) %>%
  mutate(total = par_q1_n + par_q2_n + par_q3_n + par_q4_n + par_q5_n) %>%
  mutate(par_q1_pct = par_q1_n/total * 100,
         par_q2_pct = par_q2_n/total * 100,
         par_q3_pct = par_q3_n/total * 100,
         par_q4_pct = par_q4_n/total * 100,
         par_q5_pct = par_q5_n/total * 100) %>%
  select(c(selectivity_nick,total:par_q5_pct))

dist_by_sel$selectivity_nick = factor(dist_by_sel$selectivity_nick,ordered = TRUE, 
                       levels = c("Public Elite",
                                  "Private Elite",
                                  "Public Selective",
                                  "Private Selective",
                                  "Public Competitive",
                                  "Private Competitive",
                                  "Public Non-Competitive",
                                  "Private Non-Competitive",
                                  "For Profit"))


dist_by_sel = dist_by_sel %>% arrange(selectivity_nick) %>% mutate(selectivity_nick = as.character(selectivity_nick))


stargazer(dist_by_sel, 
          summary = FALSE,
          rownames = FALSE,
          digits = NULL,
          digits.extra=NULL,
          covariate.labels=c("Selectivity",
                             "Total Graduates, 2013",
                             "From Q1",
                             "From Q2",
                             "From Q3",
                             "From Q4",
                             "From Q5"),
          #rownames = TRUE,
          digit.separator = ","
          )  


selectivity = regression_data %>%
  mutate(sel = case_when(barrons_1 == 1 ~ 1,
                         barrons_2 == 1 ~ 2,
                         barrons_3 == 1 ~ 3,
                         barrons_4 == 1 ~ 4,
                         barrons_last == 1 ~ 5)) %>%
  group_by(sel) %>%
  summarize(same_cbsa = sum(same_cbsa, na.rm = TRUE),
            same_state = sum(same_state, na.rm = TRUE),
            in_state_col = sum(in_state_col, na.rm = TRUE),
            col_hs_diff_cbsa = sum(col_hs_diff_cbsa, na.rm = TRUE),
            total = n()
  )

selectivity_control = regression_data %>%
  mutate(sel = case_when(barrons_1 == 1 ~ 1,
                         barrons_2 == 1 ~ 2,
                         barrons_3 == 1 ~ 3,
                         barrons_4 == 1 ~ 4,
                         barrons_last == 1 ~ 5)) %>%
  group_by(sel, control1) %>%
  summarize(same_cbsa = sum(same_cbsa, na.rm = TRUE),
            same_state = sum(same_state, na.rm = TRUE),
            total = n()
  )


selectivity_table = selectivity %>%
  mutate(same_cbsa_shr = (same_cbsa/total)*100,
         same_state_shr = round((same_state/total)*100, 1),
         in_state_col_shr = round((in_state_col/total)*100, 1),
         col_hs_diff_cbsa_shr =  round((1-(col_hs_diff_cbsa/total))*100, 1)) %>%
  select(-c(same_cbsa:col_hs_diff_cbsa)) %>%
  relocate(total, .after = col_hs_diff_cbsa_shr) %>%
  mutate(sel = case_when(sel == 1 ~ "Elite",
                         sel == 2 ~ "More Selective",
                         sel == 3 ~ "Selective",
                         sel == 4 ~ "Less Selective",
                         sel == 5 ~ "Least Selective"))
stargazer(selectivity_table, 
          summary = FALSE,
          covariate.labels=c("Selectivity",
                             "Same LM",
                             "Same State",
                             "In-State College",
                             "College in Same LM"),
          rownames = FALSE,
          digit.separator = ",",
          digits = 1)

```

##    Remove Individual Years
```{delete}
rm(all_binary02, all_binary03, all_binary04, all_binary05, all_binary06,
   all_binary07, all_binary08, all_binary09, all_binary10, all_binary11,
   all_binary12, all_binary13, all_binary14, all_binary15, all_binary16)
```
