```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(xtable)
library(extrafont)
library(educationdata)
library(ggrepel)
library(cartogram)
library(spatstat)
library(tidyverse)
library(tidycensus)
library(spdep)
library(sf)
library(texreg)
library(scales)
library(stargazer)
library(ggplot2)
library(data.table)

# Only needs to run once
#font_import(pattern = "lmroman*")
#loadfonts()

library(dotenv)
library(here)
load_dot_env(here::here(".env"))
directory <- Sys.getenv("BRAIN_DRAIN_ROOT")  # kept for any Outputs/-only uses not touched by this reorg
data_dir  <- file.path(directory, "Data")
out_dir   <- file.path(directory, "Outputs")

# Height, width, units, and background for maps
hei = 3.75
wid = 6.5
dpi = 600
bkgrnd = 'transparent'
unit = "in"
geos = c("cbsa","state")

diverging_colors = c('#762a83','#9970ab','#c2a5cf','#e7d4e8','#f7f7f7','#d9f0d3','#a6dba0','#5aae61','#1b7837')
prestige_bin_colors <- c("#7fc97f","#beaed4","#fdc086","#ffff99")
inst_group_colors <- c("#F8766D","#7CAE00","#00BFC4","#C77CFF")
monotonic_colors = c('#f7f7f7','#d9f0d3','#a6dba0','#5aae61','#1b7837') 
return_colors = c()

options(scipen = 999)
# Ensures stargazer tables have three digits instead of a zero after the first two
options(digits=3)
`%nin%` = Negate(`%in%`)
```

##    ROI
###   Plotting ROI Bar Chart

```{r}
# Bar chart data
roi_bar <- roi %>%
  # Merge with institutional characteristics to get institutional groupings
  inner_join(institutional_characteristics %>% select(unitid, inst_group,state_abbr), by = "unitid") %>%
  # Summarize at the institutional group level
  #group_by(inst_group,state_abbr) %>%
  filter(inst_group != "Private, For-Profit") %>%
  group_by(inst_group) %>%
  summarize(total_grads = sum(total_grads, na.rm = TRUE),
            not_recruited_shr = (sum(not_recruited, na.rm = TRUE) / total_grads),
            not_retained_shr = (sum(not_retained, na.rm = TRUE) / total_grads),
            recruited_shr = (sum(recruited, na.rm = TRUE) / total_grads),
            retained_shr = (sum(retained, na.rm = TRUE) / total_grads)) %>%
  select(-c(total_grads)) %>%
  pivot_longer(ends_with("shr"),names_to = "metric",values_to="shr") %>%
  mutate(metric = str_replace_all(metric, "_", " ") %>%
           str_replace_all("shr", "") %>%
           str_to_title() %>%
           trimws(),
         inst_group = case_when(inst_group == "PF" ~ "Public Flagship",
                                 TRUE ~ inst_group))

custom_colors = c("Recruited" = '#d9f0d3',
                  "Retained" = '#5aae61',
                  "Not Retained" = '#9970ab',
                  "Not Recruited" = '#e7d4e8') 


# Create the bar plot
ggplot(roi_bar, aes(x = shr, y = reorder(inst_group, shr), fill = metric)) +
  geom_col(alpha = 0.7) +
  labs(x = "Percent of Graduates", y = "Institutional Group") +
  scale_fill_manual(values = custom_colors) +  # Apply custom colors
  scale_x_continuous(labels = percent_format(),
                     limits = c(0,1.01),
                     expand = c(0.001,0)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text         = element_text(size=10, family="LM Roman 10"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank())
ggsave(file = paste(directory,"/Outputs/","roi_bar.png",sep = ""),
         width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi)
```

##    Appendix 
###   Omission
####    Skippable Omission Cleaning
```{r om clean, include=FALSE}

in_hs_cols = paste("in_hs_cbsa",as.character(c(min_post_grad:max_post_grad)),sep="_")
in_state_cols = paste("in_hs_state",as.character(c(min_post_grad:max_post_grad)),sep="_")

survivorship = microdata[, (in_hs_cols) := lapply(.SD, `==`, hs_cbsa_code), .SDcols = paste("cbsa_code",as.character(c(min_post_grad:max_post_grad)),sep="_")]
survivorship[, (in_state_cols) := lapply(.SD, `==`, hs_state), .SDcols = paste("cbsa_state",as.character(c(min_post_grad:max_post_grad)),sep="_")]
  

residence_cols = c(paste("in_hs_cbsa",as.character(c(min_post_grad:max_post_grad)),sep="_"),
         paste("in_hs_state",as.character(c(min_post_grad:max_post_grad)),sep="_"))

survivorship[, (residence_cols) :=  lapply(.SD, 
                                 function(x) ifelse(is.na(x)==TRUE, NA, ifelse(x==TRUE,1,0))),
             .SDcols = residence_cols]

relevant_cols = c(residence_cols,"col_end","user_id")
survivorship = survivorship[, ..relevant_cols]  

#reshaped_cbsa = melt(survivorship, (in_hs_cols)) %>% 
#  dcast((in_hs_cols) + year ~ variable)

reshaped_cbsa = melt(survivorship, 
     measure_vars = (in_hs_cols),
     id.vars = c("user_id","col_end")) %>%
  table.express::mutate(variable = str_remove_all(variable,"[[:punct:]]")) %>%
  table.express::mutate(geo = str_remove_all(variable,"[[:digit:]]")) %>%
  table.express::mutate(geo = str_remove_all(geo,"inhs")) %>%
  table.express::mutate(n_grad = str_remove_all(variable,"[[:alpha:]]")) %>%
  table.express::mutate(n_grad = as.numeric(n_grad)) %>%
  table.express::mutate(year = col_end + n_grad) %>%
  # Remove NAs that are in the future
  # Those NAs are not valid missing data
  table.express::filter(year <= 2023) #%>%
  #dcast(n_grad ~ geo,
  #      fun.aggregate = length,
  #      value_var = "value")
omission_plot = reshaped_cbsa %>%
  filter(geo == "cbsa") %>%
  # Remove missing data (years between college graduation
  # and 2023 with no work history)
  filter(is.na(value)==FALSE) %>%
  as.data.frame() %>%
  select(-c(variable,geo)) %>%
  group_by(user_id,col_end) %>%
  summarize(yrs_inc = n()) %>%
  mutate(max_yrs_inc = 2023 - col_end,
         adj_yrs_inc = case_when(yrs_inc > max_yrs_inc ~ max_yrs_inc,
                                 TRUE ~ yrs_inc))

omission_distribution = omission_plot %>%
  group_by(col_end) %>%
  summarize(yrs_inc_05 = quantile(adj_yrs_inc,0.05),
            yrs_inc_25 = quantile(adj_yrs_inc,0.25),
            yrs_inc_50 = quantile(adj_yrs_inc,0.50),
            yrs_inc_75 = quantile(adj_yrs_inc,0.75), 
            yrs_inc_95 = quantile(adj_yrs_inc,0.95)) #%>%
  #pivot_longer(!col_end,
  #             names_to = "ptile",
  #             names_prefix = "yrs_inc_",
  #             values_to = "yrs_inc"
  #             )
write.csv(omission_distribution,file.path(directory,"Outputs/omission_distribution.csv"))
```
####    Plotting Omission
```{r om plot, include=FALSE}

# Pulling data on the number of years of work history, by college graduation year
# Data shows pattern of strategic omission as workers age
omission_distribution = read_csv(file.path(directory,"Outputs/omission_distribution.csv")) %>%
  select(c(col_end,ptile,yrs_inc)) %>%
  pivot_wider(names_from = ptile,
              names_prefix = "yrs_inc_",
              values_from = yrs_inc) %>%
  mutate(n_grad = 2023 - col_end)

ggplot(omission_distribution) + 
  geom_line(aes(x = n_grad, y = yrs_inc_50, color = "Median LI User")) +
  geom_point(aes(x = n_grad, y = yrs_inc_50), color = "#40004b") +
  geom_ribbon(aes(x = n_grad, ymin = yrs_inc_25, ymax = yrs_inc_75, 
                  fill = "Interquartile Range"),
              color = NA,
              alpha = 0.3) +
  geom_line(aes(x = n_grad, y = n_grad, color = "Theoretical Maximum")) +
  scale_x_continuous(expand = c(0.001,0)) + 
  scale_y_continuous(limits = c(0,41),
                     expand = c(0,0)) + 
  scale_color_manual(name='',values = c("Median LI User"="#40004b",
                                        "Interquartile Range" = "#40004b",
                                        "Theoretical Maximum"= "#2c7fb8")) +
  scale_fill_manual(name='',values = c("Median LI User"="#40004b",
                                       "Interquartile Range" = "#40004b",
                                        "Theoretical Maximum"= "#2c7fb8")) +
  xlab("Year Since College Graduation") +
  ylab("Years of Work History on LI Profile") +
  labs(title = "Omission of Work History on LI by Years Since College Graduation") +
  theme(panel.background = element_rect(fill='transparent'),
        plot.background = element_rect(fill='transparent', color=NA),
        text         = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank(),
        legend.background = element_rect(fill='transparent',color=NA),
        legend.box.background = element_rect(fill='transparent',color=NA),
        legend.position = "bottom",
        panel.grid.major.y = element_line(color = "grey",
                                          linewidth = 0.25),
        panel.grid.major.x = element_blank(),
        axis.line.x = element_line(color="black"))
  ggsave(file = paste(directory,"/Outputs/","omission_distribution.png",sep = ""),
         width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi)      

```

####   Mapping Place of Birth

```{r birthplace}

# Pull state of residence by educational attainment from ACS
same_state = get_acs(geography = "county",
                 year = 2022,
                 variables = c(same_state = "B06009_011",
                               same_state = "B06009_012",
                               diff_state = "B06009_017",
                               diff_state = "B06009_018",
                               territory = "B06009_023",
                               territory = "B06009_024",
                               foreign = "B06009_029",
                               foreign = "B06009_030")) %>%
    mutate(GEOID = case_when(GEOID %in% c("02063","02066") ~ "02261",
                             #  Oglala Lakota County (formerly Shannon), 
                             #  South Dakota (FIPS 46102) to 46113
                             GEOID == "46102" ~ "46113",
                             #  Kusilvak Census Area (formerly Wade Hampton),
                             #  Alaska (FIPS 0) to 02270
                             GEOID == "02158" ~ "02270",
                             .default = GEOID)) %>%
  left_join(unified_cbsa, by = c("GEOID"="GeoFIPS")) %>%
  group_by(cbsa_code,variable) %>%
  summarize(total = sum(estimate)) %>%
  group_by(cbsa_code) %>%
  mutate(prop = total/sum(total)) %>%
  filter(variable == "same_cbsa_hs") %>%
  select(-c(variable,total)) %>%
  rename(same_state = prop) %>%
  filter(is.na(same_state)==FALSE)

# Linking to shapefile
birthplace_map = map %>%
  left_join(same_state, by = "cbsa_code")

ggplot(birthplace_map, aes(fill = same_state)) +
  geom_sf(show.legend = TRUE) +
  scale_fill_gradientn(name = "% of College Grads",
                       labels = scales::percent,
                       colors = color_list,
                       #values = c(0,0.06,0.12,0.18,0.24,0.36,0.5,0.75,1),
                       #low = "#40004b",
                       #high = "#1b7837",
                       #limits=c(0,1),
    ) +
  labs(title = "Share of College Graduates Born in State of Residence, 2022") +
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5))
ggsave(file = paste(directory,"/Outputs/","birthplace.png",sep = ""),
         width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi)


```
####   Map of College Nearby + In-State
```{r dist time}  

# Calculate LM-level proportions:
# College in HS labor market
# College less than 50 miles
# Attended college in-state
cbsa_dist = regression %>%
  as.data.frame() %>%
  select(c(user_id,in_state,col_in_not_hs_cbsa,dist)) %>%
  left_join(as.data.frame(cbsa_mode), by = "user_id") %>%
  mutate(in_state = case_when(in_state == "Out-of-State" ~ 0,
                              in_state == "In-State" ~ 1),
         dist = case_when(dist %in% c("[0,50]","(50,100]","(100,150]") ~ 1,
                          TRUE ~ 0)
         ) %>%
  group_by(cbsa_code) %>%
  summarize(col_hs_same_lm = 1-(sum(col_in_not_hs_cbsa)/n()),
            in_state = sum(in_state)/n(),
            dist = sum(dist)/n())

dist_map = map %>%
  left_join(cbsa_dist, by = "cbsa_code")

ggplot(dist_map, aes(fill = col_hs_same_lm)) +
  geom_sf(show.legend = TRUE) +
  scale_fill_gradientn(name = "% Attending\nCollege + HS\nIn Same LM",
                       labels = scales::percent,
                       colors = color_list,
                       #values = c(0,0.06,0.12,0.18,0.24,0.36,0.5,0.75,1),
                       #low = "#40004b",
                       #high = "#1b7837",
                       #limits=c(0,0.08),
    ) +
  labs(title = "Share Attending College and HS in Same Labor Market") +
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5))
ggsave(file = paste(directory,"/Outputs/","col_hs_same_lm.png",sep = ""),
         width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi)

ggplot(dist_map, aes(fill = in_state)) +
  geom_sf(show.legend = TRUE) +
  scale_fill_gradientn(name = "% Attending\nCollege + HS\nIn Same State",
                       labels = scales::percent,
                       colors = color_list,
                       #values = c(0,0.06,0.12,0.18,0.24,0.36,0.5,0.75,1),
                       #low = "#40004b",
                       #high = "#1b7837",
                       #limits=c(0,0.08),
    ) +
  labs(title = "Share Attending College and HS in Same State") +
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5))
ggsave(file = paste(directory,"/Outputs/","col_hs_same_state.png",sep = ""),
         width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi)
```

###    Coverage
####    Regressing Covariates 

```{r}

covariate = same_state %>%
  left_join(fraction, by = "cbsa_code") %>%
  left_join(prime_age, by = "cbsa_code") %>%
  left_join(cbsa_dist, by = "cbsa_code") %>%
  # NAs generated from merges should be zeroes because they stem
  # from small sample size
  mutate(col_hs_same_lm = if_else(is.na(col_hs_same_lm)==TRUE,0,col_hs_same_lm),
         in_state = if_else(is.na(in_state)==TRUE,0,in_state),
         dist = if_else(is.na(dist)==TRUE,0,dist))

# Regress log LI users on hs inclusion rate to determine if people in small
# towns are more likely to include it
geo_analysis1 = lm(data = covariate, prime_age_prop ~ log(total), weights = total)
geo_analysis2 = lm(data = covariate, prime_age_prop ~ log(total) + same_state + col_hs_same_lm + in_state + dist, weights = total)
texreg(list(geo_analysis1,geo_analysis2),
       file = paste0(directory,"/Outputs/Tables/geo_analysis.tex"),
       custom.model.names = c("Size Only","Size and LM Characteristics"),
       custom.coef.names = c("$log($Prime-Age College Grads Population)",
                             "College Graduates Born in Same State",
                             "College and HS in Same LM",
                             "College and HS in Same State",
                             "Attending Nearby College"
                             ),
      center = TRUE,
      digits = 5,
      align = TRUE,
      omit.coef=c('Intercept'))


```

####    Cleaning for Violin

```{r hs time}  
data(county_laea)

# Pull educational attainment by age from the Census Bureau
# Relies on the following age groups
# 18-24, 25-34, 35-44, 45-64, 65+
age_ed = get_acs(geography = "county",
                 year = 2022,
                 variables = c(ba_18 = "B15001_009",
                               ba_18 = "B15001_010",
                               ba_25 = "B15001_017",
                               ba_25 = "B15001_018",
                               ba_35 = "B15001_025",
                               ba_35 = "B15001_026",
                               ba_45 = "B15001_033",
                               ba_45 = "B15001_034",
                               ba_65 = "B15001_041",
                               ba_65 = "B15001_042",
                               ba_18 = "B15001_050",
                               ba_18 = "B15001_051",
                               ba_25 = "B15001_058",
                               ba_25 = "B15001_059",
                               ba_35 = "B15001_066",
                               ba_35 = "B15001_067",
                               ba_45 = "B15001_074",
                               ba_45 = "B15001_075",
                               ba_65 = "B15001_082",
                               ba_65 = "B15001_083"      
                               )) %>%
    mutate(GEOID = case_when(GEOID %in% c("02063","02066") ~ "02261",
                             #  Oglala Lakota County (formerly Shannon), 
                             #  South Dakota (FIPS 46102) to 46113
                             GEOID == "46102" ~ "46113",
                             #  Kusilvak Census Area (formerly Wade Hampton),
                             #  Alaska (FIPS 0) to 02270
                             GEOID == "02158" ~ "02270",
                             .default = GEOID)) %>%
  left_join(unified_cbsa, by = c("GEOID"="GeoFIPS")) %>%
  # Remove rural Puerto Rico
  filter(cbsa_code != "72999") %>%
  group_by(cbsa_code,variable) %>%
  summarize(total = sum(estimate)) %>%
  mutate(age = str_sub(variable,4,5)) %>%
  select(-variable) 

# Declare mode function used to assign single CBSA to user
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

# Calculating modal CBSA for every user
cbsa_mode = microdata %>% 
  select(starts_with(c("user_id","cbsa_code_"))) %>%
  pivot_longer(cols = starts_with("cbsa_code_"),
               names_to = "n_grad",
               values_to = "cbsa_code",
               values_transform = list(cbsa_code = as.character),
               values_drop_na = TRUE) %>%
  # CBSA codes omit leading zero so ensures all cbsa_codes include it
  mutate(cbsa_code = str_pad(cbsa_code,5,side = "left",pad = "0")) %>%
  filter(is.na(cbsa_code)==FALSE) %>%
  group_by(user_id) %>%
  summarise(cbsa_code = Mode(cbsa_code)) %>%
  as.data.table()

culled = regression[,c("user_id","birth","col_type")]
age_cbsa = cbsa_mode[culled, on = "user_id"] %>%
  as.data.frame() %>%
  group_by(cbsa_code)

# Calculating number of users by age group and CBSA
cbsa18 = age_cbsa %>%
  filter(1993 < birth) %>%
  summarize(li18 = n())
cbsa25 = age_cbsa %>%
  filter(1983 < birth & birth < 1998) %>%
  summarize(li25 = n())  
cbsa35 = age_cbsa %>%
  filter(1973 < birth & birth < 1988) %>%
  summarize(li35 = n())  
cbsa45 = age_cbsa %>%
  filter(1953 < birth & birth < 1978) %>%
  summarize(li45 = n())  
cbsa65 = age_cbsa %>%
  filter(birth < 1958) %>%
  summarize(li65 = n())  

numerator = cbsa18 %>%
  left_join(cbsa25, by = "cbsa_code") %>%
  left_join(cbsa35, by = "cbsa_code") %>%
  left_join(cbsa45, by = "cbsa_code") %>%
  left_join(cbsa65, by = "cbsa_code") %>%
  pivot_longer(cols = starts_with("li"),
               names_to = "age",
               values_to = "li_total") %>%
  mutate(age = str_sub(age,3,4)) %>%
  # Remove non-metropolitan Puerto Rico
  filter(cbsa_code != "72999")
  
fraction_long = age_ed %>%
  left_join(numerator, by = c("cbsa_code","age")) %>%
  # Not all CBSAs have LI users for all age groups
  # Coerce missing data into zeroes instead of NAs
  mutate(li_total = case_when(is.na(li_total)==TRUE ~ 0,
                              TRUE ~ li_total),
         li_prop = li_total/total)

fraction = fraction_long %>%
  pivot_wider(id_cols = cbsa_code,
              values_from = li_prop,
              names_from = age,
              names_prefix = "age_"
              )

write.csv(fraction,file.path(data_dir,"intermediate/fraction.csv"))
```

####   Plotting Violin

```{r violin}

violin = fraction_long %>%
  filter(age != "65") %>%
  mutate(age = case_when(age == "18" ~ "18-24",
            age == "25" ~ "25-34",
            age == "35" ~ "35-44",
            age == "45" ~ "45-64")) %>%
  mutate(age = factor(age, 
                      ordered = TRUE, 
                      levels = c("45-64","35-44","25-34","18-24"))) %>%
  mutate(age = as.factor(age),
         cbsa_code = as.factor(cbsa_code)) 

age_medians = violin %>%
  group_by(age) %>%
  summarize(li_prop = weighted.median(x = li_prop, w = total))


ggplot(data = violin, aes(x = li_prop, 
                          y = age,
                          color = age,
                          fill = age),
       size = total) +
  geom_violin(alpha=0.3,
              trim = TRUE,
              scale = "width") +
  geom_point(data = age_medians,
             shape = 9,
             aes(x = li_prop,
                 y = age,
                 size = 18)) +
  scale_x_continuous(labels = scales::percent,
                     expand = c(0,0)) + 
  labs(title = "LinkedIn Sample Coverage by Age Group and Labor Market") +
  ylab("Age Group") +
  xlab("LinkedIn Sample as a Percentage of All College Graduates in Labor Force") +
  theme(panel.background = element_rect(fill='transparent'),
        plot.background = element_rect(fill='transparent', color=NA),
        text         = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_line(color = "grey",
                                          linewidth = 0.25),
        panel.grid.major.y = element_blank(),
        axis.line.y = element_line(color="black"),
        legend.background = element_rect(fill='transparent',color=NA),
        legend.box.background = element_rect(fill='transparent',color=NA),
        legend.position = "none")
ggsave(file = paste(directory,"/Outputs/","violin.png",sep = ""),
         width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi)

```

####    Mapping Prime-Age Coverage

```{r prime age}

# Creating map of coverage for all 25-64 college graduates
prime_age = fraction_long %>%
  group_by(cbsa_code) %>%
  filter(age %in% c("25","35","45")) %>%
  summarize(li_total = sum(li_total),
            total = sum(total)) %>%
  mutate(prime_age_prop = li_total/total)

# Linking to shapefile
pa_map = map %>%
  left_join(prime_age, by = "cbsa_code")

ggplot(pa_map, aes(fill = prime_age_prop)) +
  geom_sf(show.legend = TRUE) +
  scale_fill_gradientn(name = "LI Share of\nCollege Grads",
                       labels = scales::percent,
                       colors = diverging_colors,
                       values = c(0,0.06,0.12,0.18,0.24,0.36,0.5,0.75,1),
                       #low = "#40004b",
                       #high = "#1b7837",
                       limits=c(0,0.08),
    ) +
  labs(title = "LI Users as a Share of All 25-64 College Graduates, by Labor Market") +
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5))
ggsave(file = paste(directory,"/Outputs/","pa_chloropleth.png",sep = ""),
         width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi)

```

####    Mapping Dorling Cartogram

```{r prime age}

# Remove NAs since Dorling function doesn't accept NA weights
dorling_data = pa_map %>%
  filter(is.na(total)==FALSE)

# Create Dorling cartogram of prime-age coverage
pa_dorling <- cartogram_dorling(x = dorling_data,
                                    weight = "total",
                                    k = 1, itermax = 100)


ggplot(data = pa_dorling, aes(fill = prime_age_prop)) +
  geom_sf(data = pa_map, fill = NA, colour="gray", size=0.1) +
  geom_sf(color = "grey30", size = 0.5,show.legend = TRUE) +
  scale_fill_gradientn(name = "LI Share of\nCollege Grads",
                       labels = scales::percent,
                       colors = color_list,
                       values = c(0,0.06,0.12,0.18,0.24,0.36,0.5,0.75,1),
                       #low = "#40004b",
                       #high = "#1b7837",
                       limits=c(0,0.08),
    ) +
  labs(title = "LI Users as a Share of All 25-64 College Graduates, by Labor Market") +
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5)) 
ggsave(file = paste(directory,"/Outputs/","pa_dorling.png",sep = ""),
         width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi)

```



###    Other
####    Distance Traveled by Out-of-State Students

```{r out-of-state}

oos_count = regression %>% 
  as.data.frame() %>%
  group_by(col_type,in_state) %>%
  dplyr::summarize(total = n())

oos_dist_long = regression %>% 
  table.express::filter(in_state == "Out-of-State") %>%
  as.data.frame() %>%
  mutate(Distance = factor(dist,
                           ordered = TRUE,
                           levels = c("[0,50]","(50,100]","(100,150]","(150,200]",
                              "(200,250]","(250,500]","(500,1e+03]","(1e+03,1e+04]")
                            )) %>%
  select(-dist)  %>%
  group_by(Distance,col_type) %>%
  dplyr::summarize(n = n()) 

oos_totals = oos_dist_long %>%
  group_by(col_type) %>%
  dplyr::summarize(total = sum(n))

oos_dist_wide = oos_dist_long %>%
  dplyr::left_join(oos_totals, by = "col_type") %>%
  mutate(pct = round((n/total)*100,1)) %>%
  select(Distance,col_type,pct) %>%
  pivot_wider(names_from = "col_type",
              values_from = "pct") %>%
  arrange(Distance) %>%
  mutate(Distance = as.character(Distance)) %>%
  relocate(Distance, .before = "Public Flagship")
  
names(oos_dist_wide) = c("Distance","Public\nFlagship","Priavate\nFor-Profit",
                        "Priavate\nNon-Profit","RPU\nLess Selective","RPU\nMore Selective")

stargazer(oos_dist_wide, 
          summary = FALSE,
          rownames = FALSE,
          digits = NA,
          #style = "qje",
          align = TRUE,
          #title = "Distance from high school to baccalaureate institution for out-of-state students, by institutional group",
          float = TRUE,
          out = file.path(directory,"/Outputs/Tables/oos-dist-wide.tex"),
          #label = "table:observation",
          digit.separator = ","
          )

```

####    Distance Traveled by In-State Students

```{r in-state}

is_count = regression %>% 
  as.data.frame() %>%
  group_by(col_type,in_state) %>%
  dplyr::summarize(total = n())

is_dist_long = regression %>% 
  table.express::filter(in_state == "In-State")%>%
  as.data.frame() %>%
  mutate(Distance = factor(dist,
                           ordered = TRUE,
                           levels = c("[0,50]","(50,100]","(100,150]","(150,200]",
                              "(200,250]","(250,500]","(500,1e+03]","(1e+03,1e+04]")
                            )) %>%
  select(-dist)  %>%
  group_by(Distance,col_type) %>%
  dplyr::summarize(n = n()) 

is_totals = is_dist_long %>%
  group_by(col_type) %>%
  dplyr::summarize(total = sum(n))

is_dist_wide = is_dist_long %>%
  dplyr::left_join(is_totals, by = "col_type") %>%
  mutate(pct = round((n/total)*100,1)) %>%
  select(Distance,col_type,pct) %>%
  pivot_wider(names_from = "col_type",
              values_from = "pct") %>%
  arrange(Distance) %>%
  mutate(Distance = as.character(Distance)) %>%
  relocate(Distance, .before = "Public Flagship")

#names(is_dist_wide) = c("Distance","Public\nFlagship","Private\nFor-Profit",
#                        "Private\nNon-Profit","RPU\nLess Selective","RPU\nMore Selective")

stargazer(is_dist_wide, 
          summary = FALSE,
          rownames = FALSE,
          digits = NA,
          #style = "qje",
          align = TRUE,
          #title = "Distance from high school to baccalaureate institution for in-state students, by institutional group",
          float = TRUE,
          out = file.path(directory,"/Outputs/Tables/is-dist-wide.tex"),
          #label = "table:observation",
          digit.separator = ","
          )

```

###   Plotting Shocks

```{r shocks, eval=FALSE}
# Filter to cases where post-graduation occupational data
microdata <- raw_microdata %>%
  filter(!is.na(cbsa_mode))
iv_cols <- names(microdata)[grepl("^(hs|col).*[1357]$", names(microdata))]
num_bins = 5
bin_shares = list()
for(col in iv_cols)
{
  bin_col_name <- paste0(col,"_bin")
  microdata[, paste0(col, "_bin") := cut(get(col), 
                                         breaks = quantile(get(col), 
                                                           probs = seq(0,1,length.out = num_bins+1),
                                                           na.rm=TRUE),
                                         labels = FALSE,
                                         include.lowest = TRUE)]
  bin_share <- microdata[, .(same_cbsa_hs = mean(same_cbsa_hs, na.rm = TRUE),
                             same_state_hs = mean(same_state_hs, na.rm = TRUE),
                             same_cbsa_col = mean(same_cbsa_col, na.rm = TRUE),
                             same_state_col = mean(same_state_col, na.rm = TRUE)),
                             by = bin_col_name]
  bin_share[, variable := col]
  setnames(bin_share, bin_col_name,"bin")
  bin_shares[[col]] <- bin_share
}
all_bin_shares <- rbindlist(bin_shares,use.names=TRUE,fill=TRUE) %>%
  mutate(geo = sub("_.*","",variable),
         avg = sub(".*_([0-9]+)$","\\1",variable),
         var = sub("(_[0-9]+)$","", sub("^[^_]+_","",variable)))

bin_shares = microdata[, .(count = .N), by = .(hs_shock_7_bin,hs_cbsa)] %>%
bin_shares[, shr := count/sum(count), by = .(hs_shock_7_bin)]

bin_composition <- dcast(bin_shares, hs_cbsa ~ hs_shock_7_bin, value.var = "shr", fill = 0)

cbsa_returns <- microdata[, .(same_cbsa_hs = mean(same_cbsa_hs, na.rm = TRUE),
                             same_state_hs = mean(same_state_hs, na.rm = TRUE),
                             same_cbsa_col = mean(same_cbsa_col, na.rm = TRUE),
                             same_state_col = mean(same_state_col, na.rm = TRUE)),
                             by = hs_cbsa]
cbsa_name = cbsa %>% 
  select(c("CBSA Code","CBSA Title")) %>% 
  rename(c("cbsa_code"="CBSA Code","cbsa_title"="CBSA Title")) %>%
  mutate(hs_cbsa = as.integer(cbsa_code)) %>%
  select(-cbsa_code) %>%
  distinct()

bin <- merge(bin_composition,cbsa_returns,by = "hs_cbsa") %>%
  merge(cbsa_name, by = "hs_cbsa")

```

###   Plotting Shocks

```{r shocks, eval=FALSE}
# Filter to cases where post-graduation occupational data
microdata <- raw_microdata %>%
  filter(!is.na(cbsa_mode))
iv_cols <- names(microdata)[grepl("^(hs|col).*[1357]$", names(microdata))]
num_bins = 5
bin_shares = list()
for(col in iv_cols)
{
  bin_col_name <- paste0(col,"_bin")
  microdata[, paste0(col, "_bin") := cut(get(col), 
                                         breaks = quantile(get(col), 
                                                           probs = seq(0,1,length.out = num_bins+1),
                                                           na.rm=TRUE),
                                         labels = FALSE,
                                         include.lowest = TRUE)]
  bin_share <- microdata[, .(same_cbsa_hs = mean(same_cbsa_hs, na.rm = TRUE),
                             same_state_hs = mean(same_state_hs, na.rm = TRUE),
                             same_cbsa_col = mean(same_cbsa_col, na.rm = TRUE),
                             same_state_col = mean(same_state_col, na.rm = TRUE)),
                             by = bin_col_name]
  bin_share[, variable := col]
  setnames(bin_share, bin_col_name,"bin")
  bin_shares[[col]] <- bin_share
}
all_bin_shares <- rbindlist(bin_shares,use.names=TRUE,fill=TRUE) %>%
  mutate(geo = sub("_.*","",variable),
         avg = sub(".*_([0-9]+)$","\\1",variable),
         var = sub("(_[0-9]+)$","", sub("^[^_]+_","",variable)))

bin_shares = microdata[, .(count = .N), by = .(hs_shock_7_bin,hs_cbsa)] %>%
bin_shares[, shr := count/sum(count), by = .(hs_shock_7_bin)]

bin_composition <- dcast(bin_shares, hs_cbsa ~ hs_shock_7_bin, value.var = "shr", fill = 0)

cbsa_returns <- microdata[, .(same_cbsa_hs = mean(same_cbsa_hs, na.rm = TRUE),
                             same_state_hs = mean(same_state_hs, na.rm = TRUE),
                             same_cbsa_col = mean(same_cbsa_col, na.rm = TRUE),
                             same_state_col = mean(same_state_col, na.rm = TRUE)),
                             by = hs_cbsa]
cbsa_name = cbsa %>% 
  select(c("CBSA Code","CBSA Title")) %>% 
  rename(c("cbsa_code"="CBSA Code","cbsa_title"="CBSA Title")) %>%
  mutate(hs_cbsa = as.integer(cbsa_code)) %>%
  select(-cbsa_code) %>%
  distinct()

bin <- merge(bin_composition,cbsa_returns,by = "hs_cbsa") %>%
  merge(cbsa_name, by = "hs_cbsa")

```



###    Table of Institutional Group Levels

```{r inst sumstat}

# Order that institutions will appear in table
col_order = c("Public Flagship","RPU, More Selective","RPU, Less Selective",
              "Private, Non-Profit","Private, For-Profit")

# Calculating return rates by institutional groups 
inst_levels = regression %>%
  as.data.frame() %>%
  mutate(in_state = case_when(in_state == "In-State" ~ "is",
                              in_state == "Out-of-State" ~ "oos"),
         col_type = factor(col_type, ordered = TRUE,
                           levels = col_order)) %>%
  group_by(col_type,in_state) %>%
  dplyr::summarise(same_cbsa_hs = sum(same_cbsa_hs),
                   same_state_hs = sum(same_state_hs),
                   n = n()) %>%
  mutate(same_cbsa_prop = round((same_cbsa_hs/n) * 100,1),
         same_state_prop = round((same_state_hs/n) * 100,1)) %>%
  select(-c(same_cbsa_hs,same_state_hs)) %>%
  pivot_wider(names_from = in_state,
              values_from = c(same_cbsa_prop,same_state_prop,n)) %>%
  mutate(cbsa_retention_gap = same_cbsa_prop_is - same_cbsa_prop_oos,
         state_retention_gap = same_state_prop_is - same_state_prop_oos) %>%
  relocate(c("n_is","n_oos"), .before = "same_cbsa_prop_is") %>%
  relocate("cbsa_retention_gap", .after = "same_cbsa_prop_oos") %>%
  # Convert institutional grouping back into character so it appears in table
  mutate(col_type = as.character(col_type))

# Splitting data into CBSA and state-level tables
inst_levels_cbsa = inst_levels %>%
  select(contains("cbsa"))
inst_levels_state = inst_levels %>%
  select(contains("state"))

#inst_levels_is = inst_levels %>%
#  select(ends_with("is"))
#inst_levels_oos = inst_levels %>%
#  select(ends_with("oos"))

# Export tables
stargazer(inst_levels_cbsa, 
          summary = FALSE,
          rownames = FALSE,
          digits = 1,
          #style = "qje",
          align = TRUE,
          covariate.labels = c("Institutional Grouping","Pct Returning, In-State","Pct Returning, Out-of-State","Difference"),
          title = "Return rate to high school labor market, by institutional group",
          float = TRUE,
          out = file.path(directory,"Outputs/Tables/inst-levels-cbsa.tex"),
          digit.separator = ","
          )
stargazer(inst_levels_state, 
          summary = FALSE,
          rownames = FALSE,
          digits = 1,
          #style = "qje",
          align = TRUE,
          covariate.labels = c("Institutional Grouping","Pct Returning, In-State","Pct Returning, Out-of-State","Difference"),
          title = "Return rate to high school state, by institutional group",
          float = TRUE,
          out = file.path(directory,"Outputs/Tables/inst-levels-state.tex"),
          digit.separator = ","
          )


median_distance = regression %>%
  as.data.frame() %>%
  filter(in_state == "Out-of-State") %>%
  mutate(col_type = case_when(col_type == "RPU, More Selective" ~ "RPU",
                              col_type == "RPU, Less Selective" ~ "RPU",
                              TRUE ~ col_type)) %>%
  group_by(col_type) %>%
  summarize(pct10 = quantile(distance_mi, 0.10),
            pct25 = quantile(distance_mi, 0.25),
            median = median(distance_mi),
            pct75 = quantile(distance_mi, 0.75),
            pct90 = quantile(distance_mi, 0.90)
            )

```


###    Table for Estimating Shock Quantiles

```{r}

quantifying_quantiles1 = cbsa_shock_ptile %>% 
  filter(year == 2021) %>% 
  group_by(ptile_avg_1) %>% 
  dplyr::summarize(est1 = stats::weighted.mean(x = avg_1, w = cbsa_actual)) %>%
  as.data.frame() %>%
  rename("ptile" = "ptile_avg_1")
quantifying_quantiles3 = cbsa_shock_ptile %>% 
  filter(year == 2021) %>% 
  group_by(ptile_avg_3) %>% 
  dplyr::summarize(est3 = stats::weighted.mean(x = avg_3, w = cbsa_actual)) %>%
  as.data.frame() %>%
  rename("ptile" = "ptile_avg_3")
quantifying_quantiles5 = cbsa_shock_ptile %>% 
  filter(year == 2021) %>% 
  group_by(ptile_avg_5) %>% 
  dplyr::summarize(est5 = stats::weighted.mean(x = avg_5, w = cbsa_actual)) %>%
  as.data.frame() %>%
  rename("ptile" = "ptile_avg_5")
quantifying_quantiles7 = cbsa_shock_ptile %>% 
  filter(year == 2021) %>% 
  group_by(ptile_avg_7) %>% 
  dplyr::summarize(est7 = stats::weighted.mean(x = avg_7, w = cbsa_actual)) %>%
  as.data.frame() %>%
  rename("ptile" = "ptile_avg_7")

quantifying_quantiles = quantifying_quantiles1 %>%
  dplyr::left_join(quantifying_quantiles3, by = "ptile")  %>%
  dplyr::left_join(quantifying_quantiles5, by = "ptile") %>%
  dplyr::left_join(quantifying_quantiles7, by = "ptile") %>%
  arrange(ptile)

stargazer(quantifying_quantiles[1:10,], 
          summary = FALSE,
          rownames = FALSE,
          digits = 3,
          #style = "qje",
          align = TRUE,
          title = "Average employment shock by decile in 2021",
          float = TRUE,
          #label = "table:observation",
          digit.separator = ",",
          out = file.path(directory,"Outputs",specification,"shocks.tex")
          )

```

###   Mapping Amenities

```{r differences}

differences <- read_csv(file.path(directory,"Data",specification,"local_differences.csv")) %>%
  mutate(cbsa_code = str_pad(hs_cbsa,width=5,side="left",pad="0")) %>%
  select(-c("hs_cbsa","...1")) %>%
  left_join(cbsa_li_crosswalk %>% select(c("cbsa_code","cbsa_core")) %>% distinct(), by = "cbsa_code") %>%
  mutate(difference_cbsa_alt = shr_returners_cbsa - pred_shr_returners_cbsa,
         difference_state_alt = shr_returners_state - pred_shr_returners_state,
         )
differences_unfilt <- read_csv(file.path(data_dir,"intermediate/local_differences_unfilt.csv")) %>%
  mutate(cbsa_code = str_pad(hs_cbsa,width=5,side="left",pad="0")) %>%
  select(-c("hs_cbsa","...1")) %>%
  left_join(cbsa_li_crosswalk %>% select(c("cbsa_code","cbsa_core")) %>% distinct(), by = "cbsa_code") %>%
  mutate(difference_cbsa_alt = shr_returners_cbsa - pred_shr_returners_cbsa,
         difference_state_alt = shr_returners_state - pred_shr_returners_state,
         )
# Import population weights
lt_cbsa <- read_csv(file.path(directory,"Data",specification,"local_ties_cbsa.csv"),col_select = -`...1`) %>%
  mutate(returners = (total *(return_col_only + return_hs_only + return_hs_col + no_ties))) %>%
  select(c(cbsa_code,returners))

# Merge into shapefile
data(county_laea)
diff_map = county_laea %>% 
  dplyr::left_join(unified_cbsa, by = c("GEOID"="GeoFIPS")) %>%
  group_by(cbsa_code) %>%
  dplyr::summarize(geometry = st_union(geometry)) %>%
  dplyr::left_join(differences_unfilt, by = "cbsa_code") %>%
  dplyr::left_join(lt_cbsa, by = "cbsa_code") %>%
  dplyr::filter(!is.na(returners)) %>%
  select(c(cbsa_code,geometry,difference_cbsa_alt,difference_state_alt,returners))

# NEED TO MERGE ON POPULATION WEIGHTS
diff_dorling <- cartogram_dorling(x = diff_map,
                                    weight = "returners",
                                    k = 1, itermax = 100)

ggplot(data = diff_dorling, aes(fill = difference_cbsa_alt)) +
  # Second layer: outlines of CBSAs for better location context
  geom_sf(data = diff_dorling, color = "gray", fill = NA, size = 0.3) +
  # First layer: the Dorling cartogram (colored circles)
  geom_sf(color = "gray30", size = 0.1, show.legend = FALSE) +  
  #geom_sf(data = net_cbsa_dorling, colour="gray", size=0.1) +
  #geom_sf(color = "grey30", size = 0.5,show.legend = TRUE) +
  scale_fill_gradientn(name = "Residual on\nLM Return",
                       labels = scales::percent,
                       colors = diverging_colors,
                       oob = scales::squish
    ) +
  labs(title = "Where Do College Graduates Return Despite Labor Demand?") +
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  guides(
    fill = guide_colorbar(
      barwidth = 10,  # Adjust width of the color bar (in lines or points)
      barheight = 0.5 # Adjust height of the color bar (in lines or points)
    )
  )

ggplot(diff_map, aes(fill = difference_cbsa_alt)) +
  geom_sf(show.legend = TRUE) +
  #facet_wrap(~ geo, ncol = 1) + # Facet for each level of inst_group
  scale_fill_gradientn(name = "Residual on\nLM Return",
                       labels = scales::percent,
                       colors = diverging_colors,
                       #oob = scales::squish,
                       #values = c(-1,-0.1,-0.05,-0.025,0,0.025,0.05,0.1,1),
                       #low = "#40004b",
                       #high = "#1b7837",
                       limits=c(-0.3,0.3),
    ) +
  labs(title = "Where College Graduates Return Despite Labor Demand?") +
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5))
ggsave(file = paste0(directory,"/Outputs/",specification,"/amenities.png"),
                 width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi) 
```



####    net_cbsa.png + net_cbsa_dorling.png

```{r prime age}

net_cbsa <- read_csv(file.path(directory,"Data",specification,"net_cbsa.csv"),col_select = -`...1`) %>%
  mutate(cbsa_code = str_pad(cbsa,width=5,side="left",pad="0")) %>%
  #select(-c("origin","destination","total_destination","net")) %>%
  #pivot_wider(names_from = "inst_group",
  #            values_from = "net_norm") %>%
    left_join(cbsa_li_crosswalk %>% dplyr::select(c(cbsa_code,cbsa_core)) %>% distinct(), by = "cbsa_code") %>%
  mutate(replacement_rate = destination/origin)

net_cbsa_map = county_laea %>% 
  dplyr::left_join(unified_cbsa, by = c("GEOID"="GeoFIPS")) %>%
  group_by(cbsa_code) %>%
  dplyr::summarize(geometry = st_union(geometry)) %>%
  dplyr::left_join(net_cbsa, by = "cbsa_code") %>%
  # Remove NAs since Dorling function doesn't accept NA weights
  filter(is.na(total_origin)==FALSE)

ggplot(data = net_cbsa_map, aes(fill = replacement_rate)) +
  geom_sf(data = net_cbsa_map, colour="gray", size=0.1) +
  scale_fill_gradientn(
    name = "Dest. Grads\nPer Orig.\nGrad  ",
    colors = diverging_colors,
    values = scales::rescale(c(0, 0.5, 1, 1.5, 2, 5)), # Define where colors are focused
    limits = c(0, 2),  # Set the visible range of the color scale
    oob = scales::squish  # Squish values outside the limits
  ) +
  labs(title = "Destination-to-Origin Ratio for College Graduates by Institutional Group") +
  facet_wrap(~ inst_group, ncol = 1) + # Facet for each level of inst_group
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  guides(
    fill = guide_colorbar(
      barwidth = 10,  # Adjust width of the color bar (in lines or points)
      barheight = 0.5 # Adjust height of the color bar (in lines or points)
    )
  )
ggsave(file = paste(directory,"/Outputs/",specification,"/net_cbsa.png",sep = ""),
         width = wid, height = 3*hei, units = unit, bg = bkgrnd, dpi = dpi)

# Create Dorling cartogram of prime-age coverage
dorling_rpu <- cartogram_dorling(x = net_cbsa_map %>% filter(inst_group == "RPU"),
                                    weight = "total_origin",
                                    k = 1, itermax = 100)
dorling_pf <- cartogram_dorling(x = net_cbsa_map %>% filter(inst_group == "PF"),
                                    weight = "total_origin",
                                    k = 1, itermax = 100)
dorling_private <- cartogram_dorling(x = net_cbsa_map %>% filter(inst_group == "Private, Non-Profit"),
                                    weight = "total_origin",
                                    k = 1, itermax = 100)
net_cbsa_dorling = rbind(dorling_rpu,dorling_pf,dorling_private)

ggplot(data = net_cbsa_dorling, aes(fill = replacement_rate)) +
  # Second layer: outlines of CBSAs for better location context
  geom_sf(data = net_cbsa_map, color = "gray", fill = NA, size = 0.3) +
  # First layer: the Dorling cartogram (colored circles)
  geom_sf(color = "gray30", size = 0.1, show.legend = FALSE) +  
  #geom_sf(data = net_cbsa_dorling, colour="gray", size=0.1) +
  #geom_sf(color = "grey30", size = 0.5,show.legend = TRUE) +
  scale_fill_gradientn(
    name = "Dest. Grads\nPer Orig.\nGrad  ",
    colors = diverging_colors,
    values = scales::rescale(c(0, 0.5, 1, 1.5, 2, 5)), # Define where colors are focused
    limits = c(0, 2),  # Set the visible range of the color scale
    oob = scales::squish  # Squish values outside the limits
  ) +
  labs(title = "Destination-to-Origin Ratio for College Graduates by Institutional Group") +
  facet_wrap(~ inst_group, ncol = 1) + # Facet for each level of inst_group
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  guides(
    fill = guide_colorbar(
      barwidth = 10,  # Adjust width of the color bar (in lines or points)
      barheight = 0.5 # Adjust height of the color bar (in lines or points)
    )
  )
ggsave(file = paste(directory,"/Outputs/",specification,"/net_cbsa_dorling.png",sep = ""),
         width = wid, height = 3*hei, units = unit, bg = bkgrnd, dpi = dpi)


```
####    net_state.png + net_state_dorling.png

```{r prime age}

net_state <- read_csv(file.path(directory,"Data",specification,"net_state.csv"),col_select = -`...1`) %>%
  #select(-c("origin","destination","total_destination","net")) %>%
  filter(state != "empty") %>% 
  # Add state FIPS codes to simplify spatial merges later
  left_join(cbsa %>% 
              separate_wider_delim(`CBSA Title`,delim = ", ", names = c("cbsa_city","state_abbr")) %>%
              rename(state_code = `FIPS State Code`) %>%
              dplyr::select(state_code,state_abbr) %>%
              filter(nchar(state_abbr)==2) %>%
              distinct(), by = c("state"="state_abbr")) %>%
  # Coerce DC FIPS code
  mutate(state_code = ifelse(is.na(state_code)==TRUE,11,state_code)) %>%
  mutate(replacement_rate = destination/origin)

net_state_map = county_laea %>% 
  dplyr::left_join(unified_cbsa, by = c("GEOID"="GeoFIPS")) %>%
  dplyr::mutate(state_code = substr(GEOID,start=1,stop=2)) %>%
  group_by(state_code) %>%
  dplyr::summarize(geometry = st_union(geometry)) %>%
  dplyr::left_join(net_state, by = "state_code") %>%
  # Remove NAs since Dorling function doesn't accept NA weights
  filter(is.na(total_origin)==FALSE)

ggplot(data = net_state_map, aes(fill = replacement_rate)) +
  geom_sf(data = net_state_map, colour="gray", size=0.1) +
scale_fill_gradientn(
    name = "Dest. Grads\nPer Orig.\nGrad  ",
    colors = diverging_colors,
    values = scales::rescale(c(0, 0.5, 1, 1.5, 2, 2.5)), # Define where colors are focused
    limits = c(0, 2),  # Set the visible range of the color scale
    oob = scales::squish  # Squish values outside the limits
  ) +
  labs(title = "Destination-to-Origin Ratio for College Graduates by Institutional Group") +
  facet_wrap(~ inst_group, ncol = 1) + # Facet for each level of inst_group
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  guides(
    fill = guide_colorbar(
      barwidth = 10,  # Adjust width of the color bar (in lines or points)
      barheight = 0.5 # Adjust height of the color bar (in lines or points)
    )
  )
ggsave(file = paste(directory,"/Outputs/",specification,"/net_state.png",sep = ""),
         width = wid, height = 3*hei, units = unit, bg = bkgrnd, dpi = dpi)

# Create Dorling cartogram of prime-age coverage
dorling_rpu <- cartogram_dorling(x = net_state_map %>% filter(inst_group == "RPU"),
                                    weight = "total_origin",
                                    k = 1, itermax = 100)
dorling_pf <- cartogram_dorling(x = net_state_map %>% filter(inst_group == "PF"),
                                    weight = "total_origin",
                                    k = 1, itermax = 100)
dorling_private <- cartogram_dorling(x = net_state_map %>% filter(inst_group == "Private, Non-Profit"),
                                    weight = "total_origin",
                                    k = 1, itermax = 100)
net_state_dorling = rbind(dorling_rpu,dorling_pf,dorling_private)

ggplot(data = net_state_dorling, aes(fill = replacement_rate)) +
  # Second layer: outlines of CBSAs for better location context
  geom_sf(data = net_state_map, color = "gray", fill = NA, size = 0.3) +
  # First layer: the Dorling cartogram (colored circles)
  geom_sf(color = "gray30", size = 0.1, show.legend = FALSE) +  
  #geom_sf(data = net_cbsa_dorling, colour="gray", size=0.1) +
  #geom_sf(color = "grey30", size = 0.5,show.legend = TRUE) +
  scale_fill_gradientn(
    name = "Dest. Grads\nPer Orig.\nGrad  ",
    colors = diverging_colors,
    values = scales::rescale(c(0, 0.5, 1, 1.5, 2, 2.5)), # Define where colors are focused
    limits = c(0, 2),  # Set the visible range of the color scale
    oob = scales::squish  # Squish values outside the limits
  ) +
  labs(title = "Destination-to-Origin Ratio for College Graduates by Institutional Group") +
  facet_wrap(~ inst_group, ncol = 1) + # Facet for each level of inst_group
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  guides(
    fill = guide_colorbar(
      barwidth = 10,  # Adjust width of the color bar (in lines or points)
      barheight = 0.5 # Adjust height of the color bar (in lines or points)
    )
  )
ggsave(file = paste(directory,"/Outputs/",specification,"/net_state_dorling.png",sep = ""),
         width = wid, height = 3*hei, units = unit, bg = bkgrnd, dpi = dpi)


```
####    net_cbsa_state

```{r prime age}

net_cbsa <- read_csv(file.path(directory,"Data",specification,"net_cbsa.csv"),col_select = -`...1`) %>%
  mutate(cbsa_code = str_pad(cbsa,width=5,side="left",pad="0")) %>%
  #select(-c("origin","destination","total_destination","net")) %>%
  #pivot_wider(names_from = "inst_group",
  #            values_from = "net_norm") %>%
    left_join(cbsa_li_crosswalk %>% dplyr::select(c("cbsa_code","cbsa_core")) %>% distinct(), by = "cbsa_code") %>%
  mutate(replacement_rate = destination/origin)

net_cbsa_map = county_laea %>% 
  dplyr::left_join(unified_cbsa, by = c("GEOID"="GeoFIPS")) %>%
  group_by(cbsa_code) %>%
  dplyr::summarize(geometry = st_union(geometry)) %>%
  dplyr::left_join(net_cbsa, by = "cbsa_code") %>%
  # Remove NAs since Dorling function doesn't accept NA weights
  filter(is.na(total_origin)==FALSE) %>%
  mutate(geo = "Labor Market")%>%
  dplyr::select(-c(cbsa,cbsa_code,cbsa_core))


net_state <- read_csv(file.path(directory,"Data",specification,"net_state.csv"),col_select = -`...1`) %>%
  #select(-c("origin","destination","total_destination","net")) %>%
  filter(state != "empty") %>% 
  # Add state FIPS codes to simplify spatial merges later
  left_join(cbsa %>% 
              separate_wider_delim(`CBSA Title`,delim = ", ", names = c("cbsa_city","state_abbr")) %>%
              rename(state_code = `FIPS State Code`) %>%
              dplyr::select(state_code,state_abbr) %>%
              filter(nchar(state_abbr)==2) %>%
              distinct(), by = c("state"="state_abbr")) %>%
  # Coerce DC FIPS code
  mutate(state_code = ifelse(is.na(state_code)==TRUE,11,state_code)) %>%
  mutate(replacement_rate = destination/origin)

net_state_map = county_laea %>% 
  dplyr::left_join(unified_cbsa, by = c("GEOID"="GeoFIPS")) %>%
  dplyr::mutate(state_code = substr(GEOID,start=1,stop=2)) %>%
  group_by(state_code) %>%
  dplyr::summarize(geometry = st_union(geometry)) %>%
  dplyr::left_join(net_state, by = "state_code") %>%
  # Remove NAs since Dorling function doesn't accept NA weights
  filter(is.na(total_origin)==FALSE) %>%
  mutate(geo = "State") %>%
  dplyr::select(-c(state,state_code))

net_cbsa_state = rbind(net_state_map,net_cbsa_map) %>%
  mutate(inst_group = case_when(inst_group == "Private, Non-Profit" ~ "Private",
                                TRUE ~ inst_group))

ggplot(data = net_cbsa_state, aes(fill = replacement_rate)) +
  geom_sf(data = net_cbsa_state, colour="gray", size=0.1) +
  scale_fill_gradientn(
    name = "Dest. Grads\nPer Orig.\nGrad  ",
    colors = diverging_colors,
    values = scales::rescale(c(0, 0.5, 1, 1.5, 2, 3.5)), # Define where colors are focused
    limits = c(0, 2.75),  # Set the visible range of the color scale
    oob = scales::squish  # Squish values outside the limits
  ) +
  labs(title = "Destination-to-Origin Ratio for College Graduates by Institutional Group") +
  facet_wrap(
    vars(inst_group, geo),  # Include both inst_group and geo for mapping
    ncol = 2,              # Two maps side by side per row
    labeller = labeller(geo = element_blank())  # Remove labels for geo
  ) + 
  theme_void() + 
  theme(text = element_text(size=12, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom",
        strip.background = element_blank(),               # Clean strip background
    panel.spacing = unit(1, "lines"),
        strip.text = element_text(size = 12, hjust = 0.5),
    strip.text.y = element_blank()) +
  guides(
    fill = guide_colorbar(
      barwidth = 20,  # Adjust width of the color bar (in lines or points)
      barheight = 0.5 # Adjust height of the color bar (in lines or points)
    )
  )
ggsave(file = paste(directory,"/Outputs/",specification,"/net_cbsa_state.png",sep = ""),
         width = wid, height = 3*hei, units = unit, bg = bkgrnd, dpi = dpi)
```


####    net_cbsa_state_dorling

```{r return-levels}

# Create Dorling cartogram of prime-age coverage
#dorling_rpu <- cartogram_dorling(x = net_cbsa_map %>% filter(inst_group == "RPU"),
#                                    weight = "total_origin",
#                                    k = 1, itermax = 100)
#dorling_pf <- cartogram_dorling(x = net_cbsa_map %>% filter(inst_group == "PF"),
#                                    weight = "total_origin",
#                                    k = 1, itermax = 100)
#dorling_private <- cartogram_dorling(x = net_cbsa_map %>% filter(inst_group == "Private, Non-Profit"),
#                                    weight = "total_origin",
#                                    k = 1, itermax = 100)
dorling_cbsa <- cartogram_dorling(x = net_cbsa_map,
                                    weight = "total_origin",
                                    k = 1, itermax = 100)
dorling_state <- cartogram_dorling(x = net_state_map,
                                    weight = "total_origin",
                                    k = 1, itermax = 100)

#net_cbsa_dorling = rbind(dorling_rpu,dorling_pf,dorling_private)
net_cbsa_state_dorling = rbind(dorling_cbsa,dorling_state)

ggplot(data = net_cbsa_state_dorling, aes(fill = shrunk_rate)) +
  # Second layer: outlines of CBSAs for better location context
  geom_sf(data = net_cbsa_map, color = "gray", fill = NA, size = 0.3) +
  # First layer: the Dorling cartogram (colored circles)
  geom_sf(color = "gray30", size = 0.1, show.legend = FALSE) +  
  #geom_sf(data = net_cbsa_dorling, colour="gray", size=0.1) +
  #geom_sf(color = "grey30", size = 0.5,show.legend = TRUE) +
  scale_fill_gradientn(
    name = "Dest. Grads\nPer Orig.\nGrad  ",
    colors = diverging_colors,
    values = scales::rescale(c(0, 0.5, 1, 1.5, 2, 5)), # Define where colors are focused
    limits = c(0, 2),  # Set the visible range of the color scale
    oob = scales::squish  # Squish values outside the limits
  ) +
  labs(title = "Destination-to-Origin Ratio for College Graduates by Institutional Group") +
  facet_wrap(
    vars(geo),  # Include both inst_group and geo for mapping
    ncol = 2,              # Two maps side by side per row
    labeller = labeller(geo = element_blank())  # Remove labels for geo
  ) + 
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  guides(
    fill = guide_colorbar(
      barwidth = 10,  # Adjust width of the color bar (in lines or points)
      barheight = 0.5 # Adjust height of the color bar (in lines or points)
    )
  )
ggsave(file = paste(directory,"/Outputs/",specification,"/net_cbsa_state_dorling.png",sep = ""),
         width = wid, height = 3*hei, units = unit, bg = bkgrnd, dpi = dpi)


```

###   Mapping Amenities

```{r differences}

differences <- read_csv(file.path(directory,"Data",specification,"local_differences.csv")) %>%
  mutate(cbsa_code = str_pad(hs_cbsa,width=5,side="left",pad="0")) %>%
  dplyr::select(-c("hs_cbsa","...1")) %>%
  left_join(cbsa_li_crosswalk %>% dplyr::select(c("cbsa_code","cbsa_core")) %>% distinct(), by = "cbsa_code") %>%
  mutate(difference_cbsa_alt = shr_returners_cbsa - pred_shr_returners_cbsa)

# Import population weights
lt_cbsa <- read_csv(file.path(directory,"Data",specification,"local_ties_cbsa.csv"),col_select = -`...1`) %>%
  mutate(returners = (total *(return_col_only + return_hs_only + return_hs_col + no_ties))) %>%
  dplyr::select(c(cbsa_code,returners))

# Merge into shapefile
data(county_laea)
diff_map = county_laea %>% 
  dplyr::left_join(unified_cbsa, by = c("GEOID"="GeoFIPS")) %>%
  group_by(cbsa_code) %>%
  dplyr::summarize(geometry = st_union(geometry)) %>%
  dplyr::left_join(differences, by = "cbsa_code") %>%
  dplyr::left_join(lt_cbsa, by = "cbsa_code") %>%
  #dplyr::filter(!is.na(returners)) %>%
  dplyr::select(c(cbsa_code,geometry,difference_cbsa_alt,returners))

# NEED TO MERGE ON POPULATION WEIGHTS
diff_dorling <- cartogram_dorling(x = diff_map,
                                    weight = "returners",
                                    k = 1, itermax = 100)

ggplot(data = diff_dorling, aes(fill = difference_cbsa_alt)) +
  # Second layer: outlines of CBSAs for better location context
  geom_sf(data = diff_dorling, color = "gray", fill = NA, size = 0.3) +
  # First layer: the Dorling cartogram (colored circles)
  geom_sf(color = "gray30", size = 0.1, show.legend = FALSE) +  
  #geom_sf(data = net_cbsa_dorling, colour="gray", size=0.1) +
  #geom_sf(color = "grey30", size = 0.5,show.legend = TRUE) +
  scale_fill_gradientn(name = "Residual on\nLM Return",
                       labels = scales::percent,
                       colors = diverging_colors,
                       oob = scales::squish
    ) +
  labs(title = "Where Do College Graduates Return Despite Labor Demand?") +
  theme_void() + 
  theme(text = element_text(size=10, family="LM Roman 10"),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  guides(
    fill = guide_colorbar(
      barwidth = 10,  # Adjust width of the color bar (in lines or points)
      barheight = 0.5 # Adjust height of the color bar (in lines or points)
    )
  )
ggsave(file = paste0(directory,"/Outputs/",specification,"/amenities.png"),
                 width = wid, height = hei, units = unit, bg = bkgrnd, dpi = dpi) 
```
