---
title: "01_import_nces"
author: "Nicholas Martens"
date: "2023-06-09"
output: html_document
---
This script imports institution-level characteristics on secondary and post-secondary institution from EDGE and IPEDS
Then it merges selectivity data with institutional data

## Setup

Import necessary packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(data.table)
```

Directories and filenames that change with machine
```{r directory, include=FALSE}
directory = "/nfs/turbo/lsa-areynoso"
#directory = "/Volumes/lsa-areynoso"

postfilename = "ipeds_hd2021.csv"
cbsafilename = "msa_2020.csv"
countyfilename = "counties.xlsx"
ctcountyfilename = "ct_counties.xlsx"
superopeidfilename = "mrc_table11.csv"
opeidunitidfilename = "CW2021.xlsx"

```

## Declaring Functions
Function used to compute mode of a dataset

```{r mode, include=FALSE}
Mode <- function(x, na.rm = TRUE)
{
  if(na.rm)
  {
    x = x[!is.na(x)]
  }
  ux <- unique(x)
  return(ux[which.max(tabulate(match(x,ux)))])
}
```

Declare %nin% so we can filter observations

```{r negate, include=FALSE}
`%nin%` = Negate(`%in%`)
```

## Import Files

```{r import, include=FALSE}
# Import SuperOPEID-OPEID Crosswalk from OI website
# https://opportunityinsights.org/data/ 
superope_ope_crosswalk = read_csv(file.path(directory,"Data/01/Crosswalks",superopeidfilename))

# Import OPEID-Unit ID Crosswalk from DOE
# https://collegescorecard.ed.gov/data/ 
ope_unit_crosswalk = read_excel(file.path(directory,"Data/01/Crosswalks",opeidunitidfilename), 
                                sheet = "Crosswalk")


# Import CBSA Conversion File
cbsa = read_csv(file.path(directory,"Data/01",cbsafilename),
                col_types = "cccccccccccc")

# Read in county list
raw_county = read_excel(file.path(directory,"Data/01",countyfilename)) %>%
  # Remove extraneous columns to simplify merge with ct_county
  dplyr::select(-c('Geo Point','Geo Shape','Year','Iso 3166-3 Area Code',"Type",'County GNIS Code','Official Name County')) %>%
  rename('state_code' = 'Official Code State',
         'state_name' = 'Official Name State',
         'GeoFIPS' = 'Official Code County',
         'county_name' = 'Name with legal/statistical area description',
         'county_code' = 'County FIPS Code') %>%
  # Remove new CT counties, which aren't used in any other data
  #filter(state_name != "CT") %>%
  # DC miscoded as part of Delaware in original data
  mutate(state_name = ifelse(county_name == "District of Columbia","DC",state_name)) %>%
  # In 2019, Alaska formed two Census areas from one
  # Add Chugach Census Area, Alaska (FIPS 02063) to 02261
  # Add Copper River, Alaska (FIPS 02066) to 02999
  mutate(GeoFIPS = case_when(GeoFIPS %in% c("02063","02066") ~ "02261",
                             #  Oglala Lakota County (formerly Shannon), 
                             #  South Dakota (FIPS 46102) to 46113
                             GeoFIPS == "46102" ~ "46113",
                             #  Kusilvak Census Area (formerly Wade Hampton),
                             #  Alaska (FIPS 0) to 02270
                             GeoFIPS == "02158" ~ "02270",
                             .default = GeoFIPS))


# Connecticut changed counties, so most data uses old boundaries
# Must append county dataset with old county codes
ct_county = read_excel(file.path(directory,"Data/01",ctcountyfilename)) %>%
  # Remove extraneous columns to simplify merge with county
  dplyr::select(-c('COUNTYNS','CLASSFP','FUNCSTAT')) %>%
  rename('state_code' = 'STATEFP',
         'state_name' = 'STATE',
         #'GeoFIPS' = 'Official Code County',
         'county_name' = 'COUNTYNAME',
         'county_code' = 'COUNTYFP') %>%
  mutate(GeoFIPS = paste0(state_code,county_code))
# Merge Connecticut and raw county data together
county = rbind(ct_county,raw_county)

## Creating Full County Name File
# Necessary for merging everything
# Create column combining county name and state abbreviation
county_full = county %>%
  mutate(full_name = paste0(county_name,", ",state_name)) %>%
  dplyr::select(c(GeoFIPS,full_name))

```

## String Cleaning
Cleaning strings on CBSA file
```{r cbsa string clean, include=FALSE}
# Pad FIPS county code
cbsa$`FIPS County Code` = str_pad(cbsa$`FIPS County Code`, width = 3, side = "left", pad = "0")
cbsa$`FIPS State Code` = str_pad(cbsa$`FIPS State Code`, width = 2, side = "left", pad = "0")
cbsa$`CBSA Code` = as.character(cbsa$`CBSA Code`)
```

## Creating Crosswalk of Codes
Unifying pseudo-CBSA and actual CBSAs
```{r crosswalk, include=FALSE}
# Paste state code 
cbsa_fips = cbsa %>%
  mutate(GeoFIPS = paste0(`FIPS State Code`,`FIPS County Code`)) %>%
  dplyr::select(c(`CBSA Code`,`GeoFIPS`)) %>%
  rename(cbsa_code = `CBSA Code`)

# Add Litchfield County to cbsa_na table to 09999
addendum = data.frame(GeoFIPS = c("09005"),
                      cbsa_code = c("09999"))

# Filter counties to only include counties outside of CBSAs
# Create psuedo-CBSA code for non-CBSA counties by adding "999" to the end
cbsa_na = county %>%
  mutate(noncbsa_code = paste0(county$state_code,"999")) %>%
  filter(GeoFIPS %nin% cbsa_fips$GeoFIPS) %>%
  # filter(is.na(cbsa_code)==TRUE) %>%
  mutate(cbsa_code = noncbsa_code) %>%
  dplyr::select(c(GeoFIPS,noncbsa_code)) %>%
  rename(cbsa_code = noncbsa_code)
  

# Join counties with CBSA codes and psuedo-coded non-CBSA counties
unified_cbsa = rbind(cbsa_fips,cbsa_na) %>%
  as.data.table()

write.csv(unified_cbsa,file.path(directory,"Data/01/unified_cbsa.csv"))

cbsa_code_name = cbsa[c(1,4)] %>%
  rename("cbsa_code" = `CBSA Code`,
         "cbsa_name" = `CBSA Title`) %>%
  distinct() %>%
  as.data.table()
unified_cbsa_name = unified_cbsa[cbsa_code_name, on = "cbsa_code"] 
```

##    Create Crosswalk of Name + Code

```{r}
# Create names, state, and code for non-metropolitan areas
nonmetros = cbsa %>% 
  separate_wider_delim(`CBSA Title`,delim = ", ", names = c("cbsa_city","state_abbr")) %>%
  rename(state_code = `FIPS State Code`) %>%
  dplyr::select(state_code,state_abbr) %>%
  filter(nchar(state_abbr)==2) %>%
  distinct() %>%
  mutate(cbsa_core = paste(state_abbr,"NONMETROPOLITAN AREA"),
         cbsa_state = state_abbr,
         cbsa_code = paste0(state_code,"999")) %>%
  dplyr::select(-starts_with("state_"))

# Extract name, state, and code for metorpolitan areas  
metros = unified_cbsa_name %>%
  #distinct(cbsa_code) %>%
  separate_wider_delim(cbsa_name, delim = ", ", names = c("cbsa_city","cbsa_state")) %>%
  separate_wider_delim(cbsa_state, delim = "-", 
                       names = c("cbsa_state1","cbsa_state","cbsa_state3","cbsa_state4"),
                       too_few = "align_start") %>%
  pivot_longer(cols = starts_with("cbsa_state"),
               names_to = "cbsa_state_n",
               values_to = "cbsa_state",
               values_drop_na = TRUE) %>%
  dplyr::select(-cbsa_state_n) %>%
  mutate(cbsa_core = str_replace(cbsa_city,"-.*","")) %>%
  dplyr::select(-c("GeoFIPS","cbsa_city")) %>%
  distinct()

# Merge birth_position to get codes for CBSAs
cbsa_li_crosswalk = rbind(metros,nonmetros)
```



##    Merge on OPEID and Unit ID

```{r institution crosswalk}

# Merge Super OPEID, OPEID, Unit ID, and system names together for easy matches
institution_crosswalk = ope_unit_crosswalk %>%
  dplyr::select(c("OPEID","IPEDSMatch","PEPSSchname","IPEDSInstnm","f1sysnam")) %>%
  distinct() %>%
  mutate(system_name = case_when(f1sysnam == "-2" ~ IPEDSInstnm,
                                 TRUE ~ f1sysnam),
         opeid = as.numeric(str_sub(OPEID,2,6))) %>%
  left_join(superope_ope_crosswalk, by = "opeid") %>%
  dplyr::select(-c("f1sysnam","institution_name","multi","superopeid_name")) %>%
  # Standardize spacing, punctuation removal, and decapitalization
  # Remove extra spaces and punctuation from institution names 
  mutate(system_name = str_trim(str_to_lower(str_replace_all(system_name, "[[:punct:]]", " "))),
         system_name = str_replace_all(system_name, "main campus", ""),
         clean_name1 = str_trim(str_to_lower(str_replace_all(PEPSSchname, "[[:punct:]]", " "))),
         clean_name1 = str_replace_all(clean_name1, "main campus", ""),
         clean_name2 = str_trim(str_to_lower(str_replace_all(IPEDSInstnm, "[[:punct:]]", " "))),
         clean_name2 = str_replace_all(clean_name2, "main campus", "")) %>%
  rename(unitid = IPEDSMatch) %>%
  dplyr::select(unitid,opeid,super_opeid,clean_name1,clean_name2,system_name)

# Crosswalk between unitids and super OPEids
unitid_super_opeid_crosswalk = institution_crosswalk %>% 
  dplyr::select(unitid,super_opeid) %>%
  mutate(unitid = as.integer(unitid)) %>%
  filter(super_opeid > 0) %>% 
  distinct()

# Create data.tables for merging based on different variations of institution names
name_crosswalk_1 = institution_crosswalk %>%
  distinct(clean_name1, .keep_all = TRUE)
name_crosswalk_2 = institution_crosswalk %>%
  distinct(clean_name2, .keep_all = TRUE)
name_crosswalk_3 = institution_crosswalk %>%
  distinct(system_name, .keep_all = TRUE)

```