---
title: "02_import_li_optimized"
author: "Nicholas Martens"
date: "2024-01-13"
output: html_document
---

## Setup

Directories and filenames that change with machine
```{r directory, include=FALSE}
library(dotenv)
library(here)
load_dot_env(here::here(".env"))
directory <- Sys.getenv("BRAIN_DRAIN_ROOT")  # kept for any Outputs/-only uses not touched by this reorg
data_dir  <- file.path(directory, "Data")
out_dir   <- file.path(directory, "Outputs")
edufilename1 = "raw_educ_STATES_AK-MD.csv"
edufilename1edit = "STATES_AK-MD.csv"
edufilename2 = "raw_educ_STATES_MI-WY.csv"
edutfilename2edit = "STATES_MI-WY.csv"
misfitscorrection = "misfits_correction.csv"
```

Import necessary packages
```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(stringi)
library(tidyverse)
library(table.express)
library(data.table)
```

Declare %nin% so we can filter observations

```{r negate, include=FALSE}
`%nin%` = Negate(`%in%`)
```

## Import and Clean Education File
Import raw education file from LinkedIN
Complete basic string cleaning like removing dashes and making lowercase

```{r import, echo=FALSE}
# Remove problematic rows
#x1 = readLines(file.path(data_dir,"raw/revelio/raw_educ_STATES_AK-MD.csv"))
#x1_edit = x1[-c(11891030)]
#x1_df = read.table(x1_edit[1:5])
#  stringi::stri_split_fixed(x1_edit[1:5],","))
#STATES_MI-WY.csv

ed_li1 = read_delim(file.path(data_dir,"raw/revelio/raw_educ_STATES_AK-MD.csv"))
ed_li2 = read_delim(file.path(data_dir,"raw/revelio/raw_educ_STATES_MI-WY.csv"))

#ed_li1 = fread(file.path(data_dir,"raw/revelio/raw_educ_STATES_AK-MD.csv"),
#              drop = c('world_rank'))
              #select = c("user_id","educ_startdate","educ_enddate",
              #         "university_name","degree","field",
              #         "university_country","alt_name"),
#              sep = ",")


#ed_li2 = fread(file.path(data_dir,"raw/revelio/raw_educ_STATES_MI-WY.csv"),
 #             drop = c('world_rank'),
#              fill=TRUE,
#              sep = ",")

ed_li = rbind(ed_li1,ed_li2) %>% select(-c(world_rank)) %>% as.data.table()
rm(ed_li2,ed_li1)
# Remove redundant intermediate objects to save memory
# Filter out associates degrees
ed_li = ed_li[degree != "Associate"]
# Filter universities outside US
# Simplifies encoding by removing institutions with foreign accents
ed_li = ed_li[university_country %in% c("United States","\\N")]
# I convert to ASCII because it avoids headaches associated with non-English characters
# Since my analysis focuses on American educational institutions,
# foreign names are not very prevalent
ed_li$university_name = iconv(ed_li$university_name, from = "UTF-8", to = "ASCII", sub = "")

# Remove extra spaces and punctuation from institution names
ed_li = ed_li[, alt_name := str_trim(str_to_lower(gsub("[[:punct:]]"," ",university_name)))]
# Remove observations with empty institution name
ed_li = ed_li[-which(ed_li$alt_name == ""), ]
# Remove "main campus" to improve matches
ed_li = ed_li[, alt_name := gsub("main campus","",alt_name)]

ed_li_sample = ed_li %>%
  sample_frac(0.01)

clean_university_names <- function(name) 
{
  #name <- gsub("\\bat\\b", "",name,ignore.case = TRUE)
  # Remove everything after "University of [name]" or "[name] State University"
  # if "college", "school", "department", or "division" appear after
  contains_keywords <- grepl("college|school|department|division", name, ignore.case = TRUE)
  # Pattern to identify if the string contains "college", "school", "department", or "division"
  if (contains_keywords) {
    # Remove all text after "University of [name]" or "[name] State University"
    name <- sub("^(University of [^ ]+).*", "\\1", name, ignore.case = TRUE)
    name <- sub("([^ ]+ State University).*", "\\1", name, ignore.case = TRUE)
    name <- sub("([^ ]+ University).*", "\\1", name, ignore.case = TRUE)
  }
  
  # Next remove any instances of colleges at universities
  # Deletes any word up to "at" if the string includes "college" prior
  # to "at" and "university" after
  # Example: College of Engineering at Western Michigan University 
  pattern_1 <- "(?i)college\\s+.*?\\bat\\b\\s+.*\\buniversity\\b"
  
  # Check if the input_string matches the pattern
  #if (str_detect(name, pattern_1)) {
    # Remove any words before and including "at"
  #  name <- str_replace(name, "^.*?\\bat\\b\\s*", "")
  #}
  
  return(trimws(name)) # Trim any trailing whitespace
}

# Apply the cleaning function to the alt_name column
#ed_li_sample[, clean_name := sapply(alt_name,clean_university_names)]



```


## Consolidated and Simplified

```{r col split, echo=FALSE}

hs_match = ed_li[all_hs, on = "alt_name"]
# Identify all LI entries that aren't high schools
not_hs = ed_li[!all_hs, on = "alt_name"]

# Count incidences of different alt_name strings
name_counts <- not_hs[, .N, by = alt_name]

# Filter observations with more than 100 occurrences
frequent_names <- name_counts[N > 3]

# Clean the filtered alt_name strings
frequent_names[, clean_name := sapply(alt_name, clean_university_names)]

# Merge the cleaned names back with the original dataset
not_hs <- merge(not_hs, frequent_names[, .(alt_name, clean_name)], by = "alt_name", all.x = TRUE)

# Replace original alt_name with cleaned names where available
not_hs[, clean_name := ifelse(is.na(clean_name), alt_name, clean_name)]

# Step 1: Merge on clean_name1
merged1 <- merge(not_hs, name_crosswalk_1, by.x = "clean_name", by.y = "clean_name1", all.x = TRUE)
merged1[, c("clean_name2","system_name") := NULL]

# Remove duplicate columns to keep merges clean
merged2 = merged1[is.na(unitid)]
merged2[, c("unitid","opeid","super_opeid") := NULL]
# Step 2: Merge remaining unmatched rows on clean_name2
merged2 <- merge(merged2, name_crosswalk_2, by.x = "clean_name", by.y = "clean_name2", all.x = TRUE)
merged2[, c("clean_name1","system_name") := NULL]

# Combine matched rows from first merge with new matched rows
col_match <- rbind(merged1[!is.na(unitid)], merged2, fill = TRUE)
rm(merged1)

# Identify rows with missing data
misfits <- rbind(col_match[is.na(unitid)], merged2[is.na(unitid)], fill = TRUE)
# Combine all matched rows
col_match <- rbind(col_match[!is.na(unitid)], merged2[!is.na(unitid)], fill = TRUE)

# Counts missing institution names
misfit_counts <- misfits[, .N, by = alt_name] %>%
  filter(N > 50)
write.csv(misfit_counts, file.path(data_dir,"intermediate/misfits_3.csv"))

# Upload manual correction of some large institutions
# Potential expansion possible
misfits_correction <- read_delim(file.path(data_dir,"intermediate/misfits_correction.csv")) %>%
  mutate(opeid = as.numeric(str_sub(opeid,2,6))) %>%
  filter(is.na(opeid) == FALSE) %>%
  distinct(alt_name,unitid,opeid) %>%
  left_join(superope_ope_crosswalk, by = "opeid") %>%
  select(-c("institution_name","superopeid_name","multi"))

# Remove columns to simplify merge
misfits[, c("unitid","opeid","super_opeid") := NULL]
misfits <- misfits[alt_name %in% misfits_correction$alt_name]

# Merge with corrections
#misfits <- misfits[-which(is.na(misfits$alt_name)), ]
misfits <- merge(misfits, misfits_correction, by.x = "alt_name", by.y = "alt_name", all.x = TRUE)
col_match <- rbind(col_match[!is.na(unitid)],misfits[!is.na(unitid)])

# Remove duplicate columns to keep merges clean
merged3 = misfits[is.na(unitid)]
merged3[, c("unitid","opeid","super_opeid") := NULL]
# Step 3: Merge remaining unmatched rows on system_name
merged3 <- merge(merged3, name_crosswalk_3, by.x = "alt_name", by.y = "system_name", all.x = TRUE)
merged3[, c("clean_name1","clean_name2") := NULL]

col_match <- rbind(col_match[!is.na(unitid)],merged3[!is.na(unitid)])
rm(misfits,misfits_correction)

# Count the most common universities as a sanity check
inst_counts <- col_match[, .N, by = unitid] 
inst_counts <- merge(inst_counts,name_crosswalk_1, by.x = "unitid", by.y = "unitid", all.x = FALSE)
write.csv(inst_counts,file.path(data_dir,"intermediate/inst_counts.csv"))
```


##    Improve High School Matches

```{r}

replacements <- c("junior" = "", "senior" = "", "middle" = "", "jrsr" = "","the" = "",
                  "high" = "", "hs" = "", "school" = "", "h s" = "", "city" = "")

# Extract stripped high school names
nces_alt_name = all_hs %>%
  mutate(stripped_name1 = str_replace_all(alt_name, replacements)) %>%
  mutate(stripped_name2 = str_replace_all(stripped_name1, "\\s{2,}", " "))

# Extract alt_names matched with an alt_name
college_names = unique(col_match$alt_name)

# Extract unique high school names in LinkedIn data
li_alt_name = frequent_names %>%
  filter(!clean_name %in% college_names) %>%
  mutate(stripped_name1 = str_replace_all(alt_name, replacements)) %>%
  mutate(stripped_name2 = str_replace_all(stripped_name1, "\\s{2,}", " ")) %>%
  # Filter to only include stripped_names that appear in the NCES
  filter(stripped_name2 %in% nces_alt_name$stripped_name2)

duplicated_hs <- all_hs[duplicated(stripped_name2) | duplicated(stripped_name2, fromLast = TRUE)]


stripped_hs = li_alt_name[,c("alt_name","stripped_name2")] 

# Added stripped name to still_hs and hs_match
# This merge should be on stripped_name2?
still_hs = not_hs[stripped_hs, on = "alt_name"]


#hs_match = stripped_hs[hs_match, on = "alt_name"]
rm(merged2,merged3)

```

##    Finding Users with Both HS and Col

```{r obs}

# Extract user IDs for people listing baccalaureate institution on LI
col_users = col_match %>% table.express::select(user_id)

hs_match <- hs_match[,c("user_id","educ_startdate","educ_enddate","university_name",
                       "degree","field","university_country","clean_name","stripped_name2","alt_name")]
#setnames(hs_match, old = "i.stripped_name2", new = "stripped_name2")
hs_match <- rbind(hs_match,still_hs)
# Extract user IDs for people listing high school on LI
hs_users = hs_match %>% table.express::select(user_id)

# Create list of people listing both high school and baccalaureate institutions
# Wait on creating both until data extracted from position file
both = as.data.table(intersect(col_users$user_id,hs_users$user_id)) %>%
  setnames("V1","user_id")

# Find users with multiple baccalaureate institutions
transfer = both[col_match, on = "user_id"] %>%
  # Remove users who listed the same baccalaureate institution twice
  distinct(user_id,alt_name)

# Create list of users with multiple users
transfer = transfer[, .(count = .N), by = user_id] %>%
  table.express::filter(count > 1)

# Remove extra column
transfer = transfer[,c("count"):=NULL]

transfer = intersect(both$user_id,transfer$user_id)

rm(ed_li,not_hs)
gc()
```

##    Measurements for Observation Accounting

```{r obs}

col_users_length = length(unique(col_users$user_id))
both_hs_col_length = length(unique(both$user_id))

```
