---
title: "03_ed_pos_optimized"
author: "Nicholas Martens"
date: "2024-01-05"
output: html_document
---

# Setup

Directories and filenames that change with machine
```{r directory, include=FALSE}

library(dotenv)
library(here)
load_dot_env(here::here(".env"))
directory <- Sys.getenv("BRAIN_DRAIN_ROOT")  # kept for any Outputs/-only uses not touched by this reorg
data_dir  <- file.path(directory, "Data")
out_dir   <- file.path(directory, "Outputs")
posfilename1 = "cleaned_pos_educ_STATES_AK-MD.csv"
posfilename2 = "cleaned_pos_educ_STATES_MI-WY.csv"
posfilename3 = "cleaned_pos_educ_sample.csv"
msastringfilename = "msa_string_cleaning.csv"
zipcodefilename = "zipcodes.csv"

# Variables user can control
# Time range for work history
work_history_start = 1975
work_history_end = 2023
# Number of years after college graduation to include in data
max_post_grad = 50
min_post_grad = 0

```

Import necessary packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(educationdata)
#library(zipcodeR)
library(geodist)
library(stringi)
library(data.table)
```

##    Import Position File
fread is faster and more effective for large .csv files
```{r pos import, include=FALSE}
pos1 = fread(file.path(data_dir,"raw/revelio/cleaned_pos_educ_STATES_AK-MD.csv"),
            # Only important columns necessary to know where people live
            # In the future, maybe I will look more at occupations
            select = c('user_id','country','state','msa','startdate','enddate','seniority',
                       'company_cleaned','mapped_role','role_k1000','onet_code','onet_title'))
pos2 = fread(file.path(data_dir,"raw/revelio/cleaned_pos_educ_STATES_MI-WY.csv"),
            # Only important columns necessary to know where people live
            # In the future, maybe I will look more at occupations
            select = c('user_id','country','state','msa','startdate','enddate','seniority',
                       'company_cleaned','mapped_role','role_k1000','onet_code','onet_title'))
pos = rbind(pos1,pos2)
rm(pos1,pos2)
gc()

```

##    Trim Position File
Remove extra columns
Compute number of unique users represented in file with pos_keys
```{r pos trim, include=FALSE}

# Match position file to users with high school and college degrees
position = both[pos, on = "user_id", nomatch = NULL] %>%
  table.express::filter(country == "United States") %>%
  table.express::mutate(user_id = as.character(user_id))

full_position = col_users[pos, on = "user_id", nomatch = NULL, allow.cartesian = TRUE] %>%
  table.express::filter(country == "United States") %>%
  table.express::mutate(user_id = as.character(user_id))


# Remove redundant intermediate objects to save memory
rm(pos)  
gc()

# Used to make figures; counts ONET codes 
pos_summary <- position[, .(n = .N), by = .(onet_code, onet_title)] %>%
  as.data.frame() %>%
  mutate(shr_li = n/sum(n)) %>%
  mutate(socp = sub("\\..*$", "",onet_code)) %>%
  select(-c("onet_code","n","onet_title")) %>%
  group_by(socp) %>%
  summarize(shr_li = sum(shr_li))

write.csv(pos_summary,file.path(data_dir,"intermediate/soc_li_distribution.csv"))

```


##    Filtering to Include HS + College

[CHANGED 2026-07-25 -- Phase 1 wiring] col_match/hs_match now come from
both_final.rds (see 03_li_ed.Rmd) and are already one row per user with
final column names -- the old setnames()-based merge is no longer needed.

```{r filter, include=FALSE}
merge_col_hs = col_match[hs_match, on = "user_id", nomatch = NULL] %>%
  table.express::filter(is.na(col_name)==FALSE) %>%
  table.express::mutate(col_length = col_end - col_start)

rm(col_match,hs_match,hs_users)
gc()
```

##   Transfer Student Dummy

[CHANGED 2026-07-25 -- Phase 1 wiring] merge_col_hs is already one row per
user (both_final.rds enforces this), so the old multi-row aggregation
(summing col_length across institutions, picking the latest/earliest
record) no longer applies -- ba_transfer_* fields already carry that
information on the same row. This just adds the transfer indicator.

```{r merge hs col, include=FALSE}
merge_col_hs = merge_col_hs %>%
  table.express::mutate(transfer = as.integer(user_id %in% transfer)) %>%
  table.express::filter(is.na(col_name)==FALSE)
```

##    Extract Earliest Job

```{r earliest job, include=FALSE}

# Transform position file into wide data
# To start, we only need to know the earliest latest start dates
# For users with no graduation date we can use it to estimate graduation year
#work_latest = position[position[, .I[which.max(enddate)], by=user_id]$V1]
#work_latest = work_latest[,c("user_id","enddate")] 
work_earliest = position[position[, .I[which.min(startdate)], by=user_id]$V1]
work_earliest = work_earliest[,c("user_id","startdate")] %>%
  table.express::mutate(user_id = as.integer(user_id))

merge_col_hs = merge_col_hs[work_earliest, on = "user_id"] %>%
  setnames(c("startdate"),
           c("work_start"))

# Obtain list of college zip codes from IPEDS
inst_zip <- get_education_data(
    level = "college-university",
    source = "ipeds",
    topic = "directory",
    filters = list(year = 2021),
    add_labels = TRUE) %>%
  select(c("unitid","zip")) %>%
  mutate(col_zip = str_extract(zip, "^.{5}"),
         unitid = as.character(unitid))

merge_col_hs <- merge(merge_col_hs, inst_zip, by.x = "col_unitid", by.y = "unitid", all.x = TRUE)


#work_extent = work_earliest[work_latest, on = "user_id"]

#rm(work_latest,work_earliest)
```
##    Selecting Correct High School CBSA

[REMOVED 2026-07-25 -- Phase 1 wiring] This distance/haversine-based
disambiguation resolved ambiguous high-school names by picking the
geographically nearest candidate to the matched college -- a heuristic the
user identified as injecting measurement error by implying a spurious
linear relationship between college and high-school distance. hs_id/hs_cbsa
are now already resolved upstream in hs_match (03_li_ed.Rmd), via
04_col_hs_construct.R's IPEDS-probabilistic method (weighting candidates by
each college's actual state-of-residence distribution, not raw distance),
so no further disambiguation is needed here.

##    Calculating Birth Year

```{r birth year, include=FALSE}
# Convert graduation and start years from character to numeric
merge_col_hs$col_start = as.numeric(merge_col_hs$col_start)
merge_col_hs$col_end = as.numeric(merge_col_hs$col_end)
merge_col_hs$hs_end = as.numeric(merge_col_hs$hs_end)

# Calculating birth date based on high school graduation if available, 
# then college start date, then college graduation if the first two aren't available
# finally work start date if the other three are unavailable
merge_col_hs = merge_col_hs %>%
  table.express::mutate(birth1 = ifelse(is.na(hs_end)==FALSE, hs_end - 18,0),
                        birth2 = ifelse(is.na(col_start)==FALSE, col_start - 18,0),
                        birth3 = ifelse(is.na(col_end)==FALSE, col_end - 22,0),
                        # Use work history if no dates provided 
                        birth4 = ifelse(is.na(work_start)==FALSE,
                                        year(work_start)-22,0)) %>%
  table.express::mutate(birth = ifelse(birth1 > 0, birth1,
                                       ifelse(birth2 > 0, birth2,
                                              ifelse(birth3 > 0, birth3,
                                                     ifelse(birth4 > 0, birth4,0))))) %>%
  # Use estimated birth years to fill in missing graduation or start dates
  table.express::mutate(col_end = ifelse(is.na(col_end)==FALSE, col_end, birth + 22))

#merge_col_hs[,c("birth1","birth2","birth3","birth4") := NULL]
```

##    Checking for Position in nth Year
Creates binary variable with a 1 if LI profile includes a position within nth year
```{r return binary, include=FALSE}

position[, user_id := as.integer(user_id)]

# Merge education and position files
birth_position = merge_col_hs[position, on = "user_id", allow.cartesian = TRUE] %>%
  setnames(c("state"),c("cbsa_state")) %>%
  table.express::mutate(startdate = as.character(startdate),
                        enddate = as.character(enddate)) %>%
  # If no end date listed, make it date Ian finished pulling data in July 2023
  table.express::mutate(enddate = ifelse(is.na(enddate)==TRUE,"2023-07-17",enddate)) %>%
  table.express::mutate(cbsa_core = str_replace(msa,"-.*","")) %>%
  table.express::mutate(cbsa_core = str_replace_all(cbsa_core," [A-Z]{2} MSA$| MSA$","")) %>%
  table.express::mutate(cbsa_core = str_replace_all(cbsa_core," [A-Z]{2}$", ""))

msa = table(birth_position$msa)
cbsa_core = table(birth_position$cbsa_core)

  #table.express::mutate(cbsa_city = str_extract(cbsa_clean,'(^.{1,}-(?=([A-Z][a-z].*)))|(^.{1,} (?=([A-Z][A-Z].*)))')) %>%
  #table.express::mutate(cbsa_city = str_replace_all(cbsa_city, '-'," "))

# Import list of string corrections to ease merge with CBSA file
string_cleaning = fread(file.path(data_dir,"intermediate/msa_string_cleaning.csv"))
patterns = string_cleaning$Lookup
replacements = string_cleaning$Rename

# Make replacements on birth_position
birth_position = birth_position[, cbsa_core := stri_replace_all_fixed(cbsa_core, patterns, replacements, vectorize_all=FALSE)]

#unique_in_both <- unique(birth_position$user_id[birth_position$user_id %in% both$user_id])
#in_both_count <- length(unique_in_both)
#na_in_both_count <- sum(birth_position$user_id %i% both & !is.na(birth_position$col_name))

li_core = unique(birth_position$cbsa_core)

rm(string_cleaning,patterns,replacements)
gc()

#birth_position_sample = birth_position[sample(.N,10000)]
birth_position = merge(birth_position,cbsa_li_crosswalk, by = c("cbsa_core","cbsa_state"), all.x = TRUE)  %>%
  table.express::filter(!is.na(col_name) & msa != "empty")
gc()

no_work_location = length(unique(birth_position$user_id))

non_chronological_work = birth_position %>% 
  # Convert start and end dates to data.table's date format
  mutate(startdate = as.IDate(startdate)) %>%
  # Remove observations with no startdate
  filter(is.na(startdate)==FALSE)

no_work_date = non_chronological_work %>%
  # Filter out jobs where end date precedes start_date
  mutate(weird = ifelse((startdate <= enddate)==TRUE,0,1)) %>%
  #mutate(num_cbsa = as.numeric(cbsa_code)) %>%
  filter(weird == 0)

non_chronological_work = length(unique(non_chronological_work$user_id))
no_work_date = length(unique(no_work_date$user_id))
gc()

birth_position = birth_position %>% 
  #filter(col_name == "Jackson College") %>%
  # Convert start and end dates to data.table's date format
  table.express::mutate(startdate = as.IDate(startdate),
         enddate = as.IDate(enddate)) %>%
  # Remove observations with no startdate
  table.express::filter(is.na(startdate)==FALSE) %>%
  # Filter out jobs where end date precedes start_date
  #table.express::mutate(weird = ifelse(,0,1)) %>%
  #mutate(num_cbsa = as.numeric(cbsa_code)) %>%
  table.express::filter((startdate <= enddate)==TRUE)

startdate_before_enddate = length(unique(birth_position$user_id))
# Since the next steps are among the most memory-intensive in the entire codebase
# Remove some particularly large objects that aren't necessary
rm(still_hs,work_earliest,full_position,ed_li_sample,position)
gc()

# Create list of non-overlapping intervals representing year between the start
# and end defined by the user
start = ymd(rep(work_history_start:work_history_end),truncated=2L)
end = start + years(1) - days(1)
interval = year(start)
work_hist = data.table(interval = interval,
                       start = as.IDate(start),
                       end = as.IDate(end))

# Standardizing time intervals on LI profiles as years since college graduation
# Reference list (just intervals from Jan 1 to Dec 31 of every year)
setkey(work_hist, start, end)
# Detecting overlaps
std_pos = foverlaps(birth_position,
                work_hist,
                by.x=c("startdate","enddate"),
                by.y=c("start","end"),
                type = "any") %>%
  # Converting overlaps into years since graduation
  table.express::mutate(yrs_graduated = interval - col_end) %>%
  # Removing jobs prior to college graduation
  # Approximately 15 percent of users only list jobs prior to their college graduation
  table.express::filter(min_post_grad <= yrs_graduated  & yrs_graduated <= max_post_grad)

#rm(work_history_start,work_history_end,interval,work_hist,start,end)
gc()

# If multiple jobs listed, selects the most common CBSA for employment
std_pos_geo = dcast(std_pos, user_id ~ yrs_graduated, 
             value.var = c("cbsa_code","cbsa_state"),
             fun.aggregate = function(x, na.rm = TRUE)
               {
               if(na.rm)
                 {
                 x = x[!is.na(x)]
                 }
               ux <- unique(x)
               return(ux[which.max(tabulate(match(x,ux)))])
               })
std_pos_soc = dcast(std_pos, user_id ~ yrs_graduated, 
             value.var = c("onet_code"),
             fun.aggregate = function(x, na.rm = TRUE)
               {
               if(na.rm)
                 {
                 x = x[!is.na(x)]
                 }
               ux <- unique(x)
               return(ux[which.max(tabulate(match(x,ux)))])
               })


almost_completed = merge_col_hs[std_pos_geo, on = "user_id",all=TRUE]
almost_completed = almost_completed[std_pos_soc, on = "user_id", all = TRUE]

# Calculate number of merges for observation accounting
no_work_hist = length(unique(almost_completed$user_id))

# Get states for all colleges
col_state <- get_education_data(
    level = "college-university",
    source = "ipeds",
    topic = "directory",
    filters = list(year = 2021),
    add_labels = TRUE) %>%
  select(c("unitid","state_abbr")) %>%
  mutate(unitid = as.character(unitid)) %>%
  rename(col_state = state_abbr)

completed = almost_completed %>% 
  # Filter out remaining incomplete observations (3% of mass)
  table.express::filter(is.na(col_name)==FALSE)

completed <- merge(completed, col_state, by.x = "col_unitid", by.y = "unitid", all.x = TRUE)

# Filter out users with multiple entries
completed <- completed[, .SD[which.min(col_end)], by = "user_id"]

college_dne = length(unique(completed$user_id))

# Should not be necessary if properly filtered
#extra_cols = c(paste("cbsa_code",c(-577:-1,51:123),sep = "_"),paste("cbsa_state",c(-577:-1,51:123),sep = "_"),c(-577:-1,51:123),"NA")
#new_names = c("user_id","col_unitid",names(almost_completed)[3:24],paste0("cbsa_code_",0:50),paste0("cbsa_state_",0:50),paste0("soc_code_",0:50),"col_state")

setnames(completed, old = as.character(c(0:50)), new = paste0("soc_code_",0:50))

rm(std_pos_geo,std_pos,birth_position)
gc()
```
##    Calculate Users per Year x CBSA

```{r numerator, include=FALSE}

cols = c("user_id","col_end","birth","hs_state","col_state",paste0("cbsa_code_",min_post_grad:max_post_grad))
completed_melt = completed[, ..cols] %>%
    table.express::filter(col_end > 1981 & col_end < 2023 & birth > 1929 & birth > 1929 & birth < 2003) %>%
  table.express::filter(!hs_state %in% c("GU","PR","AS","VI")) %>%
  table.express::filter(!col_state %in% c("GU","PR","AS","VI")) %>%
  table.express::mutate_sd(c("col_end","birth","hs_state","col_state"),NULL) %>%
  melt(id=c("user_id"), na.rm=TRUE)
  
numerator = completed_melt[, .(count = .N), by = c("value","variable")]

write.csv(numerator,file.path(data_dir,"intermediate/numerator.csv"))
write.csv(completed,file.path(data_dir,"raw/revelio/raw_microdata__05.csv"))


rm(position,all_col_unrated,almost_completed,barrons,barrons_chetty,big_chungus,both,
   cbsa_fips,cbsa_na,cbsa_code_name,chetty,chetty_raw,col_users,completed_neither,
   ed_li,full_position,merge_col_hs,not_hs,position,postsec,private,private_hs,
   public,public_hs,raw_county,tiered_barrons,tiered_chetty,transfer,unified_cbsa_name,
   unoriginal_hs,work_earliest)
gc()
```

