---
title: "final_merge"
author: "Nicholas Martens"
date: "2024-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(educationdata)
library(tidyverse)
library(table.express)
library(data.table)
```
##    Setup
Directories and filenames that change with machine
```{r directory, include=FALSE}

directory = "/nfs/turbo/lsa-areynoso"
#directory = "/Volumes/lsa-areynoso"
zipcodefilename = "zipcodes.csv"
# Choose a base year (e.g., 2020) for CPI
cpi_base_year <- 2020

min_post_grad = 0
max_post_grad = 50

```

##    Import LI Microdata
```{r}

# Import microdata file if not loaded already
if(!exists("completed"))
{
  raw_microdata = fread(file.path(directory,"Data/05/raw_microdata.csv"),
                  colClasses = c("col_zip" = "character",
                                 "hs_cnty"= "character"
                                 ))
}
if(exists("completed"))
{
  raw_microdata = completed
}
```

#    Standardize CBSAs
With this code chunk, CBSA classifications can be changed by rerunning steps 1 and 4
```{r pos import, include=FALSE}

raw_microdata[,col_unitid := as.integer(col_unitid)]
# Pull directory of basic information about institutions
col_cbsas = get_education_data(level = "college-university",
                                   source = "ipeds",
                                   topic = "directory",
                                   filters = list(year = 2021)
                   ) %>%
  select(c(unitid,county_fips)) %>%
  mutate(col_cnty = as.character(str_pad(county_fips,5,"left","0"))) %>%
  rename(col_unitid = unitid)

raw_microdata <- merge(raw_microdata,col_cbsas, by="col_unitid")
raw_microdata <- merge(raw_microdata,unified_cbsa, by.x ="col_cnty", by.y = "GeoFIPS") %>%
  setnames(c("cbsa_code"),c("col_cbsa_code"))
raw_microdata <- merge(raw_microdata,unified_cbsa, by.x ="hs_cnty", by.y = "GeoFIPS") %>%
  setnames(c("cbsa_code"),c("hs_cbsa_code"))

```

##      Mode Computation

```{r occp-mode}

# Define a helper function to calculate the mode
get_mode <- function(x) {
  x <- x[!is.na(x)]
  if (length(x) == 0) return(NA)
  unique_x <- unique(x)
  unique_x[which.max(tabulate(match(x, unique_x)))]
}

# Select the columns and apply the mode function across rows
raw_microdata[, soc_code_mode := apply(.SD, 1, get_mode), .SDcols = paste0("soc_code_", as.character(c(min_post_grad:max_post_grad)))]
raw_microdata[, cbsa_mode := apply(.SD, 1, get_mode), .SDcols = paste0("cbsa_code_", as.character(c(min_post_grad:max_post_grad)))]
raw_microdata[, state_mode := apply(.SD, 1, get_mode), .SDcols = paste0("cbsa_state_", as.character(c(min_post_grad:max_post_grad)))]


```

##      Cumulative Return for CBSA + State

```{r occp-mode, eval=FALSE}

# Import occupational prestige crosswalk created in step 8
occp_prestige <- fread(file.path(directory,"Data","occupational_prestige.csv")) %>%
  as.data.frame() %>%
  distinct(socp_raw, .keep_all = TRUE) %>%
  select(socp_raw,prestige_bin)

raw_microdata <- merge(raw_microdata,occp_prestige,by.x="soc_code_mode",by.y="socp_raw")

# Initialize an empty data.table to store results
return_cbsa <- data.table()
return_state <- data.table()

# Loop over years since graduation (0 to 50)
for (year in min_post_grad:max_post_grad) {
  print(paste("Currently on",year))
  # Dynamically construct the column name for the current year
  col_name <- paste0("cbsa_code_", year)
  cum_cols <- paste0("cbsa_code_",min_post_grad:year)
  
  # Calculate the share returning to hs_cbsa for this year
  stock <- raw_microdata[
    , .(shr_return_cbsa = mean(.SD[[1]] == hs_cbsa, na.rm = TRUE)), 
    by = .(col_unitid,prestige_bin),
    .SDcols = col_name
  ]
  cumulative <- raw_microdata[
    , .(shr_ever_return_cbsa = mean(rowSums(.SD == hs_cbsa, na.rm = TRUE) > 0)), 
    by = .(col_unitid,prestige_bin),
    .SDcols = cum_cols
  ]
  
  # Add the current year since graduation to the result
  stock[, years := year]
  cumulative[, years := year]
  return_cbsa_temp <- merge(stock,cumulative,by = c("col_unitid","years","prestige_bin"))
  
  # Append to the results data.table
  return_cbsa <- rbind(return_cbsa, return_cbsa_temp, use.names = TRUE, fill = TRUE)
}

# Loop over years since graduation (0 to 50)
for (year in min_post_grad:max_post_grad) {
  print(paste("Currently on",year))
  # Dynamically construct the column name for the current year
  col_name <- paste0("cbsa_state_", year)
  cum_cols <- paste0("cbsa_state_",min_post_grad:year)
  
  # Calculate the share returning to hs_cbsa for this year
  stock <- raw_microdata[
    , .(shr_return_state = mean(.SD[[1]] == hs_state, na.rm = TRUE)), 
    by = .(col_unitid,prestige_bin),
    .SDcols = col_name
  ]
  cumulative <- raw_microdata[
    , .(shr_ever_return_state = mean(rowSums(.SD == hs_state, na.rm = TRUE) > 0)), 
    by = .(col_unitid,prestige_bin),
    .SDcols = cum_cols
  ]
  
  # Add the current year since graduation to the result
  stock[, years := year]
  cumulative[, years := year]
  return_state_temp <- merge(stock,cumulative,by = c("col_unitid","years","prestige_bin"))
  
  # Append to the results data.table
  return_state <- rbind(return_state, return_state_temp, use.names = TRUE, fill = TRUE)
}

return <- merge(return_cbsa,return_state,by = c("years","col_unitid","prestige_bin"))

write.csv(return,file.path(directory,"Data/05","return_occp.csv"), row.names=FALSE)
```


#    Add Same CBSA Dummy

```{r pos import, include=FALSE}

# Check if user ever lived in hs and college CBSA and state
raw_microdata = raw_microdata[, same_cbsa_hs := Reduce(`|`, lapply(.SD, `==`, hs_cbsa)), .SDcols = paste("cbsa_code",as.character(c(min_post_grad:max_post_grad)),sep="_")]
raw_microdata = raw_microdata[, same_state_hs := Reduce(`|`, lapply(.SD, `==`, hs_state)), .SDcols = paste("cbsa_state",as.character(c(min_post_grad:max_post_grad)),sep="_")]
raw_microdata = raw_microdata[, ever_leave_cbsa_hs := Reduce(`|`, lapply(.SD, `!=`, hs_cbsa)), .SDcols = paste("cbsa_code",as.character(c(min_post_grad:max_post_grad)),sep="_")]
raw_microdata = raw_microdata[, ever_leave_state_hs := Reduce(`|`, lapply(.SD, `!=`, hs_state)), .SDcols = paste("cbsa_state",as.character(c(min_post_grad:max_post_grad)),sep="_")]
raw_microdata = raw_microdata[, same_cbsa_col := Reduce(`|`, lapply(.SD, `==`, col_cbsa_code)), .SDcols = paste("cbsa_code",as.character(c(min_post_grad:max_post_grad)),sep="_")]
raw_microdata = raw_microdata[, same_state_col := Reduce(`|`, lapply(.SD, `==`, col_state)), .SDcols = paste("cbsa_state",as.character(c(min_post_grad:max_post_grad)),sep="_")]
raw_microdata = raw_microdata[, ever_leave_cbsa_col := Reduce(`|`, lapply(.SD, `!=`, col_cbsa_code)), .SDcols = paste("cbsa_code",as.character(c(min_post_grad:max_post_grad)),sep="_")]
raw_microdata = raw_microdata[, ever_leave_state_col := Reduce(`|`, lapply(.SD, `!=`, col_state)), .SDcols = paste("cbsa_state",as.character(c(min_post_grad:max_post_grad)),sep="_")]
# Coerce from NA/TRUE to standard 0/1 dummy variable
cols = c("same_cbsa_hs","same_state_hs","same_cbsa_col","same_state_col","ever_leave_cbsa_hs","ever_leave_state_hs",
         "ever_leave_state_col","ever_leave_cbsa_col")
microdata = raw_microdata[, (cols) :=  lapply(.SD, function(x) ifelse(is.na(x)==TRUE, 0, 1)), .SDcols = cols]

# Count number of non-missing years
microdata[,yrs_included := rowSums(!is.na(.SD)),
          .SDcols = patterns("^cbsa_code")]

# Loop through levels
for (level in c("hs", "col")) {
  # Define the CBSA variable dynamically
  cbsa_col <- paste0(level, "_cbsa_code")
  state_col <- paste0(level, "_state")
  
  # Calculating year of return to state, relative to college graduation
  microdata[, paste0("yr_return_", level, "_cbsa") := {
    comparison_matrix <- lapply(.SD, function(col) as.numeric(col ==  get(cbsa_col)))
    comparison_matrix <- do.call(cbind,comparison_matrix) 
    comparison_matrix[!is.na(comparison_matrix)] <- comparison_matrix[!is.na(comparison_matrix)] + 1
    comparison_matrix[is.na(comparison_matrix)] <- 0
    match_indices <- max.col(comparison_matrix, ties.method = "first")
    match_indices[!rowSums(comparison_matrix==2)] <- NA
    # Subtract 1 from non-NA elements
    match_indices <- ifelse(is.na(match_indices), NA, match_indices - 1)
    #print(year_indices[match_indices])
  }, .SDcols = patterns("^cbsa_code")]

  # Calculating year of return to state, relative to college graduation
  microdata[, paste0("yr_return_", level, "_state") := {
    comparison_matrix <- lapply(.SD, function(col) as.numeric(col ==  get(state_col)))
    comparison_matrix <- do.call(cbind,comparison_matrix) 
    comparison_matrix[!is.na(comparison_matrix)] <- comparison_matrix[!is.na(comparison_matrix)] + 1
    comparison_matrix[is.na(comparison_matrix)] <- 0
    match_indices <- max.col(comparison_matrix, ties.method = "first")
    match_indices[!rowSums(comparison_matrix==2)] <- NA
    # Subtract 1 from non-NA elements
    match_indices <- ifelse(is.na(match_indices), NA, match_indices - 1)
  }, .SDcols = patterns("^cbsa_state")]
}
```

##    Return by Year

```{r filtering}
# Define parameters for dynamic condition creation
levels <- c("hs", "col") # High school and college
geos <- c("cbsa", "state") # Geographic levels
ranges <- c("", " > 9", " > 19", " > 29") # Correspond to unc, 10, 20, 30
groups <- c("unc", "10", "20", "30") # Group labels

# Initialize results
return_results <- list()

# Loop through levels (hs, col)
for (level in levels) {
  for (geo in geos) {
    # Create conditions for the current level and geography
    conditions <- lapply(ranges, function(range) {
      # Dynamically create condition as a string
      cond_str <- paste0(
        "ever_leave_", geo, "_", level, " == 1 & same_", geo, "_", level, " == 1",
        ifelse(range != "", paste0(" & yrs_included", range), "")
      )
      # Parse and evaluate the condition
      parse(text = cond_str)
    })
    
    # Apply conditions to data and store results
    return_results[[paste0(level, "_", geo)]] <- rbindlist(
      lapply(seq_along(conditions), function(i) {
        # Evaluate the condition and compute counts and shares
        microdata[eval(conditions[[i]]) & !is.na(get(paste0("yr_return_", level, "_", geo))),
          .(N = .N),
          by = .(get(paste0("yr_return_", level, "_", geo)))
        ][, `:=`(
          group = groups[i], # Add group label
          type = paste0("return_", level, "_", geo) # Add type label
        )]
      })
    )
  }
}
# Assuming `results` is a list of data.tables
return_by_year <- rbindlist(return_results)

# Split the 'type' column into 'return', 'level', 'geo' using `tstrsplit`
return_by_year[, c("return", "level", "geo") := tstrsplit(type, "_", fixed = TRUE)]

# Remove the original 'return' column
return_by_year[, type := NULL]
return_by_year[, return := NULL]

# Calculate the share of N within each group
return_by_year[, shr := N / sum(N), by = .(group, level, geo)]  

# Order results (optional)
setorder(return_by_year, get, group)

# Rename column for easier intepretation
setnames(return_by_year, "get", "year")

# Conditional on returning to home state, when do people do it
write.csv(return_by_year,file.path(directory,"Data/07","return_by_year.csv"), row.names=FALSE)
```

##    Filtering Birth Years and Geographies

```{r filtering}

birth_outliers = microdata %>%
  # Remove obvious birth outliers
  table.express::filter(col_end > 1981 & col_end < 2022 & birth > 1929 & birth > 1929 & birth < 2003)

territory_hs_col = birth_outliers %>%
  table.express::filter(!hs_state %in% c("GU","PR","AS","VI")) %>%
  table.express::filter(!col_state %in% c("GU","PR","AS","VI"))

birth_outliers = length(unique(birth_outliers$user_id))
territory_hs_col = length(unique(territory_hs_col$user_id))

microdata = microdata %>%
  # Remove obvious birth outliers
  table.express::filter(col_end > 1981 & col_end < 2023 & birth > 1929 & birth < 2003) %>%
  # Remove profiles from US territories since no CBP data
  table.express::filter(!hs_state %in% c("GU","PR","AS","VI")) %>%
  table.express::filter(!col_state %in% c("GU","PR","AS","VI"))

```

## Calculate Distance Between HS and Col

```{r distance, echo=FALSE}

# Obtain list of college zip codes from IPEDS
#inst_zip <- get_education_data(
#    level = "college-university",
#    source = "ipeds",
#    topic = "directory",
#    filters = list(year = 2021),
#    add_labels = TRUE) %>%
#  select(c("unitid","zip")) %>%
#  mutate(col_zip = str_extract(zip, "^.{5}"))

# Merge into microdata
#microdata <- merge(microdata, inst_zip, by.x = "col_unitid", by.y = "unitid", all.x = TRUE)

# Obtain list of high school ZIP codes from NCES
hs_zip <- all_hs %>%
  select(hs_unitid,ZIP) %>%
  rename(hs_zip = ZIP)

# Merge into microdata
microdata <- merge(microdata, hs_zip, by = "hs_unitid", all.x = TRUE)

# https://stackoverflow.com/questions/55408526/r-find-the-distance-between-two-us-zipcode-columns
## Convert the zip codes to data.table so we can join on them
## using the centroid of the zipcodes (lng and lat).
dt_zips <- as.data.table(read.csv(file.path(directory,"Data/03",zipcodefilename),
                                  colClasses = c("character","numeric","numeric")))

# Ensure ZIP code for educational institution is standard five digits
microdata[
  , `:=`(
    col_zip = str_sub(col_zip,1,5),
    hs_zip = str_sub(hs_zip,1,5)
  )
]

## Attach origin lon & lat using a join
microdata[
  dt_zips
  , on = .(col_zip = zipcode)
  , `:=`(
    lng_start = lng
    , lat_start = lat
  )
]

## Attach destination lon & lat using a join
microdata[
  dt_zips
  , on = .(hs_zip = zipcode)
  , `:=`(
    lng_end = lng
    , lat_end = lat
  )
]

## Calculate the distance
microdata[
  , distance_metres := geodist::geodist_vec(
    x1 = lng_start
    , y1 = lat_start
    , x2 = lng_end
    , y2 = lat_end
    , paired = TRUE
    , measure = "haversine"
  )
]

microdata[
  , `:=`(
    distance_km = distance_metres / 1000,
    distance_mi = distance_metres * 0.000621371
  )
]

microdata[, dist := cut(x = distance_mi, 
                   breaks = c(0,50,100,150,200,250,500,1000,10000),
                   #labels = TRUE, 
                   include.lowest = TRUE)]

```

## Merge Occupational Prestige

```{r occp-prestige}

#posfilename3 = "cleaned_pos_educ_sample.csv"
bls_occupation_filename = "occupation.xlsx"
bls_education_filename = "education.xlsx"
occupational_prestige_filename = "OccupationalPrestigeRatings.csv"

# Import occupational prestige data from Harvard Dataverse
# https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/G1E4BF
raw_prestige = read_csv(file.path(directory,"Data/07",occupational_prestige_filename),
                                  col_types = cols_only(`ONET SOC 2018 Code` = col_character(),
                                                        `OPR Job Rating` = col_double(),
                                                        `ONET SOC 2018 Title` = col_character())) %>%
  rename(prestige = `OPR Job Rating`,
         socp_raw = `ONET SOC 2018 Code`,
         socp_title = `ONET SOC 2018 Title`)

# Import educational attainment by detailed occupation
# https://www.bls.gov/emp/documentation/education-training-system.htm
soc_educ <- readxl::read_excel(file.path(directory, "Data", bls_education_filename), 
                               col_types = c("text","text","numeric","numeric","numeric","numeric","numeric","numeric","numeric"),
                                sheet = "Table 5.3")[-1, -1] %>%
  mutate(shr_ba = as.numeric(`...7`) + as.numeric(`...8`) + as.numeric(`...9`)) %>% # Ensure columns are numeric
  select(shr_ba,`...2`) %>%  # Select the last column (which is now the rightmost)
  rename(socp = `...2`) 
  # Rename the rightmost column
# Import employment by detailed occupation
# https://www.bls.gov/emp/tables/occupational-projections-and-characteristics.htm
raw_occp <- readxl::read_excel(file.path(directory, "Data", bls_occupation_filename), 
                               col_types = c("text","text","text","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric"),
                                sheet = "Table 1.2")[-1, ]
# Import distribution of occupations in LI data
#pos_summary = fread(file.path(directory,"Data/07","soc_li_distribution.csv"))  

  
occp_prestige = raw_prestige %>%
  #dplyr::mutate(socp = str_sub(socp_raw, end = -4)) %>%
  dplyr::mutate(socp = socp_raw) %>%
  dplyr::filter(!is.na(socp)) %>%
  dplyr::group_by(socp,socp_raw) %>%
  dplyr::summarize(prestige = max(prestige, na.rm = TRUE)) %>%
  # These two codes (for fine artists and door to door salespeople) don't have ratings
  dplyr::filter(!socp %in% c("27-1013","41-9091"))

# Extract names of different occupational groupings to improve comprehensibility
soc_labels <- raw_occp %>%
  filter(`...3` == "Summary") %>% 
  select("Table 1.2 Occupational projections, 2023–33, and worker characteristics, 2023 (Numbers in thousands)",`...2`) %>% 
  rename(socp = `...2`,soc_title = "Table 1.2 Occupational projections, 2023–33, and worker characteristics, 2023 (Numbers in thousands)" ) %>%
  mutate(last_3 = substr(socp, start = 5, stop = 7),
         mid_1 = substr(socp, start = 4, stop = 4),
         soc_3 = substr(socp, start = 1, stop = 4),
         soc_2 = substr(socp, start = 1, stop = 2))
# Extract names for two-digit SOCs
soc_2_labels <- soc_labels %>%
  filter(mid_1 == "0" & soc_2 != "00") %>%
  mutate(soc_2_title=str_replace_all(soc_title," occupations","")) %>%
  select(soc_2_title,soc_2)
# Extract names for three-digit SOCs
soc_3_labels <- soc_labels %>%
  filter(mid_1 != "0" & last_3 == "000") %>%
  rename(soc_3_title=soc_title) %>%
  select(soc_3_title,soc_3)
  
# Extract detailed occupation employment counts from BLS data 
soc_occp <- raw_occp  %>%
  filter(`...3` == "Line item") %>% 
  select("Table 1.2 Occupational projections, 2023–33, and worker characteristics, 2023 (Numbers in thousands)",`...2`, `...4`) %>% 
  rename(socp = `...2`, emp_2023 = `...4`,soc_title = "Table 1.2 Occupational projections, 2023–33, and worker characteristics, 2023 (Numbers in thousands)" )

# Identify SOCs that appear in LI data but not BLS
microdata_socp <- microdata[,socp := substr(soc_code_mode, start = 1, stop = 7)] 
micro_socp <- unique(microdata_socp$socp)
misfit_socp_list <- micro_socp[!micro_socp %in% soc_occp$socp]

#micro_socp8 <- unique(microdata$soc_code_mode)
#misfit_socp8_list <- micro_socp8[!micro_socp8 %in% occp_prestige$socp_raw]
#misfit_socp8 <- data.frame(socp_raw = misfit_socp8_list,
#           emp_2023 = NA,
#           soc_title = NA,
#           shr_ba = NA,
#           col_grad = NA,
#           socp = substr(misfit_socp8_list, start = 1, stop = 7),
#          prestige = NA)

# Merge prestige ratings, share with BAs, and estimated prevalence in 2022
#soc_full = rbind(soc_occp,misfit_socp) %>%
soc_full = soc_occp %>%
  left_join(soc_educ, by = "socp") %>%
  # Calculate number of college grads in occupation
  mutate(col_grad = (shr_ba/100) * as.numeric(emp_2023) * 1000) %>%
  left_join(occp_prestige, by = "socp") %>%
  #rbind(misfit_socp8) %>%
  mutate(soc_3 = substr(socp, start = 1, stop = 4),
         soc_2 = substr(socp, start = 1, stop = 2)) %>%
  left_join(soc_3_labels, by = "soc_3") %>%
  left_join(soc_2_labels, by = "soc_2")

# For SOC codes missing a prestige rating, I take the average rating of other jobs
# in the same 3-digit code, weighted by their frequency among college graduates in 2022
prestige_imputation_3 = soc_full %>%
  group_by(soc_3) %>%
  summarize(prestige_imp_3 = weighted.mean(prestige, w = col_grad, na.rm = TRUE))
prestige_imputation_2 = soc_full %>%
  group_by(soc_2) %>%
  summarize(prestige_imp_2 = weighted.mean(prestige, w = col_grad, na.rm = TRUE))

# Impute prestige bin for occupations in LI data but not BLS
misfit_socp <- data.frame(socp = misfit_socp_list,
           emp_2023 = NA,
           soc_title = NA,
           col_grad = NA,
           shr_bls = NA,
           shr_ba = NA,
           prestige_bin = NA,
           prestige = NA
           ) %>%
  mutate(soc_3 = substr(socp, start = 1, stop = 4),
         soc_2 = substr(socp, start = 1, stop = 2)) %>%
  left_join(soc_3_labels, by = "soc_3") %>%
  left_join(soc_2_labels, by = "soc_2") %>%
  left_join(prestige_imputation_3, by = "soc_3") %>%
  left_join(prestige_imputation_2, by = "soc_2") %>%
  mutate(prestige_imp = case_when(!is.na(prestige) ~ prestige,
                              (is.nan(prestige) | is.na(prestige)) & (!is.nan(soc_3) | !is.nan(soc_3)) ~ prestige_imp_3,
                              !is.nan(prestige_imp_2) ~ prestige_imp_2))

# Calculate total workers and find bin thresholds
total_workers <- sum(soc_full$col_grad, na.rm = TRUE)
workers_per_bin <- total_workers / 3

# Place all occupations into bins and merge LI data
soc_ba = soc_full %>%
  left_join(prestige_imputation_3, by = "soc_3") %>%
  left_join(prestige_imputation_2, by = "soc_2") %>%
  mutate(prestige_imp = case_when(!is.na(prestige) ~ prestige,
                              (is.nan(prestige) | is.na(prestige)) & (!is.nan(soc_3) | !is.nan(soc_3)) ~ prestige_imp_3,
                              !is.nan(prestige_imp_2) ~ prestige_imp_2)) %>%
  mutate(prestige_imp = ifelse(is.nan(prestige_imp)==TRUE,prestige_imp_2,prestige_imp)) %>%
  arrange(prestige_imp) %>%
  mutate(cum_workers = cumsum(col_grad)) %>%
  mutate(prestige_bin = case_when(cum_workers <= workers_per_bin ~ "Low",
                                  cum_workers <= 2 * workers_per_bin ~ "Middle",
                                  TRUE ~ "High")) %>%
  mutate(shr_bls = col_grad/sum(col_grad)) %>%
  select(-c(cum_workers,socp_raw)) %>%
  rbind(misfit_socp) %>%
  arrange(prestige_imp) %>%
  tidyr::fill(prestige_bin, .direction = "downup")

write.csv(soc_ba,file.path(directory,"Data/07","soc_ba.csv"), row.names=FALSE)


soc_merge = soc_ba %>%
  select("soc_title","socp","prestige_imp","prestige_bin") %>%
  filter(!is.na(socp)) %>%
  distinct(socp, .keep_all = TRUE)

write.csv(soc_ba,file.path(directory,"Data/07","soc_merge.csv"), row.names=FALSE)


# Subset to educator codes
teacher_recodes <- soc_occp %>%
  filter(substr(socp,1,4)=="25-2" & socp != "25-2032") %>%
  left_join(soc_educ, by = "socp") %>%
  mutate(col_grad = (shr_ba/100) * as.numeric(emp_2023) * 1000) %>%
  mutate(weights = col_grad/sum(col_grad))

cumulative_weights <- cumsum(teacher_recodes$weights)
soc_recodes <- paste0(teacher_recodes$socp,".00")

microdata[, random_value := runif(.N)]
microdata[, soc_code_mode := fifelse(
    soc_code_mode %in% c("19-3093.00","19-2011.00","19-1011.00"),
    fcase(
      random_value <= cumulative_weights[1], soc_recodes[1],
      random_value <= cumulative_weights[2], soc_recodes[2],
      random_value <= cumulative_weights[3], soc_recodes[3],
      random_value <= cumulative_weights[4], soc_recodes[4],
      random_value <= cumulative_weights[5], soc_recodes[5],
      random_value <= cumulative_weights[6], soc_recodes[6],
      random_value <= cumulative_weights[7], soc_recodes[7],
      random_value <= cumulative_weights[8], soc_recodes[8],
      random_value <= cumulative_weights[9], soc_recodes[9],
      random_value <= cumulative_weights[10], soc_recodes[10],
      random_value <= cumulative_weights[11], soc_recodes[11]
    ),
    soc_code_mode
)]
microdata <- microdata[,random_value :=NULL]
microdata <- microdata[,socp := substr(soc_code_mode,1,7)]
microdata = merge(microdata, soc_merge, by = "socp",all.x=TRUE)

# Recount the occupational distribution for subsequent figure and table production
soc_li_dist <- microdata[,.(count = .N),by=.(soc_code_mode)]
soc_li_dist[,shr_li := (count/sum(count))]
soc_li_dist[,count := NULL]
write.csv(soc_li_dist,file.path(directory,"Data/07","soc_li_distribution.csv"), row.names=FALSE)

```



## Merge Shocks with Microdata
If using preloaded data, start here to update
```{r merge shocks}

# Only keep deciles for merge, removing raw shock calculations 
#cbsa_shock_merge = cbsa_shock_ptile %>%
#  select(cbsa_code,year,starts_with("ptile_avg"),starts_with("avg"))
cols = c("hs_shock_avg_1","hs_shock_avg_3","hs_shock_avg_5","hs_shock_avg_7","col_shock_avg_1","col_shock_avg_3","col_shock_avg_5","col_shock_avg_7","V1")
microdata[, (cols) := NULL]

microdata[
  cbsa_shock_ptile
  , on = .(hs_cbsa_code = cbsa_code,
           col_end = year)
  , `:=`(
    hs_cbsa_actual = cbsa_actual,
    hs_cbsa_proj = cbsa_proj,
    hs_cbsa_proj_change = cbsa_proj_change,
    hs_shock_ptile_1 = ptile_shock_avg_1,
    hs_shock_ptile_3 = ptile_shock_avg_3,
    hs_shock_ptile_5 = ptile_shock_avg_5,
    hs_shock_ptile_7 = ptile_shock_avg_7,
    hs_shock_1 = shock_avg_1,
    hs_shock_3 = shock_avg_3,
    hs_shock_5 = shock_avg_5,
    hs_shock_7 = shock_avg_7,
    hs_growth_ptile_1 = ptile_growth_avg_1,
    hs_growth_ptile_3 = ptile_growth_avg_3,
    hs_growth_ptile_5 = ptile_growth_avg_5,
    hs_growth_ptile_7 = ptile_growth_avg_7,
    hs_growth_1 = growth_avg_1,
    hs_growth_3 = growth_avg_3,
    hs_growth_5 = growth_avg_5,
    hs_growth_7 = growth_avg_7
  )
]

microdata[
  cbsa_shock_ptile
  , on = .(col_cbsa_code = cbsa_code,
           col_end = year)
  , `:=`(
    col_cbsa_actual = cbsa_actual,
    col_cbsa_proj = cbsa_proj,
    col_cbsa_proj_change = cbsa_proj_change,
    col_shock_ptile_1 = ptile_shock_avg_1,
    col_shock_ptile_3 = ptile_shock_avg_3,
    col_shock_ptile_5 = ptile_shock_avg_5,
    col_shock_ptile_7 = ptile_shock_avg_7,
    col_shock_1 = shock_avg_1,
    col_shock_3 = shock_avg_3,
    col_shock_5 = shock_avg_5,
    col_shock_7 = shock_avg_7,
    col_growth_ptile_1 = ptile_growth_avg_1,
    col_growth_ptile_3 = ptile_growth_avg_3,
    col_growth_ptile_5 = ptile_growth_avg_5,
    col_growth_ptile_7 = ptile_growth_avg_7,
    col_growth_1 = growth_avg_1,
    col_growth_3 = growth_avg_3,
    col_growth_5 = growth_avg_5,
    col_growth_7 = growth_avg_7
  )
]

```

## Export Full Version

```{r merge shocks}

# Export full sample
write.csv(microdata,file.path(directory,"Data/06/microdata.csv"), row.names=FALSE)
# Export sample to ease testing
microdata_sample <- microdata[sample(.N,100000)]
write.csv(microdata_sample,file.path(directory,"Data/06/microdata_sample.csv"), row.names=FALSE)

```

## Export Compressed Version

```{r merge shocks}

# Compress size of file to speed up import, export, and exploration of data
# Ensures the number of shocks and same geography criteria can vary
patterns_list <- c("^hs","^col","^same","^ever","^yr")
pattern_cols <- names(microdata)[Reduce(`|`, lapply(patterns_list, function(pat) grepl(pat, names(microdata))))]
selected_cols <- c("user_id","transfer", "work_start", "birth", "distance_mi",
                   "state_mode","cbsa_mode",
                    "dist","soc_code_mode","prestige_imp","soc_title","prestige_bin",pattern_cols)

microdata <- microdata[, .SD, .SDcols = selected_cols]

write.csv(microdata,file.path(directory,"Data/06/microdata_compressed.csv"), row.names=FALSE)


```
