---
title: "02_import_ed_microdata"
author: "Nicholas Martens"
date: "2023-06-09"
output: html_document
---
## Setup

Directories and filenames that change with machine
```{r directory, include=FALSE}
directory = "/Users/nickmartens/Dropbox (University of Michigan)/Linkedin/"
edufilename = "raw_educ_STATES.csv"
```

Import necessary packages
```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(data.table)
library(tidyverse)
```

## Declaring Functions
Function used to compute mode of a dataset

```{r mode, include=FALSE}
Mode <- function(x, na.rm = TRUE)
{
  if(na.rm)
  {
    x = x[!is.na(x)]
  }
  ux <- unique(x)
  return(ux[which.max(tabulate(match(x,ux)))])
}
```

Declare %nin% so we can filter observations

```{r negate, include=FALSE}
`%nin%` = Negate(`%in%`)
```

## Import and Clean Education File
Import raw education file from LinkedIN
Complete basic string cleaning like removing dashes and making lowercase

```{r import, echo=FALSE}
ed_li = read_csv(file.path(directory,"Data/02",edufilename)) %>%
  mutate(alt_name = str_to_lower(university_name),
#         alt_name = str_trim(alt_name),
         alt_name = str_replace_all(alt_name, "-"," "),
         alt_name = str_replace_all(alt_name, "—"," "),
         alt_name = str_replace_all(alt_name, ","," "),
         alt_name = str_replace_all(alt_name, "main campus",""),
         #        alt_name = str_replace_all(alt_name,"^the ",""),
         alt_name = str_trim(alt_name)) %>%
  mutate(clean_name = alt_name) %>%
  # Filter out 135,449 associates 
  filter(degree != "Associate")
```

## Extract High School Diplomas

```{r hs split, echo=FALSE}
li_hs = ed_li %>%
  filter(degree == "High School") %>%
  # Remove any observations that match to a postsecondary institution
  left_join(all_col, by = "alt_name") %>%
  distinct(user_id,INSTNM, .keep_all = TRUE)

# Reclassifies observations Revelio misidentified
li_hs_missclassified = li_hs %>%
  filter(is.na(barrons)==FALSE) %>%
  mutate(degree.x = "Bachelor") %>%
  rename(degree = degree.y)

# High schools correctly classified by Revelio
li_hs_correct = li_hs %>%
  filter(is.na(barrons)==TRUE) %>%
  select(-c(UNITID:barrons)) %>%
  left_join(all_hs, by = "alt_name") %>%
  filter(is.na(clean_name.y)==FALSE) %>%
  distinct(user_id,NAME, .keep_all = TRUE) %>%
  select(-c(clean_name.x,degree.x)) %>%
  # Rename to columns to appease to rbind gods
  rename(clean_name = clean_name.y)
```

## Extract Unknown Degrees

```{r hs split, echo=FALSE}
# Users with unknown degrees
# Currently matches based on first institution listed
# Eventually I will hone the matching based on workhistory
li_unknown = ed_li %>%
  filter(degree == "empty") %>%
  left_join(all_col, by = "alt_name") %>%
  distinct(user_id,INSTNM, .keep_all = TRUE)
li_unknown_col = li_unknown %>%
  filter(is.na(degree.y)==FALSE) %>%
  rename(degree = degree.y)
li_unknown_unmatched = li_unknown %>%
  filter(is.na(degree.y)==TRUE) %>%
  select(-c(INSTNM:barrons)) %>%
  left_join(all_hs, by = "alt_name") %>%
  distinct(user_id,NAME, .keep_all = TRUE)
li_unknown_hs = li_unknown_unmatched %>%
  filter(is.na(clean_name.y)==FALSE) %>%
  # Rename to columns to appease to rbind gods
  rename(clean_name = clean_name.y) %>%
  select(-c(degree.x,clean_name.x,UNITID))
```

## Extract College Degrees

```{r col split, echo=FALSE}
# College groups bachelor's and master's degrees together
li_col = ed_li %>%
  filter(degree %nin% c("empty","High School")) %>%
  # Remove any observations that match to a postsecondary institution
  left_join(all_hs, by = "alt_name") %>%
  distinct(user_id,NAME, .keep_all = TRUE)

# Reclassifies observations Revelio misidentified
# Marks any graduates of the New School as high schoolers unless corrected
li_col_missclassified = li_col %>%
  filter(is.na(clean_name.y)==FALSE) %>%
  filter(alt_name != "the new school") %>%
  mutate(degree.x = "High School") %>%
  select(-c(clean_name.x,degree.x)) %>%
  rename(degree = degree.y,
         clean_name = clean_name.y)

# High schools correctly classified by Revelio
li_col_correct = li_col %>%
  filter(is.na(clean_name.y)==TRUE | alt_name == "the new school") %>%
  select(-c(NAME:clean_name.y)) %>%
  left_join(all_col, by = "alt_name") %>%
  filter(is.na(degree)==FALSE) %>%
  distinct(user_id,INSTNM, .keep_all = TRUE) %>%
  mutate(degree.x = if_else(is.na(degree.x)==TRUE,degree,degree.x)) %>%
  # For now I will filter out all graduate degrees
  filter(degree.x == "Bachelor") %>%
  # Rename to columns to appease to rbind gods
  rename(clean_name = clean_name.x)
```

##    Combine Correct + Incorrect

```{r combine, echo=FALSE}

options(scipen=999)

# Create unified list of users with bachelors degrees
col = rbind(li_col_correct, li_hs_missclassified, li_unknown_col) %>%
  group_by(user_id)
# Create unified list of users with high schools listed
hs = rbind(li_hs_correct, li_col_missclassified, li_unknown_hs) %>%
  group_by(user_id)

col_users = col %>%
  group_keys()

hs_users = hs %>%
  group_keys()


both = intersect(col_users$user_id,hs_users$user_id)
both = as_tibble(both) %>%
  rename(user_id = value)
```